### 2020-09-19 SuplementaryInformation.tex
Add files via upload

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

	%\title{Thickness optimization in wide range quasi omnidirectional multilayer
	% structures}
	\title{Suplementary information: Thickness optimization in wide range quasi
		omnidirectional 1-D photonic structures}
	\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
				victor1\_1@hotmail.com}}}
	\author[1,2,3]{Luis Eduardo Puente-Díaz}
	\author[4]{D. Ariza-Flores}
	\author[3]{Hector Pérez-Aguilar}
	\author[2]{W. Luis Mochán\thanks{email: {\tt
				mochan@fis.unam.mx}}}
	\author[1]{Vivechana Agarwal\thanks{email: {\tt
				vagarwal@uaem.mx}}}
	\affil[1]{Centro de Investigación en Ingeniería y Ciencias Aplicadas,
		Universidad del Estado de Morelos, Av. Universidad 1001
		Col. Chamilpa, Cuernavaca, Morelos 62209, México.}
	\affil[2]{Instituto de Ciencias Físicas, Universidad Nacional Autónoma
		de México, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca,
		Morelos, México.}
	\affil[3]{Facultad de Ciencias Físico Matemáticas,
		Universidad Michoacana de San Nicolás de Hidalgo, Av. Francisco
		J. Múgica S/N 58030, Morelia, Mich., México.}
	\affil[4]{Conacyt-Universidad Autónoma de San Luis Potosí, Karakorum 1470, Lomas 4ta Secc, San Luis Potosí, S.L.P., 78210, México.}
	%\date{{\small {\today}}}
	\maketitle

\section{Development of the transfer matrix}

If you consider that the system only varies on the $z$ axis (as show in Fig.
\ref{Fig1}(a)) , the transfer matrix is $M\left(z_{2},z_{1}\right) ${}{}a
2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left( 
\begin{array}{c}
E_{\Vert } \\ 
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left( 
\begin{array}{c}
E_{\Vert } \\ 
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%

Many equivalent formulations have been proposed to obtain $M$ . For example, if you 
have a complete multilayer system and it periodically replicates to form an artificial photonic crystal, then Bloch's theorem can be used to describe the normal 
modes of this crystal. According to Bloch's theorem, the modes of a periodic system 
may be written as a superposition of Bloch waves, each of which acquires a 
\emph{phase factor} as it propagates from one period to the next. Therefore, each 
Bloch wave would obey 
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\ 
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\ 
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\ 
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ represents a 1D Bloch's
vector corresponding to a wave that propagates along $z$-direction. Thus, $\Lambda _{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that exactly $\det M=1$
is used, so that the product of eigenvalues ought to be $\Lambda _{+}\Lambda
_{-}=1$, and the dispersion relation of the Bloch modes may be obtained in
principle from 
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials a and b, with refractive indices $n_{a}$ and $n_{b}$, and their
		thickness $d_{a}$ and $d_{b}$ gradually increases according to the condition
		of $1/4$ of the wavelength at wich $j$-th. period will be sintonized. 
		\textbf{E}$_{\protect\alpha }^{\protect\beta }$ and \textbf{H}$_{\protect%
			\alpha }^{\protect\beta }$ are the electric and magnetic fields, and \textbf{%
			k}$_{\protect\alpha }^{\protect\beta }$ is the wavevector, where $\alpha
		=\left\{ i,r,a,b\right\} $ corresponds to the medium where the wave is
		traveling and $\beta =\{-,+\}$ to the direction of propagation of the wave
		along the $\pm z$ axis. (b) The multilayer system can be replaced by a broad
		effective layer within which the electric \textbf{E}$_{\protect\beta }$ and
		magnetic \textbf{H}$_{\protect\beta }$ fields, and a Bloch wave \textbf{K}$_{%
			\protect\beta }$ propagate in the positive direction and another set
		propagate in the opposite direction along the $z$ axis.}
	\label{Fig1}
\end{figure}

Now, considering a finite system made of $P$ periods, with $PD$ thickness
and placed on a substrate. For the extreme case of only $P=1$ period, the
optical properties of this system can be obtained by considering an incoming
wave from the ambient, a wave reflected to the environment, a wave
transmitted to the substrate, and two Bloch waves within the structure, one
moving up and other down, as show in Fig. \ref{Fig1}(b).

Hence, the continuity of $E_{\Vert }$ and $H_{\Vert }$ will produce two
equations at each interface, with which the four unknowns are obtained,
namely $r$, $t$ and the amplitudes of two Bloch's waves. In a finite system, 
$K$ can be complex. Even in the presence of very little dissipation, Bloch's
waves should decay as they propagate. Thus, the eigenvalue of ascending mode 
$\Lambda _{+}=e^{iKD}$ is identified as the one that obeys $|\Lambda +|<1$, $%
\text{Im}K>0$, adding a negligible amount of dissipation if necessary to
avoid cases $|\Lambda +|=1$.

From the eigenvalues $\Lambda _{\pm }$ of the transfer matrix, we may obtain
the corresponding eigenvectors $E_{\Vert }^{\pm }$ and $H_{\Vert }^{\pm }$
from Eq. (\ref{Bloch}), and from them, the corresponding surfaces impedances 
\begin{equation}
Z^{\pm }=-\frac{M_{12}}{M_{11}-\Lambda _{\pm }},  \label{Z+-}
\end{equation}%
where $M_{ij}$ with $i=1,2$ and $j=1,2$ denote the elements of the transfer
matrix $M$. By writing the fields at $z_{0}$ and $z_{N}$ as a superposition
of the upward and downward propagating (or decaying) fields, $E_{\Vert
}^{\pm }=Z^{\pm }H_{\Vert }^{\pm }$, we can relate the fields at $z_{N}$ to
the fields at $z_{0}$ through a \emph{reconstructed} transfer matrix, 
\begin{equation}
\begin{pmatrix}
E_{\Vert } \\ 
H_{\Vert }%
\end{pmatrix}%
_{z_{N}}=\tilde{M}%
\begin{pmatrix}
E_{\Vert } \\ 
H_{\Vert }%
\end{pmatrix}%
_{z_{0}},  \label{tilMEH}
\end{equation}%
where 
\begin{equation}
\tilde{M}=\frac{1}{Z^{+}-Z^{-}}%
\begin{pmatrix}
Z^{+}e^{iKD}-Z^{-}e^{-iKD} & -2iZ^{+}Z^{-}\sin KD \\ 
2i\sin KD & Z^{+}e^{-iKD}-Z^{-}e^{iKD}%
\end{pmatrix}%
.  \label{tilM}
\end{equation}%
Finally, the explicit expressions for the optical coefficients are: 
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
	\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
	_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and 
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
	_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) has been chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization.

\section{Chirped-type Bragg mirrors}

As the porosity contrast of the periods increases, the thickness of the structure 
decreases and the average reflectance increases, as shown in table 1. For example, 
you could have structures with a thickness of 10 $\mu$m and their average 
reflectance greater than 90$\%$.

\begin{table}[tbph]
	\caption{ Design parameters obtained after the optimization of functions for maximum average reflectance and minimum thickness }
	\includegraphics[width=\textwidth]
	{SITableOptimized.pdf}
\end{table}

The mapping of the calculated reflectance of the structures designed with the 
optimized parameters is shown in Fig. \ref{Fig2}. Here it is observed that all of 
them have a PBG in the NIR region of the electromagnetic spectrum, i. e.,  
structures designed from functions $f_{1}$ and $f_{3}$ with a porosity contrast of 
$30/76\%$ have the highest PBG localized from 970 to 1370 nm, these are shown in 
panels (a) and (c). \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIReflectanceVisNIR.pdf}
	\end{center}
	\caption{Calculated reflectance of the structures designed with the optimized parameters of $f_{1}$ (left), $f_{2}$ (center) and $f_{3}$ (right) and with the porosity contrasts of $30/76\%$ (upper panels) and $42/76\%$ (lower panels). The dotted lines limit the area of the PBG.}
	\label{Fig2}
\end{figure}

\newpage

\section{Photonic structure with sub-mirrors stacking}

Before showing the design of the structures formed by the stacking of sub-mirrors, 
the transfer matrix trace of individual mirrors formed by one period (Fig. 
\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)) was calculated. The reflectance 
of each mirror with its respective periods was also calculated (Figs. \ref{Fig3}(c) 
and \ref{Fig3}(d)). Each mirror was designed to reflect a wavelength in the range of 
400-3000 nm and the illumination range was the same. Additionally, the T$r|\text{M}|$ and R$(\lambda,\theta)$ were calculated for light with TE 
polarization and 45${{}^\circ}$ of incidence. In Fig. 3d it is shown that by using 
mirrors that have 6 periods and designed to reflect at wavelengths greater than 1000 
nm, they also reflect in a certain region of the visible spectrum. Then, to 
reinforce the reflection of the electromagnetic waves in the visible, it is enough 
to place a smaller number of periods. This is another reason for the increasing 
number of periods in the 400 to 800 nm region. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SITrazasyRefSE.pdf}
	\end{center}
	\caption{Calculated transfer matrix trace and reflectance of individual mirrors using ((a) and (c)) one period  and ((b) and (d)) six periods, respectively. Each mirror was tuned to a wavelength between 400 and 3000 nm. The calculations were made in the visible and NIR region and at 45${{}^\circ}$ of incidence.}
	\label{Fig3}
\end{figure}
\newpage

It is common to imagine that the stacking of the sub-mirrors is the following: that 
the PBG of the second mirror begins at the edge of the PBG of the first mirror, the 
third PBG that begins at the edge of the PBG of the second mirror, and so on until 
the desired interval is completed. With this configuration, the reflectance 
decreases at each intersection of the two PBGs. For example, in Figs. \ref{Fig4}(a) 
and \ref{Fig4}(b) show the calculated R$(\lambda, \theta)$ for the structures formed 
by sub-mirrors that have one and six periods, respectively, using non-polarized 
light. In these cases, the calculations do not show a PBG, or quasi-PBG. For this 
reason, the R$_{Ave}(\lambda, \theta)$ was maximized through the percentage of 
overlap of the PBGs of two consecutive sub-mirrors. In Fig. 3 (b) of the main 
article the results obtained at the end of the optimization process are shown. The 
calculated R$(\lambda, \theta)$ for the structures designed with 4 periods for each 
sub-mirror and using the pattern described in the main article are shown in Figs. 
\ref{Fig4}(c) and \ref{Fig4}(d) of this document, respectively. Here the overlap of 
the two consecutive PBGs was optimized, being $72\%$ for the first case and $78\%$ 
for the last. Furthermore, the calculations indicate that the structures have a 
quasi-PBG.

\begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIReflectanceSEoptimized.pdf}
	\end{center}
	\caption{Reflectance calculated for structures designed through the stacking of 
		sub-mirrors analyzing the overlap of the PBG and the number of periods of 
		each one of them. Case I: there is no overlap of the PBGs and each 
		sub-mirror has (a) one period and (b) six periods. Case II: optimized 
		overlap of consecutive PBGs and (c) each subsmirror has 4 periods with 
		$72\%$ overlap, and (d) proposed arrangement in the main article with 6 
		periods for $\lambda>800$ nm and $78\%$ overlap. The quasi-OD region is bounded by the dotted lines.
	}
	\label{Fig4}
\end{figure}

\end{document}

### 2020-09-19 PaperVictor.tex
Add files via upload

\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{ Thickness optimization in wide range quasi
omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-Dìaz}
\author[4]{D. Ariza-Flores}
\author[3]{Hector Pérez-Aguilar}
\author[2]{W. Luis Mochán\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigación en Ingenierìa y Ciencias Aplicadas,
	Universidad del Estado de Morelos, Av. Universidad 1001
	Col. Chamilpa, Cuernavaca, Morelos 62209, México.}
\affil[2]{Instituto de Ciencias Fìsicas, Universidad Nacional Autónoma
	de México, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca,
	Morelos, México.}
\affil[3]{Facultad de Ciencias Fìsico Matemáticas,
	Universidad Michoacana de San Nicolás de Hidalgo, Av. Francisco
	J. Múgica S/N 58030, Morelia, Mich., México.}
\affil[4]{Conacyt-Universidad Autónoma de San Luis Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potosì, S.L.P., 78210, México.}
%\date{{\small {\today}}}
\maketitle

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayer structures, since high and low porosity layers
can be synthesized by simple electrochemical technique. We report the
maximization of average reflectance (R$_{\text{prom}}\left(\lambda,\theta%
\right)$) with minimum possible thickness of PS-based mirrors with different
porosity contrasts. Optimization is performed in two regions (Visible and
NIR) of the electromagnetic spectrum. We employ two techniques to design the
mirrors: \textit{chirped} structures and the \textit{stacking} of sub-mirrors. The
chirped structures were found to be relatively more suitable for obtaining
highly reflectivity in the visible range, while the second type of
structure was more effective for obtaining high reflectivity in the IR
region. Some of the optimized omnidirectional structures with less than 100
periods have been designed and experimentally demonstrated in a wide
spectral range.
\end{abstract}

\section{Introduction}

Photonic crystal (PC)-based structures are extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and 
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be limited by photonic band gaps (PBGs)
where transmission states are forbidden. The PC  shows a 
PBG corresponding to the electromagnetic modes which are not allowed to propagate
through the structure and behaves as a perfect mirror for that range. The width of
reflection spectrum is important while designing an omnidirectional mirror for 
different applications. The metallic mirrors are widely accepted for reflection 
purposes, but widespread use is limited due to their absorptive nature at the 
visible and near infrared frequencies.  A good alternative are dielectric
structures as they also provide design flexibility in terms of
reflection wavelength. These properties are widely used to design various
one-dimensional (1D) and two-dimensional (2D) PCs for its
potential applications in optoelectronics, optical telecommunications and computing, 
laser technology \cite{Lopez2013,Masaya2010}, and radiative cooling applications 
\cite{Kumar2020}. The simplest 1D PC is composed of alternating high $\left( 
n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror, 
BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
n_{H}d_{H}=n_{L}d_{L}=\lambda _{0}/4$, at some operating wavelength $\lambda
_{0}$ (center wavelength) to obtain a certain
omnidirectional band gap. As the gap depends on the contrast of the
refractive indices and the number of periods,  broadband mirrors can  be
engineered by modulating the reflection in a broader wavelength range.
One of the ways to obtain such structures has been the continuous variation of 
thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997} 
structures. Additionally, broader mirrors can also be achieved by overlapping 
different BMs, where each one reflects around a specific central wavelength, 
resulting in a wider photonic band gap \cite{Xifre2009}.

Till now, different deposition techniques have been used to obtain omnidirectional 
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of 
TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003} 
used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers, 
followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by 
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting 
respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm 
wavelength. Furthermore, Jena et al., \cite{Jena2016}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate 1DPC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and
require sophisticated equipment and long fabrication time. Using porous silicon (PS) 
is an alternative, as PS is typically fabricated by simple electrochemical etching of
crystalline Si in hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air in a relatively short duration of 
time. The generated porosity can be tuned by changing the applied current
density and hence modifies the refractive index of the resulting PS. This
fact opens the possibility of designing 1DPC with PS, which seeks to
control the propagation of light in a dielectric medium. The low cost and
ease of obtaining porous silicon make it an excellent candidate to develop
optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of porous silicon, they have been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
photoluminescence control \cite{Antunez2014}. Recently, the study of 
quasi-omnidirectional Bragg mirrors has increased due to their possible application 
as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric 
optical filters, quasi-ODBM and ODBM have been extensively studied in different 
regions of the electromagnetic spectrum, such as ultraviolet (UV) 
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping 
in view that high values of average porosity, refractive index contrast and 
thickness make the multilayer structures fragile, in this work various wide
band gap photonic structures have been proposed to obtain maximal average 
reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum 
possible thickness and low refractive index contrast.

This paper is organized as follows. Section 2 presents the development of
methods used to design and calculate the reflectance spectra of the PS
multilayer structures. Section 3 provides the experimental details about the
fabrication of some of these structures. Section 4 presents the numerical
results corresponding to different methodologies (chirped structures and sub-mirror stacks) adopted to minimize the thickness of the structure for 
maximal reflectance along with the experimental results and its comparison with the 
existing reports.  The obtained experimental results revealed an enhancement in the 
quasi omnidirectional band gap (0-60${{}^\circ}$) by a factor of approximately 2 
with half the structure physical thickness in both the configurations, compared to 
the last reported works \cite{DelRio2018,Chavez2020}. Finally, the conclusions of 
this work are presented in Section 5.

\section{Theoretical analysis}

In the analysis of the propagation of the electromagnetic field through
multilayer systems, it is common to employ the transfer matrix method (put the 
reference). Under the consideration that the system only varies along the $z$ axis, the transfer matrix is $M\left(z_{2},z_{1}\right)$ 
a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left( 
\begin{array}{c}
E_{\Vert } \\ 
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left( 
\begin{array}{c}
E_{\Vert } \\ 
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain $M$ \cite%
{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism  
to calculate the reflectance of large multilayer systems proposed by Puente-D%
\'{\i}az, et al \cite{Puente2020}, since we need a reliable and stable tool
to design an optimized structure through a minimization procedure that
requires the calculation of complete spectra for all sets of design parameters. 
The development of $M$ is shown in the supplementary information. Therefore, the 
explicit expressions for the optical coefficients are: 
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and 
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization. Additionally, complex refractive indices of the porous 
layers in the simulations were obtained by Bruggeman effective medium theory, which 
has been reported to adequately reproduce the PS optical parameters 
\cite{Giusseppe2011,Pap2006,Estrada2018}.

After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.

\section{Experimental details}

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions 
\cite{Canham90,Escorcia07}. Electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
cm$^{2}$, respectively. However, it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}. 
For this reason, the current
densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
acquired through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions and were weighed ($m_{i}$)
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to calculate
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Brugeman2006}. Etching
rate of PS was obtained by re-synthetizing individual layers under similar
conditions and measuring their thicknesses through scanning electron
microscopy (SEM). The absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident angles $%
\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

\section{Results and discussion}

This section presents the comparison of the calculated and measured reflectance 
spectra at different incidence angles in the regions of interest. In the first 
subsection, the design and optimization of R$_{\text{ave}} 
\left(\lambda,\theta\right)$ of \textit{chirped}  photonic structures is presented, 
and next subsection the design of the structure is analyzed through sub-mirrors 
stacks.

\subsection{Chirped-type Bragg mirrors}

The generic form of the expression that modulates the design of photonic
structure is: 
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left( x_{j}\right),\label{Dis}
\end{equation}%
where $\lambda _{\min }$, $\lambda _{\max }$ and $\lambda _{j}$ correspond
to the minimum, maximum, and design wavelengths to which the $j$-th period
is tuned, respectively, and $f\left( x_{j}\right) $ represents any
normalized function that modulates the thickness. Here $x_{j}=\frac{j}{N_{p}}$ being 
$j$ the $j$-th period and $N_{p}$ the total number of periods that the structure 
will contain. Only restriction for $f\left( x_{j}\right) $ is that it has to be an 
increasing function, due to the high absorption of PS in the ultraviolet region 
which decreases in the visible and becomes negligible in the near infrared. So, the 
first periods are syntonized in the UV-Vis regions. This work shows the analysis
of following functions:
\begin{equation}
f_{1}\left( x\right) =x^{\alpha },  \label{F1}
\end{equation}%
\begin{equation}
f_{2}\left( x\right) =A\left( x^{\alpha }+x^{\beta}\right)
\label{F2}
\end{equation}%
and%
\begin{equation}
f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
\end{equation}%
where $\alpha $, $\beta $ and $A$ are parameters to optimize. The function 
$f_{1}$ (Eq. (\ref {F1})) represents the simplest profiles. The restrictions 
for the values $\alpha$ are that they must be positive and they must not be 
extremely large or small. In these cases, mirrors that reflect in $\lambda _{\text{min}}$ or $\lambda _{\text{max}}$,
respectively, will be obtained. Eq. (\ref{F2}) is formed by the average of
two functions of type $f_{1}$ with different powers. The function $f_{3}$
(Eq. (\ref{F3})) was designed so that the first and second additions
predominate the short and long wavelengths, respectively. The R$_{\text{ave}} 
\left(\lambda,\theta\right)$ of the structures is calculated in
the wavelength range from 350 to 1400 nm and from 0 to 90${{}^\circ}$ angle of 
incidence. The optimized parameters using a porosity contrast of $51/76\%$ are shown 
in Table 1 and in the supplementary information they appear for the porosity 
contrasts of $30/76\%$ and $42/76\%$.  
\begin{table}
\caption{ Design parameters obtained after the optimization of functions (Eqs. (\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
\includegraphics[width=\textwidth]
{F2TableOptimized.pdf}
\end{table}

According to the values shown in table I, the structure (named as ST-A) that has the
maximum average reflectance with the minimum thickness is the one designed
with the function $f_{3}$ (Eq. (\ref{F3})). Thus, the first and last periods
are tuned to 320 and 1400 nm, respectively. The complete distribution of the
periods is presented in Fig. \ref{Fig2}(a). 
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
		{F3OptimizedVis.pdf}
\end{center}
\caption{(a) Distribution of $\protect\lambda _{j}$ in the $j$-th period for
the design of the 63-period multilayer structure. (b) Mapping of the average
reflectance of the structures designed with different values{}of $%
\protect\alpha $ and $N_{p}$ parameters. It is verified that the parameters
obtained during the optimization are adequate ($\protect\alpha =1.23$ and $%
N_{p}=63$). (c) Mapping the calculated reflectance for non polarized light of the 
designed structure with the optimized values. (d) Comparison of reflectance spectra 
calculated and measured at different angles of incidence. The gray band indicates the
region in which the reflectance is greater than 95\%. Inset shows the
top view photograph of the synthesized structure.}
\label{Fig2}
\end{figure}
To verify that the values
obtained are optimal, in Fig. \ref{Fig2}(b), the average reflectances of the
photonic structures designed with different parameters are mapped and,
indeed, the values are in the area where R$_{\text{ave}}\left( \lambda
,\theta \right)$ is maximum. Here, the parameters $\lambda _{\text{min}}$, 
$\lambda _{\text{max}}$, $\beta$ and $A$ were adjusted, while $N_{p}$ and $\alpha $ 
varied from 30 to 200 periods and from 0.4 to 1.3, respectively. The calculated 
reflectance, R$\left( \lambda ,\theta \right) $, of the photonic structure is shown 
in Fig \ref{Fig2}(c). Here, the wavelength and incidence angle cover the ranges
from 350 to 1400 nm, and from 0${{}^\circ}$ to 90${{}^\circ}$, respectively. 
Calculations indicate that the structure has a localized omnidirectional band gap
from 1000 to 1200 nm, taken with a reflectance greater than 95$\%$. Due to 
experimental limitations, reflectance spectra for non polarized light are shown in all results.
In Fig. \ref{Fig2}(d), the calculated and measured reflectance is compared
at 10${{}^\circ}$, 20${{}^\circ}$, 30${{}^\circ}$, 40${{}^\circ}$, 50${{}^\circ}$ 
and 60${{}^\circ}$ of incidence. In this angular range, the structure has a 
quasi-omnidirectional band gap (R$\left(\lambda,\theta\right)>95\%$) located from 
980 to 1340 nm. The numerical and experimental spectral line shapes at different 
angles are in good agreement. For wavelengths greater than 700 nm and lying between 
10${{}^\circ}$ to 40${{}^\circ}$ of incidence angle, the difference in spectra is 
less than $5\%$. For angles of incidence greater than 40 degree, although their 
characteristics are similar, the measured spectrum demonstrates relatively less 
reflectance than calculated reflectance. This difference can be attributed, in part, 
to the scattering of light between each of the actual interfaces, which generally 
have some roughness \cite{Theiss1994,Chavez2020}.

Due to the absorptive nature of Si in the UV and visible region, it is relatively 
difficult to design porous silicon omnidirectional mirrors in that region.
However, in the IR region, it is relatively easy to obtain highly reflective
and even omnidirectional photonic structures over a wide range. Therefore,
the average reflectance was optimized using the function $f_{1}$ (Eq. (\ref{F1})) 
in the region of 850 to 3000 nm. It was found that the best value for 
$\alpha $ is 1.2 and the minimum thickness is 60.4 $\mu$m, distributed in
90 periods. The complete design of the structure (named as ST-B) is graphed in Fig. 
\ref{Fig3}(a). 
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F4OptimizedNIRPC.pdf}
\end{center}
\caption{(a) Distribution of $\protect\lambda _{j}$ in the $j$-th period
modulated by the optimization of the function $f_{1}$ for the design of the
multilayer structure of 90 periods. (b) Mapping of the average reflectance
of the structures designed with different values of the $\protect\alpha $
and $N_{p}$ parameters. The optimized parameters are $\protect\alpha =1.2$
and 90 periods. (c) Mapping the calculated reflectance of the designed
structure with the optimized values for non polarized light. (d) Comparison of 
reflectance spectra calculated and measured at different angles of incidence. The 
gray band indicates the region in which the reflectance is greater than 95$\%$. Inset
there is a photograph of the synthesized structure.}
\label{Fig3}
\end{figure}
In Fig \ref{Fig3}(b) the average reflectance of structures
designed with different values of $\alpha$ and $N_{p}$ is mapped. As in the
previous case, the optimized parameters are within the zone of maximum
average reflectance. The reflectance calculation shows that this structure
has a wide quasi-omnidirectional gap that goes from 850 to 3000 nm and from
0${{}^\circ}$ to 70${{}^\circ}$ of incidence; the corresponding contour plot is 
shown in Fig. \ref{Fig3}(c) and its average reflectance between 850-3000nm is 
greater than 95\%. The measured and calculated reflectance spectra have very 
similar characteristics as shown in Fig \ref{Fig3}(d).  The synthesized PS 
multilayered 1D photonic structure has a quasi omnidirectional (from 0${{}^\circ}$ 
to 60${{}^\circ}$) band gap of approximately 1800 nm. The difference
between the calculated and measured spectra at the longer wavelengths can be
attributed to a thickness gradient along the depth, which is more pronounced in
the lower layers due to the restricted diffusivity of the electrolyte
through the structure itself \cite{Negro2003,Vincent1993} and interface roughness.

\subsection{Photonic structure with sub-mirrors stacking}

Another technique to design Bragg mirrors in a wide range of the
electromagnetic spectrum is by stacking sub-mirrors at different
wavelengths \cite{Xifre20,DelRio2018,Agarwal2003}. Such grouping must meet the condition 
imposed by the dispersion relation, $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is 
the period, which corresponds to the actual thickness of the sub-mirror, $\pm K$ 
represents a 1D Bloch's vector corresponding to a wave that propagates along 
$z$-direction \cite{Mochan1987,Mochan1988,Perez2018}, and T$\text{r}$ denotes the 
trace. This equation is bounded by the minimum and maximum values that the cosine 
function can take. Furthermore, if  the value of $\left\vert \text{Tr}\left( 
M\right) \right\vert$ is $>2$, it indicates that this frequency will not 
be able to propagate through the structure.

The ideal stack of sub-mirrors would be that PBG of the $j$-th mirror begins 
at the edge of the PBG of the $j-1$-th mirror, until the desired interval has been covered. 
However, this arrangement does not give the maximum average reflectance due to the 
decrease in the reflectance at each intersection of the two PBGs. On the other hand, 
the number of periods of each sub-mirror is an important parameter due to its direct 
dependence on the magnitude and  width of  the photonic band gap.  As the structures 
were synthesized using porous silicon, it is essential to minimize the number of 
periods corresponding to the visible region sub-mirrors. Also, in the supplementary 
information we show the reflectance calculations for structures composed of sub 
mirrors with a constant number of periods, in these cases ODBMs are not obtained. 
For these reasons, the number of periods for each mirror was chosen as follows: for 
design wavelengths less than 500 nm ($\lambda_{D}<$500 nm), one period, for 500 
$<\lambda_{D}<$650 nm, two periods , for 650 $<\lambda_{D}<$800 nm, three, and for 
$\lambda_{D}>$ 800 nm, the number of periods was variable (Fig. \ref{Fig4}(a)). 
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F6OptimizedNIRSE.pdf}
\end{center}
\caption{(a) Diagram showing the distribution of sub-mirrors and the corresponding 
number of periods in a PS multilayer. (b) Maximization of the average reflectance as 
a function of the overlap photonic band gap for the structures formed by sub-mirrors 
with a fixed number of periods (3 and 4), and for structures with the design of (a) 
using 3 and 6 periods for the tuned sub-mirrors in $\lambda>800$ nm. (c) Mapping the
calculated reflectance of the designed structure with the optimized values for non 
polarized light. (d) Comparison of reflectance spectra calculated and measured at 
different angles of incidence. The gray band indicates the region in which the
reflectance is greater than 95$\%$. Inset shows the top view photograph of the
synthesized structure.}
\label{Fig4}
\end{figure}

Therefore, in this work the overlap percentage of the PBGs of the first and second 
mirror, second and third mirror, and so on, is also optimized. Fig \ref{Fig4}(b) 
shows the optimization results in terms of maximum average reflectance with respect 
to the PBG overlap at different sub-mirror periods, keeping them fixed (3, 4) or 
variable (1, 2  and 3) for $\lambda<500$(1 period), $500<\lambda<650$ nm (2 
periods), $650<\lambda<800$ nm (3 periods) and $\lambda>800$ (3, 6 periods). For 
example, the calculations corresponding to the reflectance spectra of the structures 
formed using sub-mirrors with constant periods (3 and 4) revealed a lower average 
reflectance as compared to the structure formed with variable periods. The 1D 
photonic structure with the highest average reflectance (named as ST-C)  is the one 
designed with variable periods and contemplates 6 periods for each sub-mirror in the 
NIR region. In the optimized structure designed for 400-3000 nm range, the photonic 
band gap overlap is around 78$\%$, thickness is 41.5 $\mu $m and the average 
reflectance is 95.3$\%$, when the  electromagnetic waves are incident from 
0${{}^\circ}$ to 89 ${{}^\circ}$. The optimized photonic structure is made up of 18 
sub-mirrors tuned to the following wavelengths 400, 460, 510, 570, 640, 720,810, 
910, 1020, 1150, 1290, 1450, 1630, 1830, 2060, 2320, 2610 and 2860 nm  with periods 
of 1 (400, 460 nm), 2(510, 570, 640 nm), 3 (720 nm) and 6 (810 nm and above).

The reflectance mapping shown in Fig \ref{Fig4}(c) reveals a quasi omnidirectional 
band gap from 950 to 2900 nm, taking into account 0${{}^\circ}$ to 60${{}^\circ}$ of 
incidence. It is also observed that at incidence angles $>$70${{}^\circ}$, for long 
wavelengths the reflectance decreases and has oscillations, which are attributed to 
the greater penetration of the electromagnetic field within the structure, as shown 
by Puente-D\'{\i}az, et al \cite{Puente2020}. Furthermore, in supplementary 
information we show the transfer matrix trace calculations as a function of the 
wavelength and the incidence angle for the ST-C photonic structure using the TE and 
TM polarization. In Fig \ref{Fig4}(d) the calculated and measured reflectance 
corresponding to the structure ST-C, at different angles of incidence is compared. 
Although, the quasi omnidirectional band gap of the synthesized structure is 
slightly less than that calculated (located from 950 to 2750 nm), the measured PBG 
is almost twice as compared to the recently reported similar structures 
(\cite{DelRio2018,Chavez2020}).

Finally, table 2 shows some porous silicon based ODBMs designed to operate in the
NIR region and the width of the omnidirectional band gap is compared with the 
structures analyzed in the present study. The table reveals that the porous silicon 
based structures ST-B and ST-C have the widest gap width, being 1.8 times greater 
than recently reported works.

\begin{table}[h!]
	\begin{center}
		\caption{Summary of the development in porous silicon based ODBMs designed in the NIR region.}
		\label{tab:table1}
		\begin{tabular}{c|c|c|c}
			\hline % <-- Toprule here
		\textbf{Reference}&\textbf{Year}&\textbf{ODBM range}&\textbf{ODBM width}\\	
			%\multicolumn{3}{c|}{\textbf{ODBM width}} \\ % <-- Combining two cells with alignment c| and content 12.			
			 & &(nm)&(nm)\\%&\textbf{ST-B}&\textbf{ST-C}\\
			\hline % <-- Midrule here
Bruyant, et al \cite{Bruyant2003}. & 2003 & 1100-1440 & 340 \\ 
Xifre-P\'{e}rez, et al \cite{Xifre2005}. & 2004 & 1297-1615 & 318\\ 
Estevez, et al \cite{Estevez2009}. & 2009 & 950-1456 & 506 \\ 
Chavez, et al \cite{Chavez2020}. & 2020 & 1000-2000 & 1000 \\ 
			\hline % <-- Bottomrule here
			\begin{tabular}{c|c}
					&ST-A\\
					This article&ST-B\\
				&ST-C\\
			\end{tabular}&
			\begin{tabular}{c}
			\\
			\\
			\\
			\end{tabular}&
		\begin{tabular}{c}
			980-1340\\
			980-2780\\
			950-2750\\
		\end{tabular}&
		\begin{tabular}{c}
			360\\
			1800\\
			1800\\
		\end{tabular}\\
		\hline % <-- Bottomrule here
	\end{tabular}
	\end{center}
\end{table}

\section{Conclusion}

We have demonstrated the formation of highly reflective PS multilayer photonic 
structures optimized using two types of design techniques for maximal reflectance 
and minimal thickness in the NIR region. With \textit{chirped}-type Bragg mirrors, 
two regions of the electromagnetic spectrum were analyzed. The first region (350nm - 
1400 nm), optimized through an increasing function resulted in an average 
reflectance $>85\%$ with the quasi omnidirectional PBG of 360 nm centered at 1160 nm 
(980-1340 nm) for the angular range 0-60${{}^\circ}$ and more than 50$\%$ of 
reflectance from 550-980nm. The second structure was designed for 850-3000 nm 
wavelength range and the synthesized structure with optimized parameters resulted in 
the average reflectance of $~91\%$ with q-OD bandgap from 980 to 2780 nm and a 
thickness of 60.4 $\mu$m. The other design technique consisting of sub-mirrors 
stacks (designed at different wavelengths), was optimized for maximum average 
reflectance with respect to the percentage overlap of the PBG for each sub-mirror. A 
multilayer structure using the optimized parameters with sub-mirrors stack method 
was obtained with the average reflectance of $~95\%$ and a thickness of 41.5 $\mu$m. 
Furthermore, this structure revealed a 1800 nm q-OD PBG, centered at 1850 nm, in 
angular range 0-60${{}^\circ}$. Therefore, this second technique was found to be 
better due to the decreased thickness (by a factor of $~1.5$) of the framework and 
increased average reflectance. Additionally, the analysis techniques developed here 
can be used to optimize reflectance with other refractive index contrasts in PS 
multilayers or different other systems composed of other types of materials. Such 
proposed structures could be used as mirrors for solar concentrators, flat focusing reflectors,
 thermal regulators, or, if defects are included, as filters or remote chemical/biosensors 
with a wide angular independent response.

\section*{Acknowledgments}
This work was partially supported by Consejo Nacional de Ciencia y Tecnolog\'{i}a through grant No. \textbf{256243} and C\'{a}tedras Conacyt program 1577.
%\end{acknowledgments}

\begin{thebibliography}{99}
\bibitem{Joannopoulos2008} J. D. Joannopoulos et al., Photonic Crystals:
Molding the Flow of Light, Princeton University Press, New Jersey (2008).

\bibitem{Goyal2018} A. K. Goyal et al., Porous photonic crystal structure
for sensing applications,\ \textit{J. Nanophotonics }12(\textbf{4}), 040501
(2018).

\bibitem{Lopez2013} C. L\'{o}pez, Materials aspects of photonic crystals, 
\textit{Adv. Mater.} \textbf{15}, 1679--1704 (2013).

\bibitem{Masaya2010} N. Masaya, Manipulating light with strongly modulated
photonic crystals, \textit{Rep. Prog.Phys.} \textbf{73} 096501, (2010).

\bibitem{Kumar2020} A. K. Goyal, A. Kumar, Recent advances and progresses in
photonic devices for passive radiative cooling application: a review, 
\textit{J. Nanophoton}. 14(\textbf{3}) 030901 (2020)
https://doi.org/10.1117/1.JNP.14.030901

\bibitem{Zipock1997} R. Szip\"{o}cs and A. Koh\'{a}zi-Kis, Theory and design
of chirped dielectric mirrors, \textit{Appl. Phys. B }\textbf{65}, 115
(1997), doi:10.1007/s003400050258

\bibitem{Xifre2009} Xifre-Perez, Appl Phys B, 95: 169-172 (2009)

\bibitem{Chen1999} K.M. Chen, A.W. Sparks, H.-C. Luan, D.R. Lim, K.Wada,
L.C. Kimerling, SiO2/TiO2 omnidirectional reflector andmicrocavity resonator
via the sol--gelmethod, \textit{Appl. Phys. Lett. 75}  3805--3807, (1999).

\bibitem{Park2003} Y. Park, Y.-G. Roh, C.-O. Cho, H. Jeon, M.G. Sung,
J.C.Woo, GaAs-based near-infrared omnidirectional reflector, \textit{Appl.
Phys. Lett}. \textbf{82} (2003) 2770--2772.

\bibitem{DeCorby2005} R. G. DeCorby, H. T. Nguyen, P. K. Dwivedi, and T. J.
Clement, Planar omnidirectional reflectors in chalcogenide glass and
polymer, \textit{Opt. Express }13, 6228-6233 (2005)

\bibitem{Jena2016} S. Jena, R.B. Tokas, S. Tripathi, K.D. Rao, D.V. Udupa,
S. Thakur, N.K. Sahoo Influence of oxygen partial pressure on
microstructure, optical properties, residual stress and laser induced damage
threshold of amorphous HfO2 thin films \textit{Journal of Alloys and
Compounds}, Volume 771, 2019, pp. 373-381

\bibitem{Xifre2015} Xifr\'{e}-P\'{e}rez E., Ferr\'{e}-Borrull J., Pallar\'{e}%
s J., and Marsal L. F. Methods, Properties and Applications of Porous
Silicon, \textit{Electrochemically Engineered Nanoporous Materials},
Springer Series in Materials Science 220, Ch.2, (2015).

\bibitem{Pavesi2000} Bisi O., Stefano Ossicini, and Pavesi L. Porous
silicon: a quantum sponge structure for silicon based optoelectronics, 
\textit{Surface Science Reports} \textbf{38} 1-126, (2000).

\bibitem{Estevez2009} Estevez J. O., Arriaga J., M\'{e}ndez Blas A., and
Agarwal V. Enlargement of omnidirectional photonic band gap in porous silicon
dielectric mirrors with a Gaussian profile refractive index. \textit{Applied
Physics Lettesrs}, \textbf{94}, 061914, (2009).

\bibitem{Ariza2014} Ariza-Flores D., P\'{e}rez-Huerta J.S., Kumar Y.,
Encinas A., and Agarwal V. Design and optimization of antireflecting
coatings from nanostructured porous silicon dielectric multilayers. \textit{%
Solar Energy Materials \& Solar Cells}, \textbf{123} 144-149, (2014).

\bibitem{Giusseppe2011} Ruminski A.M., Barillaro G., Chaffin C., and Sailor
M. J., Internally Referenced Remote Sensors for HF and Cl2 Using Reactive
Porous Silicon Photonic Crystals. \textit{Adv. Funct. Mater.}, \textbf{21}:
1511-1525, (2011).

\bibitem{Agarwal2018} Karthik T.V.K., Martinez L., and Agarwal V. Porous
silicon ZnO/SnO$_{2}$ structures for CO$_{2}$ detection. \textit{Journal of
Allows and Compounds}, \textbf{731} 853-863, (2018).

\bibitem{Hussel1997} C.P. Hussell, R.V. Ramaswamy, \textit{IEEE Photonics
Technol. Lett.} \textbf{9}, 636, (1997).

\bibitem{Antunez2014} Antunez E.E., Estevez J.O., Campos J., Basurto-Pensado
M.A., and V.Agarwal V. Formation of photoluminescent n-type macroporous
silicon: Effect of magnetic field and lateral electric potential. \textit{%
Physica B} \textbf{453} 34--39, (2014).

\bibitem{Kozar2017} A. V. Kozar, S. V. Marchenko and P. Y. Shestakov, "Focusing and defocusing of reflected light beams from chirped dielectric layered structure," 2017 Days on Diffraction (DD), St. Petersburg, pp. 200-204, (2017).

\bibitem{Cheng2018} Yu-Chieh Cheng and  Kestutis Staliunas, Near-field flat focusing mirrors, Applied Physics Reviews 5, 011101 (2018).

\bibitem{Jimenez2020} Jimen\'{e}z-Vivanco M. R., Garc\'{\i}a G., Carrillo
J., Agarwal V., D\'{\i}az-Becerril T., Doti R., Faubert J., and Lugo J. E.
Porous Si-SiO2 based UV Microcavities. \textit{Scientific Reports} \textbf{10%
}: 2220, (2020).

\bibitem{Ariza2012} Ariza-Flores A. D., Gaggero-Sager L. M., and Agarwal V.
White metal like omnidirectional mirror from porous silicon dielectric
multilayers. \textit{Appl. Phys. Lett.}, 101(\textbf{3}):031119, (2012).

\bibitem{Bruyant2003} Bruyant A., L erondel G., Reece P. J., and Gal M.
All-silicon omnidirectional mirrors based on one-dimensional photonic
crystals. \textit{Appl. Phys. Lett.}, 82(\textbf{19}):3227-3229, (2003).

\bibitem{DelRio2018} Estrada-Wiese, D., del R\'{\i}o-Chanona, E.A. \& del R%
\'{\i}o, J.A. Stochastic optimization of broadband reflecting photonic
structures. \textit{Sci Rep} \textbf{8}, 1193 (2018).

\bibitem{Chavez2020} B. A. Chavez-Castillo, J. S. P\'{e}rez-Huerta, J.
Madrigal-Melchor, S. Amador-Alvarado, I. A. Sustaita-Torres, V. Agarwal, and
D. Ariza-Flores, A wide band porous silicon omnidirectional mirror for the
near infrared range, \textit{Journal of Applied Physics}, \textbf{127}, 20,
(2020).

\bibitem{Mochan1987} Moch\'{a}n W. L., del Castillo-Mussot M., and Barrera
Rub\'{e}n G. Effect of plasma waves on the optical properties of
metal-insulator superlattices. \textit{Phys. Rev. B}, 35(\textbf{3}%
):1088-1098, (1987).

\bibitem{Ortiz2020} Leandro L. Missoni, Guillermo P. Ortiz, Mar\'{i}a Luz
Mart\'{\i}nez Ricci, Victor J. Toranzos, W. Luis Moch\'{a}n, Rough 1D
photonic crystals: A transfer matrix approach, \textit{Optical Materials}, 
\textbf{109}, 110012 (2020).

\bibitem{Puente2020} Luis Eduardo Puente-D\'{i}az, Victor
Castillo-Gallardo, Guillermo P. Ortiz, Jos\'{e} Samuel P\'{e}rez-Huerta, H%
\'{e}ctor P\'{e}rez-Aguilar, Vivechana Agarwal, W. Luis Moch\'{a}n, Stable
calculation of optical properties of large non-periodic dissipative
multilayered systems, \textit{Superlattices and Microstructures}, \textbf{145%
}, 106629, (2020).

\bibitem{Pap2006} Pap Andrea Edit, Kord\'{a}s Kriszti\'{a}n, V\"{a}h\"{a}kangas 
Jouko, Uusim\"{a}ki Antti, Lepp\"{a}vuori Seppo, Pilon Laurent, and Szatm\'{a}ri 
S\'{a}ndor. Optical properties of porous silicon. part iii: Comparison of 
experimental and theoretical results. \textit{Optical Materials}, 28(5):506-513, (2006).

\bibitem{Estrada2018} D. Estrada-Wiese and J. A. del R\'{\i}o, Refractive index evaluation of porous silicon using Bragg reflectors. \textit{Revista mexicana de f\'{\i}sica}, \textbf{64}(1), 72-81, (2018).

\bibitem{minuit} James F. and Winkler M. Minuit user's guide. CERN, Geneva,
(2004).

\bibitem{Canham90} Canham L. T. Silicon quantum wire array fabrication by
electrochemical and chemical dissolution of wafers. \textit{Appl. Phys. Lett.%
}, 57(\textbf{10}):1046-1048, (1990).

\bibitem{Escorcia07} Escorcia J. and Agarwal V. E ect of duty cycle and
frequency on the morphology of porous silicon formed by alternating square
pulse anodic etching. \textit{Phys. Status Solidi (c)}, 4(\textbf{6}%
):2039-2043, (2007).

\bibitem{Ariza2011} A. David Ariza-Flores, L M Gaggero-Sager and V Agarwal,
Effect of interface gradient on the optical properties of multilayered porous 
silicon photonic structures, J Phys D: Appl Phys, 44(15), 155102 (2011)

\bibitem{Brugeman2006} Andrea Edit Pap, Kriszti an Kord as, Jouko
Vahakangas, Antti Uusimaki, Seppo Leppavuori, Laurent Pilon, and Sandor
Szatmari. Optical properties of porous silicon. part iii: Comparison of
experimental and theoretical results. \textit{Optical Materials}, 28(\textbf{%
5}):506-513, (2006).

\bibitem{Theiss1994} W. Thei\ss , R. Arens-Fischer, M. Arntzen, M.G. Berger,
S. Frohnhoff, S. Hilbrich, andWernke M. Probing optical transitions in
porous silicon by reflectance spectroscopy in the near infrared, visible and
UV. \textit{MRS Proceedings}, 358:435, (1994).

\bibitem{Negro2003} L. Dal Negro, C. J. Oton, Z. Gaburro, L. Pavesi, P.
Johnson, A. Lagendijk, R. Righini, M. Colocci, and D. S. Wiersma. Light
Transport through the Band-Edge States of Fibonacci Quasicrystals. \textit{%
	Phys. Rev. Lett}. \textbf{90}, 055501, (2003).

\bibitem{Vincent1993} G. Vincent. Optical properties of porous silicon
superlattices \textit{Appl. Phys. Lett}. \textbf{64}, 2367 (1994).

\bibitem{Agarwal2003} V. Agarwal and J. A. del R\'{\i}o, Tailoring the 
photonic band gap of a porous silicon dielectric mirror, Applied Physics 
Letters \textbf{82}, 1512 (2003).

\bibitem{Mochan1988} Moch\'{a}n W. L. and del Castillo-Mussot M. Optics of
multilayered conducting systems: Normal modes of periodic superlattices. 
\textit{Phys. Rev. B}, 37(\textbf{12}):6763-6771, (1988).

\bibitem{Perez2018} P\'{e}rez-Huerta J. S., Ariza-Flores D., Castro-Garc%
\'{\i}a R., Moch\'{a}n W. L., Ortiz G. P., and Agarwall V. Reflectivity of
1D photonic crystals: A comparison of computational schemes with
experimental results. \textit{Int. J. Mod. Phys. B}, 32(\textbf{11}%
):1850136, (2018).

\bibitem{Xifre2005} E. Xifr\'{e}-P\'{e}rez, L. Marsal, J. Pallar\'{e}s, and
J. Ferr\'{e}-Borrull, \textquotedblleft Porous silicon mirrors with enlarged
omnidirectional band gap,\textquotedblright\ \textit{J. Appl. Phys.} \textbf{%
97}, 064503 (2005).

\bibitem{Estevez2005} Estevez J. O., Arriaga J., M\'{e}ndez Blas A., and
Agarwal V. Omnidirectional photonic band gaps in porous silicon based mirrors
with a Gaussian profile refractive index. \textit{Appl. Phys. Lett.} \textbf{%
93}:191915, (2005).

\end{thebibliography}

\end{document}

### 2020-12-06 PaperVictor.tex
Remove end of lines
Add Acknowldgment to dgapa.
Revise abstract

@@
 \usepackage{xcolor}
+\usepackage{braket}
 \newif{\ifmover}
@@
 Porous silicon (PS) is a very versatile material for developing optical
-devices based on multilayer structures, since high and low porosity layers
-can be synthesized by simple electrochemical technique. We report the
-maximization of average reflectance (R$_{\text{prom}}\left(\lambda,\theta%
-\right)$) with minimum possible thickness of PS-based mirrors with different
-porosity contrasts. Optimization is performed in two regions (Visible and
-NIR) of the electromagnetic spectrum. We employ two techniques to design the
-mirrors: \textit{chirped} structures and the \textit{stacking} of sub-mirrors. The
-chirped structures were found to be relatively more suitable for obtaining
-highly reflectivity in the visible range, while the second type of
-structure was more effective for obtaining high reflectivity in the IR
-region. Some of the optimized omnidirectional structures with less than 100
-periods have been designed and experimentally demonstrated in a wide
-spectral range.
+devices based on multilayered structures, since high and low porosity layers
+can be synthesized by a simple electrochemical technique. We
+maximize the reflectance ($\braket{R}$ \notaL{El promedio no depende
+  de lambda ni theta, y prom es castellano} averaged over a wide wavelength
+and angular range  of PS-based mirrors with different
+porosity contrasts searching for a minimum thickness. Optimization is
+performed in the visible (Vis) and near infrarred (NIR) regions of the
+electromagnetic spectrum. We design the mirrors using \textit{chirped}
+structures and \textit{stacking} sub-mirrors. The
+chirped structures were better suited for the Vis, and the stacked
+sub-mirrors for the NIR regions. We design, fabricate and test some
+optimized omnidirectional structures with less than 100
+periods.
 \end{abstract}
@@
 potential applications in optoelectronics, optical telecommunications and computing,
-laser technology \cite{Lopez2013,Masaya2010}, and radiative cooling applications 
+laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
 \cite{Kumar2020}. The simplest 1D PC is composed of alternating high $\left(
@@
 respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm
-wavelength. Furthermore, Jena et al., \cite{Jena2016}
+wavelength. Furthermore, Jena et al., \cite{Jena2019}
 used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
@@
 resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
-\cite{Canham90,Escorcia07}. Electrochemical anodization process was
+\cite{Canham1990,Escorcia2007}. Electrochemical anodization process was
 performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
@@
 \section*{Acknowledgments}
-This work was partially supported by Consejo Nacional de Ciencia y Tecnolog\'{i}a through grant No. \textbf{256243} and C\'{a}tedras Conacyt program 1577.
+This work was partially supported by Consejo Nacional de Ciencia y
+Tecnolog\'{i}a through grant No. \textbf{256243} and C\'{a}tedras
+Conacyt program 1577, and by DGAPA-PAPIIT UNAM under grant IN111119.
 %\end{acknowledgments}
+
+\bibliographystyle{unsrt}
+\bibliography{Bibliografia}
+\end{document}
 
@@
 
-\bibitem{Lopez2013} C. L\'{o}pez, Materials aspects of photonic crystals, 
-\textit{Adv. Mater.} \textbf{15}, 1679--1704 (2013).
+\bibitem{Lopez2003} C. L\'{o}pez, Materials aspects of photonic crystals,
+\textit{Adv. Mater.} \textbf{15}, 1679--1704 (2003).
 
@@
 
-\bibitem{Jena2016} S. Jena, R.B. Tokas, S. Tripathi, K.D. Rao, D.V. Udupa,
+\bibitem{Jena2019} S. Jena, R.B. Tokas, S. Tripathi, K.D. Rao, D.V. Udupa,
 S. Thakur, N.K. Sahoo Influence of oxygen partial pressure on
@@
 
-\bibitem{Canham90} Canham L. T. Silicon quantum wire array fabrication by
+\bibitem{Canham1990} Canham L. T. Silicon quantum wire array fabrication by
 electrochemical and chemical dissolution of wafers. \textit{Appl. Phys. Lett.%
@@
 
-\bibitem{Escorcia07} Escorcia J. and Agarwal V. E ect of duty cycle and
+\bibitem{Escorcia2007} Escorcia J. and Agarwal V. E ect of duty cycle and
 frequency on the morphology of porous silicon formed by alternating square

### 2020-12-07 PaperVictor.tex
Agregue un espacio para hacer pruebas
En PaperVictor.tex aplique el comando dos2unix, actualice a mi última versión, modifique PC a PhC  y quite una referencia duplicada. En Bibliografia.bib quite la referencia duplicada (Bruggeman2006 y Pap2006) y corregí el nombre de los compuestos involucrados en las referencias (i. e., zno a ZnO)

@@
 			victor1\_1@hotmail.com}}}
-\author[1,2,3]{Luis Eduardo Puente-Dìaz}
+\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
 \author[4]{D. Ariza-Flores}
-\author[3]{Hector Pérez-Aguilar}
-\author[2]{W. Luis Mochán\thanks{email: {\tt
+\author[3]{Hector P\'{e}rez-Aguilar}
+\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
 			mochan@fis.unam.mx}}}
@@
 			vagarwal@uaem.mx}}}
-\affil[1]{Centro de Investigación en Ingenierìa y Ciencias Aplicadas,
-	Universidad del Estado de Morelos, Av. Universidad 1001
-	Col. Chamilpa, Cuernavaca, Morelos 62209, México.}
-\affil[2]{Instituto de Ciencias Fìsicas, Universidad Nacional Autónoma
-	de México, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca,
-	Morelos, México.}
-\affil[3]{Facultad de Ciencias Fìsico Matemáticas,
-	Universidad Michoacana de San Nicolás de Hidalgo, Av. Francisco
-	J. Múgica S/N 58030, Morelia, Mich., México.}
-\affil[4]{Conacyt-Universidad Autónoma de San Luis Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potosì, S.L.P., 78210, México.}
+\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y 
+Ciencias Aplicadas, Universidad del Estado de Morelos, Av. 
+Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209, 
+M\'{e}xico.}
+\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad 
+Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N, 
+Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
+\affil[3]{Facultad de Ciencias Fìsico Matem\'{a}ticas, 
+Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av. 
+Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
+\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis 
+Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i}, 
+S.L.P., 78210, M\'{e}xico.}
 %\date{{\small {\today}}}
@@
 can be synthesized by a simple electrochemical technique. We
-maximize the reflectance ($\braket{R}$ \notaL{El promedio no depende
+maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
   de lambda ni theta, y prom es castellano} averaged over a wide wavelength
@@
 performed in the visible (Vis) and near infrarred (NIR) regions of the
-electromagnetic spectrum. We design the mirrors using \textit{chirped}
+electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
 structures and \textit{stacking} sub-mirrors. The
@@
 
-Photonic crystal (PC)-based structures are extensively investigated due
+Photonic crystal (PhC)-based structures are extensively investigated due
 to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
@@
 crystal, their propagation will be limited by photonic band gaps (PBGs)
-where transmission states are forbidden. The PC  shows a
+where transmission states are forbidden. The PhC  shows a
 PBG corresponding to the electromagnetic modes which are not allowed to propagate
@@
 reflection wavelength. These properties are widely used to design various
-one-dimensional (1D) and two-dimensional (2D) PCs for its
+one-dimensional (1D) and two-dimensional (2D) PhCs for its
 potential applications in optoelectronics, optical telecommunications and computing,
 laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
-\cite{Kumar2020}. The simplest 1D PC is composed of alternating high $\left(
+\cite{Kumar2020}. The simplest 1DPhC is composed of alternating high $\left(
 n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror,
 BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
-n_{H}d_{H}=n_{L}d_{L}=\lambda _{0}/4$, at some operating wavelength $\lambda
-_{0}$ (center wavelength) to obtain a certain
+n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$, at some operating wavelength $\lambda_{0}$ 
+(center wavelength) to obtain a certain
 omnidirectional band gap. As the gap depends on the contrast of the
@@
 _{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
-layers) to generate 1DPC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
+layers) to generate 1DPhC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
 592 to 668 nm. However, these techniques are expensive and
-require sophisticated equipment and long fabrication time. Using porous silicon (PS)
+require sophisticated equipment and long fabrication time. Using PS
 is an alternative, as PS is typically fabricated by simple electrochemical etching of
@@
 density and hence modifies the refractive index of the resulting PS. This
-fact opens the possibility of designing 1DPC with PS, which seeks to
+fact opens the possibility of designing 1DPhC with PS, which seeks to
 control the propagation of light in a dielectric medium. The low cost and
@@
 multilayer systems, it is common to employ the transfer matrix method (put the
-reference). Under the consideration that the system only varies along the $z$ axis, the transfer matrix is $M\left(z_{2},z_{1}\right)$
+reference). Under the consideration that the system only varies along the $z$ axis, the 
+transfer matrix is $M\left(z_{2},z_{1}\right)$
 a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
@@
 \end{equation*}%
-Many equivalent formulations have been proposed to obtain $M$ \cite%
-{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
+Many equivalent formulations have been proposed to obtain $M$ 
+\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
 to calculate the reflectance of large multilayer systems proposed by Puente-D%
-\'{\i}az, et al \cite{Puente2020}, since we need a reliable and stable tool
+\'{\i}az, et al. \cite{Puente2020}, since we need a reliable and stable tool
 to design an optimized structure through a minimization procedure that
@@
 dissolving the already formed porous silicon layer ($m_{3}$), to calculate
-the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Brugeman2006}. Etching
+the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}. Etching
 rate of PS was obtained by re-synthetizing individual layers under similar
-conditions and measuring their thicknesses through scanning electron
-microscopy (SEM). The absolute reflectivity measurements were carried out
+conditions and measuring their thicknesses through SEM (Scanning Electron
+Microscopy). The absolute reflectivity measurements were carried out
 with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
@@
 spectra at different incidence angles in the regions of interest. In the first
-subsection, the design and optimization of R$_{\text{ave}}
-\left(\lambda,\theta\right)$ of \textit{chirped}  photonic structures is presented,
-and next subsection the design of the structure is analyzed through sub-mirrors
-stacks.
+subsection, the design and optimization of R$_{\text{ave}}$ of \textit{chirped}  
+photonic structures is presented, and next subsection the design of the structure is 
+analyzed through sub-mirrors stacks.
 
@@
 \end{equation}%
-where $\lambda _{\min }$, $\lambda _{\max }$ and $\lambda _{j}$ correspond
+where $\lambda_{\min }$, $\lambda_{\max }$ and $\lambda_{j}$ correspond
 to the minimum, maximum, and design wavelengths to which the $j$-th period
@@
 f_{1}\left( x\right) =x^{\alpha },  \label{F1}
-\end{equation}%
+\end{equation}
 \begin{equation}
@@
 \label{F2}
-\end{equation}%
+\end{equation}
 and%
@@
 f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
-\end{equation}%
-where $\alpha $, $\beta $ and $A$ are parameters to optimize. The function
+\end{equation}
+where $\alpha$, $\beta$ and $A$ are parameters to optimize. The function
 $f_{1}$ (Eq. (\ref {F1})) represents the simplest profiles. The restrictions
 for the values $\alpha$ are that they must be positive and they must not be
-extremely large or small. In these cases, mirrors that reflect in $\lambda _{\text{min}}$ or $\lambda _{\text{max}}$,
-respectively, will be obtained. Eq. (\ref{F2}) is formed by the average of
-two functions of type $f_{1}$ with different powers. The function $f_{3}$
-(Eq. (\ref{F3})) was designed so that the first and second additions
-predominate the short and long wavelengths, respectively. The R$_{\text{ave}}
-\left(\lambda,\theta\right)$ of the structures is calculated in
+extremely large or small. In these cases, mirrors that reflect in 
+$\lambda_{\text{min}}$ or $\lambda _{\text{max}}$, respectively, will be obtained. Eq. 
+(\ref{F2}) is formed by the average of two functions of type $f_{1}$ with different 
+powers. The function $f_{3}$ (Eq. (\ref{F3})) was designed so that the first and second 
+additions predominate the short and long wavelengths, respectively. The 
+R$_{\text{ave}}$ of the structures is calculated in
 the wavelength range from 350 to 1400 nm and from 0 to 90${{}^\circ}$ angle of
@@
 \begin{table}
-\caption{ Design parameters obtained after the optimization of functions (Eqs. (\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
+\caption{ Design parameters obtained after the optimization of functions (Eqs. 
+(\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
 \includegraphics[width=\textwidth]
@@
 \end{center}
-\caption{(a) Distribution of $\protect\lambda _{j}$ in the $j$-th period for
+\caption{(a) Distribution of $\protect\lambda_{j}$ in the $j$-th period for
 the design of the 63-period multilayer structure. (b) Mapping of the average
@@
 \end{figure}
-To verify that the values
-obtained are optimal, in Fig. \ref{Fig2}(b), the average reflectances of the
-photonic structures designed with different parameters are mapped and,
-indeed, the values are in the area where R$_{\text{ave}}\left( \lambda
-,\theta \right)$ is maximum. Here, the parameters $\lambda _{\text{min}}$,
-$\lambda _{\text{max}}$, $\beta$ and $A$ were adjusted, while $N_{p}$ and $\alpha $
-varied from 30 to 200 periods and from 0.4 to 1.3, respectively. The calculated
-reflectance, R$\left( \lambda ,\theta \right) $, of the photonic structure is shown
-in Fig \ref{Fig2}(c). Here, the wavelength and incidence angle cover the ranges
-from 350 to 1400 nm, and from 0${{}^\circ}$ to 90${{}^\circ}$, respectively.
-Calculations indicate that the structure has a localized omnidirectional band gap
-from 1000 to 1200 nm, taken with a reflectance greater than 95$\%$. Due to
-experimental limitations, reflectance spectra for non polarized light are shown in all results.
-In Fig. \ref{Fig2}(d), the calculated and measured reflectance is compared
+To verify that the values obtained are optimal, in Fig. \ref{Fig2}(b), the average 
+reflectances of the photonic structures designed with different parameters are mapped 
+and, indeed, the values are in the area where R$_{\text{ave}}$ is maximum. Here, the 
+parameters $\lambda_{\text{min}}$, $\lambda_{\text{max}}$, $\beta$ and $A$ were 
+adjusted, while $N_{p}$ and $\alpha$ varied from 30 to 200 periods and from 0.4 to 1.3, 
+respectively. The calculated reflectance, R$\left( \lambda ,\theta \right) $, of the 
+photonic structure is shown in Fig \ref{Fig2}(c). Here, the wavelength and incidence 
+angle cover the ranges from 350 to 1400 nm, and from 0${{}^\circ}$ to 90${{}^\circ}$, 
+respectively. Calculations indicate that the structure has a localized omnidirectional 
+band gap from 1000 to 1200 nm, taken with a reflectance greater than 95$\%$. Due to
+experimental limitations, reflectance spectra for non polarized light are shown in all results. In Fig. \ref{Fig2}(d), the calculated and measured reflectance is compared
 at 10${{}^\circ}$, 20${{}^\circ}$, 30${{}^\circ}$, 40${{}^\circ}$, 50${{}^\circ}$
@@
 \end{figure}
+
 In Fig \ref{Fig3}(b) the average reflectance of structures
@@
 0${{}^\circ}$ to 70${{}^\circ}$ of incidence; the corresponding contour plot is
-shown in Fig. \ref{Fig3}(c) and its average reflectance between 850-3000nm is
+shown in Fig. \ref{Fig3}(c) and its average reflectance between $850-3000$ nm is
 greater than 95\%. The measured and calculated reflectance spectra have very
@@
 electromagnetic spectrum is by stacking sub-mirrors at different
-wavelengths \cite{Xifre20,DelRio2018,Agarwal2003}. Such grouping must meet the condition
+wavelengths \cite{DelRio2018,Agarwal2003}. Such grouping must meet the condition
 imposed by the dispersion relation, $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is
@@
 The ideal stack of sub-mirrors would be that PBG of the $j$-th mirror begins
-at the edge of the PBG of the $j-1$-th mirror, until the desired interval has been covered.
-However, this arrangement does not give the maximum average reflectance due to the
-decrease in the reflectance at each intersection of the two PBGs. On the other hand,
+at the edge of the PBG of the $j-1$-th mirror, until the desired interval has been 
+covered. However, this arrangement does not give the maximum average reflectance due to 
+the decrease in the reflectance at each intersection of the two PBGs. On the other hand,
 the number of periods of each sub-mirror is an important parameter due to its direct
@@
 		\textbf{Reference}&\textbf{Year}&\textbf{ODBM range}&\textbf{ODBM width}\\
-			%\multicolumn{3}{c|}{\textbf{ODBM width}} \\ % <-- Combining two cells with alignment c| and content 12.
 			 & &(nm)&(nm)\\%&\textbf{ST-B}&\textbf{ST-C}\\
@@
 multilayers or different other systems composed of other types of materials. Such
-proposed structures could be used as mirrors for solar concentrators, flat focusing reflectors,
- thermal regulators, or, if defects are included, as filters or remote chemical/biosensors
-with a wide angular independent response.
+proposed structures could be used as mirrors for solar concentrators, flat focusing 
+reflectors, thermal regulators, or, if defects are included, as filters or remote 
+chemical/biosensors with a wide angular independent response.
 
@@
 \end{document}
-
-\begin{thebibliography}{99}
-\bibitem{Joannopoulos2008} J. D. Joannopoulos et al., Photonic Crystals:
-Molding the Flow of Light, Princeton University Press, New Jersey (2008).
-
-\bibitem{Goyal2018} A. K. Goyal et al., Porous photonic crystal structure
-for sensing applications,\ \textit{J. Nanophotonics }12(\textbf{4}), 040501
-(2018).
-
-\bibitem{Lopez2003} C. L\'{o}pez, Materials aspects of photonic crystals,
-\textit{Adv. Mater.} \textbf{15}, 1679--1704 (2003).
-
-\bibitem{Masaya2010} N. Masaya, Manipulating light with strongly modulated
-photonic crystals, \textit{Rep. Prog.Phys.} \textbf{73} 096501, (2010).
-
-\bibitem{Kumar2020} A. K. Goyal, A. Kumar, Recent advances and progresses in
-photonic devices for passive radiative cooling application: a review,
-\textit{J. Nanophoton}. 14(\textbf{3}) 030901 (2020)
-https://doi.org/10.1117/1.JNP.14.030901
-
-\bibitem{Zipock1997} R. Szip\"{o}cs and A. Koh\'{a}zi-Kis, Theory and design
-of chirped dielectric mirrors, \textit{Appl. Phys. B }\textbf{65}, 115
-(1997), doi:10.1007/s003400050258
-
-\bibitem{Xifre2009} Xifre-Perez, Appl Phys B, 95: 169-172 (2009)
-
-\bibitem{Chen1999} K.M. Chen, A.W. Sparks, H.-C. Luan, D.R. Lim, K.Wada,
-L.C. Kimerling, SiO2/TiO2 omnidirectional reflector andmicrocavity resonator
-via the sol--gelmethod, \textit{Appl. Phys. Lett. 75}  3805--3807, (1999).
-
-\bibitem{Park2003} Y. Park, Y.-G. Roh, C.-O. Cho, H. Jeon, M.G. Sung,
-J.C.Woo, GaAs-based near-infrared omnidirectional reflector, \textit{Appl.
-Phys. Lett}. \textbf{82} (2003) 2770--2772.
-
-\bibitem{DeCorby2005} R. G. DeCorby, H. T. Nguyen, P. K. Dwivedi, and T. J.
-Clement, Planar omnidirectional reflectors in chalcogenide glass and
-polymer, \textit{Opt. Express }13, 6228-6233 (2005)
-
-\bibitem{Jena2019} S. Jena, R.B. Tokas, S. Tripathi, K.D. Rao, D.V. Udupa,
-S. Thakur, N.K. Sahoo Influence of oxygen partial pressure on
-microstructure, optical properties, residual stress and laser induced damage
-threshold of amorphous HfO2 thin films \textit{Journal of Alloys and
-Compounds}, Volume 771, 2019, pp. 373-381
-
-\bibitem{Xifre2015} Xifr\'{e}-P\'{e}rez E., Ferr\'{e}-Borrull J., Pallar\'{e}%
-s J., and Marsal L. F. Methods, Properties and Applications of Porous
-Silicon, \textit{Electrochemically Engineered Nanoporous Materials},
-Springer Series in Materials Science 220, Ch.2, (2015).
-
-\bibitem{Pavesi2000} Bisi O., Stefano Ossicini, and Pavesi L. Porous
-silicon: a quantum sponge structure for silicon based optoelectronics,
-\textit{Surface Science Reports} \textbf{38} 1-126, (2000).
-
-\bibitem{Estevez2009} Estevez J. O., Arriaga J., M\'{e}ndez Blas A., and
-Agarwal V. Enlargement of omnidirectional photonic band gap in porous silicon
-dielectric mirrors with a Gaussian profile refractive index. \textit{Applied
-Physics Lettesrs}, \textbf{94}, 061914, (2009).
-
-\bibitem{Ariza2014} Ariza-Flores D., P\'{e}rez-Huerta J.S., Kumar Y.,
-Encinas A., and Agarwal V. Design and optimization of antireflecting
-coatings from nanostructured porous silicon dielectric multilayers. \textit{%
-Solar Energy Materials \& Solar Cells}, \textbf{123} 144-149, (2014).
-
-\bibitem{Giusseppe2011} Ruminski A.M., Barillaro G., Chaffin C., and Sailor
-M. J., Internally Referenced Remote Sensors for HF and Cl2 Using Reactive
-Porous Silicon Photonic Crystals. \textit{Adv. Funct. Mater.}, \textbf{21}:
-1511-1525, (2011).
-
-\bibitem{Agarwal2018} Karthik T.V.K., Martinez L., and Agarwal V. Porous
-silicon ZnO/SnO$_{2}$ structures for CO$_{2}$ detection. \textit{Journal of
-Allows and Compounds}, \textbf{731} 853-863, (2018).
-
-\bibitem{Hussel1997} C.P. Hussell, R.V. Ramaswamy, \textit{IEEE Photonics
-Technol. Lett.} \textbf{9}, 636, (1997).
-
-\bibitem{Antunez2014} Antunez E.E., Estevez J.O., Campos J., Basurto-Pensado
-M.A., and V.Agarwal V. Formation of photoluminescent n-type macroporous
-silicon: Effect of magnetic field and lateral electric potential. \textit{%
-Physica B} \textbf{453} 34--39, (2014).
-
-\bibitem{Kozar2017} A.
-V.
-Kozar, S.
-V.
-Marchenko and P.
-Y.
-Shestakov, "Focusing and defocusing of reflected light beams from chirped dielectric layered structure," 2017 Days on Diffraction (DD), St.
-Petersburg, pp.
-200-204, (2017).
-
-\bibitem{Cheng2018} Yu-Chieh Cheng and  Kestutis Staliunas, Near-field flat focusing mirrors, Applied Physics Reviews 5, 011101 (2018).
-
-\bibitem{Jimenez2020} Jimen\'{e}z-Vivanco M. R., Garc\'{\i}a G., Carrillo
-J., Agarwal V., D\'{\i}az-Becerril T., Doti R., Faubert J., and Lugo J. E.
-Porous Si-SiO2 based UV Microcavities. \textit{Scientific Reports} \textbf{10%
-}: 2220, (2020).
-
-\bibitem{Ariza2012} Ariza-Flores A. D., Gaggero-Sager L. M., and Agarwal V.
-White metal like omnidirectional mirror from porous silicon dielectric
-multilayers. \textit{Appl. Phys. Lett.}, 101(\textbf{3}):031119, (2012).
-
-\bibitem{Bruyant2003} Bruyant A., L erondel G., Reece P. J., and Gal M.
-All-silicon omnidirectional mirrors based on one-dimensional photonic
-crystals. \textit{Appl. Phys. Lett.}, 82(\textbf{19}):3227-3229, (2003).
-
-\bibitem{DelRio2018} Estrada-Wiese, D., del R\'{\i}o-Chanona, E.A. \& del R%
-\'{\i}o, J.A. Stochastic optimization of broadband reflecting photonic
-structures. \textit{Sci Rep} \textbf{8}, 1193 (2018).
-
-\bibitem{Chavez2020} B. A. Chavez-Castillo, J. S. P\'{e}rez-Huerta, J.
-Madrigal-Melchor, S. Amador-Alvarado, I. A. Sustaita-Torres, V. Agarwal, and
-D. Ariza-Flores, A wide band porous silicon omnidirectional mirror for the
-near infrared range, \textit{Journal of Applied Physics}, \textbf{127}, 20,
-(2020).
-
-\bibitem{Mochan1987} Moch\'{a}n W. L., del Castillo-Mussot M., and Barrera
-Rub\'{e}n G. Effect of plasma waves on the optical properties of
-metal-insulator superlattices. \textit{Phys. Rev. B}, 35(\textbf{3}%
-):1088-1098, (1987).
-
-\bibitem{Ortiz2020} Leandro L. Missoni, Guillermo P. Ortiz, Mar\'{i}a Luz
-Mart\'{\i}nez Ricci, Victor J. Toranzos, W. Luis Moch\'{a}n, Rough 1D
-photonic crystals: A transfer matrix approach, \textit{Optical Materials},
-\textbf{109}, 110012 (2020).
-
-\bibitem{Puente2020} Luis Eduardo Puente-D\'{i}az, Victor
-Castillo-Gallardo, Guillermo P. Ortiz, Jos\'{e} Samuel P\'{e}rez-Huerta, H%
-\'{e}ctor P\'{e}rez-Aguilar, Vivechana Agarwal, W. Luis Moch\'{a}n, Stable
-calculation of optical properties of large non-periodic dissipative
-multilayered systems, \textit{Superlattices and Microstructures}, \textbf{145%
-}, 106629, (2020).
-
-\bibitem{Pap2006} Pap Andrea Edit, Kord\'{a}s Kriszti\'{a}n, V\"{a}h\"{a}kangas
-Jouko, Uusim\"{a}ki Antti, Lepp\"{a}vuori Seppo, Pilon Laurent, and Szatm\'{a}ri
-S\'{a}ndor. Optical properties of porous silicon. part iii: Comparison of
-experimental and theoretical results. \textit{Optical Materials}, 28(5):506-513, (2006).
-
-\bibitem{Estrada2018} D.
-Estrada-Wiese and J.
-A.
-del R\'{\i}o, Refractive index evaluation of porous silicon using Bragg reflectors.
-\textit{Revista mexicana de f\'{\i}sica}, \textbf{64}(1), 72-81, (2018).
-
-\bibitem{minuit} James F. and Winkler M. Minuit user's guide. CERN, Geneva,
-(2004).
-
-\bibitem{Canham1990} Canham L. T. Silicon quantum wire array fabrication by
-electrochemical and chemical dissolution of wafers. \textit{Appl. Phys. Lett.%
-}, 57(\textbf{10}):1046-1048, (1990).
-
-\bibitem{Escorcia2007} Escorcia J. and Agarwal V. E ect of duty cycle and
-frequency on the morphology of porous silicon formed by alternating square
-pulse anodic etching. \textit{Phys. Status Solidi (c)}, 4(\textbf{6}%
-):2039-2043, (2007).
-
-\bibitem{Ariza2011} A. David Ariza-Flores, L M Gaggero-Sager and V Agarwal,
-Effect of interface gradient on the optical properties of multilayered porous
-silicon photonic structures, J Phys D: Appl Phys, 44(15), 155102 (2011)
-
-\bibitem{Brugeman2006} Andrea Edit Pap, Kriszti an Kord as, Jouko
-Vahakangas, Antti Uusimaki, Seppo Leppavuori, Laurent Pilon, and Sandor
-Szatmari. Optical properties of porous silicon. part iii: Comparison of
-experimental and theoretical results. \textit{Optical Materials}, 28(\textbf{%
-5}):506-513, (2006).
-
-\bibitem{Theiss1994} W. Thei\ss , R. Arens-Fischer, M. Arntzen, M.G. Berger,
-S. Frohnhoff, S. Hilbrich, andWernke M. Probing optical transitions in
-porous silicon by reflectance spectroscopy in the near infrared, visible and
-UV. \textit{MRS Proceedings}, 358:435, (1994).
-
-\bibitem{Negro2003} L. Dal Negro, C. J. Oton, Z. Gaburro, L. Pavesi, P.
-Johnson, A. Lagendijk, R. Righini, M. Colocci, and D. S. Wiersma. Light
-Transport through the Band-Edge States of Fibonacci Quasicrystals. \textit{%
-	Phys. Rev. Lett}. \textbf{90}, 055501, (2003).
-
-\bibitem{Vincent1993} G. Vincent. Optical properties of porous silicon
-superlattices \textit{Appl. Phys. Lett}. \textbf{64}, 2367 (1994).
-
-\bibitem{Agarwal2003} V. Agarwal and J. A. del R\'{\i}o, Tailoring the
-photonic band gap of a porous silicon dielectric mirror, Applied Physics
-Letters \textbf{82}, 1512 (2003).
-
-\bibitem{Mochan1988} Moch\'{a}n W. L. and del Castillo-Mussot M. Optics of
-multilayered conducting systems: Normal modes of periodic superlattices.
-\textit{Phys. Rev. B}, 37(\textbf{12}):6763-6771, (1988).
-
-\bibitem{Perez2018} P\'{e}rez-Huerta J. S., Ariza-Flores D., Castro-Garc%
-\'{\i}a R., Moch\'{a}n W. L., Ortiz G. P., and Agarwall V. Reflectivity of
-1D photonic crystals: A comparison of computational schemes with
-experimental results. \textit{Int. J. Mod. Phys. B}, 32(\textbf{11}%
-):1850136, (2018).
-
-\bibitem{Xifre2005} E. Xifr\'{e}-P\'{e}rez, L. Marsal, J. Pallar\'{e}s, and
-J. Ferr\'{e}-Borrull, \textquotedblleft Porous silicon mirrors with enlarged
-omnidirectional band gap,\textquotedblright\ \textit{J. Appl. Phys.} \textbf{%
-97}, 064503 (2005).
-
-\bibitem{Estevez2005} Estevez J. O., Arriaga J., M\'{e}ndez Blas A., and
-Agarwal V. Omnidirectional photonic band gaps in porous silicon based mirrors
-with a Gaussian profile refractive index. \textit{Appl. Phys. Lett.} \textbf{%
-93}:191915, (2005).
-
-\end{thebibliography}
-
-\end{document}

### 2020-12-31 PaperVictor.tex
Revise introduction

@@
 maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
-  de lambda ni theta, y prom es castellano} averaged over a wide wavelength
-and angular range  of PS-based mirrors with different
-porosity contrasts searching for a minimum thickness. Optimization is
+  de lambda ni theta, y prom es castellano}   of PS-based
+mirrors  averaged over a wide wavelength
+and angular range, for different
+porosity contrasts, and we minimize their thickness. Optimization is
 performed in the visible (Vis) and near infrarred (NIR) regions of the
 electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
-structures and \textit{stacking} sub-mirrors. The
-chirped structures were better suited for the Vis, and the stacked
-sub-mirrors for the NIR regions. We design, fabricate and test some
+structures and by \textit{stacking} sub-mirrors. We found \notaL{No
+  estoy seguro del tiempo} that
+chirped structures were better suited for the Vis stacked
+sub-mirrors for the NIR region. We design, fabricate and test some
 optimized omnidirectional structures with less than 100
@@
 
-Photonic crystal (PhC)-based structures are extensively investigated due
+Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
+  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
+structures have been extensively investigated due
 to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
@@
 are consequently organized into photonic bands. Analogous to electrons in a
-crystal, their propagation will be limited by photonic band gaps (PBGs)
-where transmission states are forbidden. The PhC  shows a
-PBG corresponding to the electromagnetic modes which are not allowed to propagate
-through the structure and behaves as a perfect mirror for that range. The width of
-reflection spectrum is important while designing an omnidirectional mirror for
-different applications. The metallic mirrors are widely accepted for reflection
-purposes, but widespread use is limited due to their absorptive nature at the
-visible and near infrared frequencies.  A good alternative are dielectric
-structures as they also provide design flexibility in terms of
-reflection wavelength. These properties are widely used to design various
-one-dimensional (1D) and two-dimensional (2D) PhCs for its
-potential applications in optoelectronics, optical telecommunications and computing,
+crystal, their propagation will be forbidden if their energy lies
+within certain regions known as photonic band gaps (PBG's). Thus, the
+PC behaves as a mirror if illuminated by light with frequencies
+withinin a PBG. For several applications it is useful to fabricate
+{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
+mirrors is limited due to their relatively large absorption at
+visible and near infrared frequencies.  An attractive alternative
+consists of low-absorption dielectric
+structures,  which may be designed for specific frequency
+ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
+applications in optoelectronics, optical telecommunications and computing,
 laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
-\cite{Kumar2020}. The simplest 1DPhC is composed of alternating high $\left(
-n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror,
-BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
-n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$, at some operating wavelength $\lambda_{0}$ 
-(center wavelength) to obtain a certain
-omnidirectional band gap. As the gap depends on the contrast of the
-refractive indices and the number of periods,  broadband mirrors can  be
-engineered by modulating the reflection in a broader wavelength range.
-One of the ways to obtain such structures has been the continuous variation of
-thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997}
-structures. Additionally, broader mirrors can also be achieved by overlapping
-different BMs, where each one reflects around a specific central wavelength,
-resulting in a wider photonic band gap \cite{Xifre2009}.
+\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
+of periodically alternating
+layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
+corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
+thicknesses of is quarter-wavelength
+$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at some chosen nominal
+wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
+which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
+and the number of periods are large enough. Mirrors with high
+reflectance within a wider frequency range may be engineered by
+using different nominal wavelengths for different layers.
+One way to obtain such structures is to gradually change the width of
+the layers as a function of their depth, producing
+\textit{chirped}-type \cite{Zipock1997}
+structures. An alternative is to stack BM's, such that their PBG
+overlap each other, resulting in a wider high-reflection band
+\cite{Xifre2009}.
+\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
+  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
+  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
+  que no son periódicos, tal vez 'brecha prohibida' no es un buen
+  término. Más bien, queremos hablar del ancho de banda del espejo,
+  i.e., la región en que es buen reflector.}
 
@@
 BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
-electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
-reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of
-TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003}
-used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers,
-followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
-oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
-nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by
+electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
+\notaL{Hay que checar que la puntuación vaya después de las citas,
+  para este estilo de citas entre corchetes} have
+reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
+TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al., \cite{Park2003}
+used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
+followed by its conversion to
+GaAs/Al$_{2}$O$_{3}$ layers by selective
+oxidation of the AlAs layers, to obtain an ODBM with a band from 710 to 950
+nm. On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
 coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
 polyamide-imide polymer, deposited by thermal evaporation and spin-casting
-respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm
-wavelength. Furthermore, Jena et al., \cite{Jena2019}
+respectively, to obtain a 150 nm wide omnidirectional band centered at
+1750 nm. Furthermore, Jena et al., \cite{Jena2019}
 used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
 _{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
-layers) to generate 1DPhC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
-592 to 668 nm. However, these techniques are expensive and
-require sophisticated equipment and long fabrication time. Using PS
-is an alternative, as PS is typically fabricated by simple electrochemical etching of
-crystalline Si in hydrofluoric acid based electrolyte, to obtain the
-sponge-like nanostructure composed of Si and air in a relatively short duration of
-time. The generated porosity can be tuned by changing the applied current
-density and hence modifies the refractive index of the resulting PS. This
-fact opens the possibility of designing 1DPhC with PS, which seeks to
+layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved ODBM from
+592 to 668 nm. However, these techniques are expensive and they
+require sophisticated equipment and long fabrication times. Using PS
+is an attractive alternative, as PS may be fabricated by simple
+electrochemical etching during short times of
+crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
+sponge-like nanostructure composed of Si and air. By modulating in
+time the applied current, the porosity of the PS, and thus its
+refractive index, can be modulated
+along its depth. This allows the design and fabrication of 1D-PC's with PS, to
 control the propagation of light in a dielectric medium. The low cost and
-ease of obtaining porous silicon make it an excellent candidate to develop
-optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
+ease of fabrication of PS make it an excellent candidate to develop
+multilayered optical devices \cite{Xifre2015,Pavesi2000}.
 Although optical filters \cite{Estevez2009,Ariza2014} are the most common
-application of porous silicon, they have been widely used as chemical
+application of PS PC's, they have also been widely used as chemical
 sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
-photoluminescence control \cite{Antunez2014}. Recently, the study of
-quasi-omnidirectional Bragg mirrors has increased due to their possible application
-as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric
+for photoluminescence control \cite{Antunez2014}. Recently, the study of
+quasi-omnidirectional Bragg mirrors has
+increased due to their possible application
+as a flat lens \cite{Kozar2017,Cheng2018}.\notaL{Lens o mirror, no
+  puede ser ambas? De verdad esto es lo que más lo ha popularizado?}
+PS based dielectric
 optical filters, quasi-ODBM and ODBM have been extensively studied in different
-regions of the electromagnetic spectrum, such as ultraviolet (UV)
-\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping
-in view that high values of average porosity, refractive index contrast and
-thickness make the multilayer structures fragile, in this work various wide
-band gap photonic structures have been proposed to obtain maximal average
-reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum
-possible thickness and low refractive index contrast.
+regions of the electromagnetic spectrum, such as the ultraviolet (UV)
+\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR)
+\cite{Bruyant2003}. However, to obtain the desirable high index of refraction
+contrast, layers of high porosity have to be employed, so that the
+resulting structures may be fragile, making large structures, with a
+very large number of layers, unfeasible. For this reason, in this work
+we study different strategies to produce photonic mirrors
+that have a large reflectance over a wide band-width with a relatively
+small thickness and refractive index contrast. Specifically, our aim
+is to maximize the reflectance $R$ averaged over a wide range of
+wavelengths $\lambda$ and angles of incidence $\theta$.
 
-This paper is organized as follows. Section 2 presents the development of
+This paper is organized as follows. In Sec. \ref{s:theory} \notaL{No uses números,
+  usa referencias a etiquetas para numerar y referir todo} we develop the
 methods used to design and calculate the reflectance spectra of the PS
-multilayer structures. Section 3 provides the experimental details about the
-fabrication of some of these structures. Section 4 presents the numerical
-results corresponding to different methodologies (chirped structures and sub-mirror stacks) adopted to minimize the thickness of the structure for
-maximal reflectance along with the experimental results and its comparison with the
-existing reports.  The obtained experimental results revealed an enhancement in the
-quasi omnidirectional band gap (0-60${{}^\circ}$) by a factor of approximately 2
-with half the structure physical thickness in both the configurations, compared to
-the last reported works \cite{DelRio2018,Chavez2020}. Finally, the conclusions of
-this work are presented in Section 5.
+multilayered structures such as chirped structures and mirror
+stacks. In Sec. \ref{s:exp} we provide details about the
+fabrication of these structures. In Sec. \ref{s:res} we present the numerical
+and experimental results for our proposed structures and compare
+them to previous reports. We obtained significantly larger band-widths
+with significantly thinner structures. \notaL{Dejo para resultados y
+  conclusiones los detalles de con quién comparamos y qué salió.}
+Finally, we discuss our conclusions in Section \ref{s:conc}.
 
-\section{Theoretical analysis}
+\section{Theoretical analysis}\label{s:theory}
 
+\notaL{Pon etiquetas a todo para poderlo referir}
 In the analysis of the propagation of the electromagnetic field through
@@
 
-\section{Experimental details}
+\section{Experimental details}\label{s:exp}
 
@@
 
-\section{Results and discussion}
+\section{Results and discussion}\label{s:res}
 
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{s:conc}
 

### 2020-12-31 PaperVictor.tex
Revise theory

@@
 % structures}
-\title{ Thickness optimization in wide range quasi
-omnidirectional 1-D photonic structures}
+\title{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
 \author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
@@
 
-\section{Theoretical analysis}\label{s:theory}
+\section{Theory}\label{s:theory}
 
 \notaL{Pon etiquetas a todo para poderlo referir}
-In the analysis of the propagation of the electromagnetic field through
-multilayer systems, it is common to employ the transfer matrix method (put the
-reference). Under the consideration that the system only varies along the $z$ axis, the
-transfer matrix is $M\left(z_{2},z_{1}\right)$
-a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
-and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
-normal to the axis of the structure, evaluated at any two points $z_{2}$
-and $z_{1}$
+For the analysis of the propagation of electromagnetic fields through
+multilayer systems it is usual to employ the transfer matrix
+method\notaL{reference}. Assuming the system is 1D, with variations
+only along the $z$ directions, and that the polarization of light is either
+transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
+  sería de 4x4}, the
+transfer matrix $M\left(z_{2},z_{1}\right)$ is
+a 2x2 matrix that relates the components of the electric $E_{\| }$
+and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
+evaluated at $z_2$ to their value at $z_{1}$,
 \begin{equation*}
@@
 \begin{array}{c}
-E_{\Vert } \\
-H_{\Vert }%
+E_{\|} \\
+H_{\| }%
 \end{array}%
@@
 \begin{array}{c}
-E_{\Vert } \\
-H_{\Vert }%
+E_{\| } \\
+H_{\| }%
 \end{array}%
@@
 \end{equation*}%
-Many equivalent formulations have been proposed to obtain $M$
+Many equivalent formulations have been proposed to obtain and use $M$
 \cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
-to calculate the reflectance of large multilayer systems proposed by Puente-D%
-\'{\i}az, et al. \cite{Puente2020}, since we need a reliable and stable tool
-to design an optimized structure through a minimization procedure that
-requires the calculation of complete spectra for all sets of design parameters.
-The development of $M$ is shown in the supplementary information. Therefore, the
+for the numerically stable calculation of the reflectance of large
+multilayer systems, as
+proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
+supplementary information. The
 explicit expressions for the optical coefficients are:
 \begin{equation}
-r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
-\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
-_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
+r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
+M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
 \end{equation}%
@@
 \begin{equation}
-t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
-_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
+t=\frac{2Z_{\alpha
+  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
 \end{equation}%
-where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
+where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
+  explicarlas, y no creo que sean importantes para el lector} are the elements
+of the transfer matrix which transfer
+the fields from its surface interface with vacuum at $z_0$ towards the
+substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
+surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
+of the reflected and transmitted fields, where we choose the $F$'s as electric
+fields for (TE) polarization and magnetic fields
+for transverse magnetic polarization (TM). The upper sign $-$ in
+Eq. (\ref{rBloch}) and the subscript $\alpha =s$
 in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
 the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
-polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
+polarization, respectively.
+The reflectance is given by
+$R=|r|^{2}$ and the
 transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
-=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
-the case of TM polarization. Additionally, complex refractive indices of the porous
-layers in the simulations were obtained by Bruggeman effective medium theory, which
+=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
+TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
+  estaban en la fórmula} The complex refractive index of the porous
+layers were obtained through the Bruggeman's effective medium theory, which
 has been reported to adequately reproduce the PS optical parameters
@@
 
+\notaL{Creo que esto debería estar más adelante:
   After the next section, two techniques are developed to design multilayer
@@
 dispersion relation is analyzed.
+}
 

### 2021-01-01 PaperVictor.tex
Revise experimental details

@@
 Some of the proposed photonic structures were synthesized through anodic
-etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
+etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
 resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
-\cite{Canham1990,Escorcia2007}. Electrochemical anodization process was
-performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
+\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
+performed at room temperature, with an electrolyte of aqueous
+hydrofluoric acid (HF) (48$\%$ of
 wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
 With this electrolyte, the minimum and maximum porosities that can be
-obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
-cm$^{2}$, respectively. However, it is not desirable to use very high
-porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}.
-For this reason, the current
-densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
-porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
-acquired through a gravimetric technique as follows: single layers of porous
-silicon were synthesized under similar conditions and were weighed ($m_{i}$)
+obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de
+  aquí, pues lo discutes abajo:(gravimetrically obtained)}, using
+current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$,
+respectively. However, as it is not desirable to use very high
+porosity contrasts due to structure fragility and electrolyte
+diffusivity problems \cite{Ariza2011}, the current
+densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, with
+corresponding
+porosities of 51\% and 76\%, respectively. The porosity was calibrated
+\notaL{Creo que no muestras curvas de calibración: calibration curves were
+acquired} through a gravimetric technique as follows: single layers of porous
+silicon were synthesized under similar conditions applying a constant
+current for a time \notaL{cuánto tiempo para la calibración?}  and were weighed to
+obtain their mass $m_i$
 before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
-dissolving the already formed porous silicon layer ($m_{3}$), to calculate
-the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}. Etching
-rate of PS was obtained by re-synthetizing individual layers under similar
-conditions and measuring their thicknesses through SEM (Scanning Electron
-Microscopy). The absolute reflectivity measurements were carried out
+dissolving the already formed porous silicon layer ($m_{3}$), to obtain
+the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.
+The etching
+rate of PS was obtained by synthetizing single layers under similar
+conditions and measuring their thicknesses through Scanning Electron
+Microscopy (SEM). Absolute reflectivity measurements were carried out
 with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
-angle universal reflectance accessory (URA) for different incident angles $%
-\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
-50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
+angle universal reflectance accessory (URA) for different incident
+angles $\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$,
+$40^{\circ }$, $50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
 minimum values of $\theta _{i}$ were constrained by the angular range of the
@@
 
-This section presents the comparison of the calculated and measured reflectance
+In this section we present compare the calculated and measured reflectance
 spectra at different incidence angles in the regions of interest. In the first
@@
 
+\notaL{Quizás esto se pueda incluir por aquí.:
+  After the next section, two techniques are developed to design multilayer
+photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
+the $j$-th period of the structure is designed, is modulated by an
+increasing function. This can be as simple or complex as you like. The
+proposed function was optimized with the Minuit module of PDL (Perl Data
+Language) \cite{minuit}. The other technique for proposing highly reflective
+structures over a wide region of the electromagnetic spectrum is to stack
+sub-mirrors tuned to different wavelengths. For each sub-mirror the
+dispersion relation is analyzed.
+}
 \subsection{Chirped-type Bragg mirrors}

### 2021-01-01 PaperVictor.tex
Revise up to the first experimental results

@@
 can be synthesized by a simple electrochemical technique. We
-maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
+maximize the reflectance $\braket{R}$ \notaL{El promedio no depende
   de lambda ni theta, y prom es castellano}   of PS-based
@@
 
-In this section we present compare the calculated and measured reflectance
-spectra at different incidence angles in the regions of interest. In the first
-subsection, the design and optimization of R$_{\text{ave}}$ of \textit{chirped}
-photonic structures is presented, and next subsection the design of the structure is
-analyzed through sub-mirrors stacks.
+In this section we presents optimized calculations of the reflectance
+of different multilayered omnidirectional wide-band mirrors and we
+compare the results to spectra taken from
+the corresponding samples at several angles of
+incidence. Sec. \ref{ss:chirped} is devoted to chirped-type Bragg
+mirrors while Sec. \ref{ss:stacked} is devoted to structures made of
+stacked sub-mirrors.
 
@@
 the $j$-th period of the structure is designed, is modulated by an
-increasing function. This can be as simple or complex as you like. The
+increasing function. This can be as simple or complex as you
+like. {\tiny The
 proposed function was optimized with the Minuit module of PDL (Perl Data
-Language) \cite{minuit}. The other technique for proposing highly reflective
+Language) \cite{minuit}.} The other technique for proposing highly reflective
 structures over a wide region of the electromagnetic spectrum is to stack
@@
 }
-\subsection{Chirped-type Bragg mirrors}
+\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}
 
-The generic form of the expression that modulates the design of photonic
-structure is:
+Here we study multilayered structures where the thicknesses for each
+pair $j=0\ldots N_p$ of layers are tuned to a wavelength $\lambda_j$ which changes
+gradually with the depth of the layer, according to
 \begin{equation}
-\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left( x_{j}\right),\label{Dis}
+\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f(j/N_p)),\label{Dis}
 \end{equation}%
-where $\lambda_{\min }$, $\lambda_{\max }$ and $\lambda_{j}$ correspond
-to the minimum, maximum, and design wavelengths to which the $j$-th period
-is tuned, respectively, and $f\left( x_{j}\right) $ represents any
-normalized function that modulates the thickness. Here $x_{j}=\frac{j}{N_{p}}$ being
-$j$ the $j$-th period and $N_{p}$ the total number of periods that the structure
-will contain. Only restriction for $f\left( x_{j}\right) $ is that it has to be an
-increasing function, due to the high absorption of PS in the ultraviolet region
-which decreases in the visible and becomes negligible in the near infrared. So, the
-first periods are syntonized in the UV-Vis regions. This work shows the analysis
-of following functions:
+where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and {\em
+  design} wavelengths respectively, $N_p$ is the index of the deepst
+pair of layers and $f(x)$ is some smooth function
+that goes from 0 to 1 as its argument goes from surface ($x=0$) to the
+substrate ($x=1)$. We only consider increasing functions $f$ due to
+the high absorption of PS in the ultraviolet region
+which decreases in the visible and becomes negligible in the near
+infrared, so, the
+first periods are syntonized in the UV-Vis regions. We consider the
+following classes of functions:
 \begin{equation}
@@
 where $\alpha$, $\beta$ and $A$ are parameters to optimize. The function
-$f_{1}$ (Eq. (\ref {F1})) represents the simplest profiles. The restrictions
-for the values $\alpha$ are that they must be positive and they must not be
-extremely large or small. In these cases, mirrors that reflect in
-$\lambda_{\text{min}}$ or $\lambda _{\text{max}}$, respectively, will be obtained. Eq.
-(\ref{F2}) is formed by the average of two functions of type $f_{1}$ with different
-powers. The function $f_{3}$ (Eq. (\ref{F3})) was designed so that the first and second
-additions predominate the short and long wavelengths, respectively. The
-R$_{\text{ave}}$ of the structures is calculated in
-the wavelength range from 350 to 1400 nm and from 0 to 90${{}^\circ}$ angle of
-incidence. The optimized parameters using a porosity contrast of $51/76\%$ are shown
-in Table 1 and in the supplementary information they appear for the porosity
-contrasts of $30/76\%$ and $42/76\%$.
+$f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
+restricting  $\alpha>0$. The functions $f_2$ are arithmetic averages
+of two functions of the type $f_{1}$ with different
+powers $\alpha$ and $beta$ \notaL{A ¿no debe ser 1/2 a fuerza, para
+  que $f_2(1)=1$?}. The functions $f_{3}$ (Eq. (\ref{F3})) are
+designed so that the power $\alpha$ dominates close to the surface and
+the power $\beta$ close to the substrate, to allow different behaviors
+at the UV and at the IR end of the spectrum. The reflectance
+$R(\lambda,\theta)$ of the resulting structures was calculated in
+the wavelength range from 350 to 1400 nm and for angles of incidence
+from normal ($0^\circ$)  to grazing ($90^\circ$) incidence and
+averaged to yield $\braket{R}$. The parameters $\alpha$, $\beta$
+and $\gamma$ were then optimized to maximize the average
+reflectance. The calculations were done using the Perl Data Language
+(PDL) and its interface to the MINUIT minimization
+package\cite{minuit}.The optimized parameters corresponding to a
+porosity contrast of
+51/76\% are shown
+in Table 1.  In the supplementary information we include the
+parameters for porosity contrasts of $30/76\%$ and $42/76\%$.
 \begin{table}
-\caption{ Design parameters obtained after the optimization of functions (Eqs.
-(\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
-\includegraphics[width=\textwidth]
-{F2TableOptimized.pdf}
+\includegraphics[width=\textwidth]{F2TableOptimized.pdf}
+\caption{Optimized parameters yielding the highest average reflectance
+  $\braket{R}$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs.
+  (\ref{F1}) - (\ref{F3}))}
 \end{table}
+\notaL{Sugiero poner aquí una tabla de latex, editable, en lugar de
+  una figura}
+\notaL{No es claro en el texto cómo se obtiene $N_p$. Se mencionaba
+  una minimización del ancho, pero no recuerdo cómo se minimizó a la
+  vez que se maximizaba la reflectancia. ¿Fue minuit? ¿Fue a ojo?}
 
-According to the values shown in table I, the structure (named as ST-A) that has the
+According to table I, the structure (named as ST-A)\notaL{Este nombre
+  no está en la tabla. ¿Qué significa el acrónimo?} that has the
 maximum average reflectance with the minimum thickness is the one designed
-with the function $f_{3}$ (Eq. (\ref{F3})). Thus, the first and last periods
-are tuned to 320 and 1400 nm, respectively. The complete distribution of the
-periods is presented in Fig. \ref{Fig2}(a).
+with the function $f_{3}$ (Eq. (\ref{F3})) with parameters
+$\alpha=1.23$, $\beta=0.54$ and $A=0.18$, which is shown in
+Fig. \ref{Fig2}(a). \notaL{Si queremos que $x_j$ vaya de 0 a 1 habría
+  que numerar $j$ de 0 a $N_p-1$, y dividir entre $N_p-1$ en lugar de 1 a $N_p$ y
+  dividir entre $Np$. Parece que no lo hiciste así, entonces habría que
+  revisar un poco la discusión arriba}.
 \begin{figure}
 \begin{center}
-\includegraphics[width=\textwidth]
-{F3OptimizedVis.pdf}
+\includegraphics[width=\textwidth]{F3OptimizedVis.pdf}
 \end{center}
-\caption{(a) Distribution of $\protect\lambda_{j}$ in the $j$-th period for
-the design of the 63-period multilayer structure. (b) Mapping of the average
-reflectance of the structures designed with different values{}of $%
-\protect\alpha $ and $N_{p}$ parameters. It is verified that the parameters
-obtained during the optimization are adequate ($\protect\alpha =1.23$ and $%
-N_{p}=63$). (c) Mapping the calculated reflectance for non polarized light of the
-designed structure with the optimized values. (d) Comparison of reflectance spectra
+\caption{(a)Design wavelength $\lambda_{j}$ vs. period number $j$-th
+  for the optimized structure ST-A with 63-periods.\notaL{Parece un
+    poster miniatura. ¿La ilustración a la derecha está a escala o
+    es esquemática? ¿La necesitamos? Está tan chica que es ilegible}
+  (b) Average reflectance of the structures designed with different
+  values of $\alpha$ and $N_{p}$.\notaL{Por qué en la misma figura?
+    ¿Cuál es el propósito de incluir esta? Cambia el cbrange para que
+    el color diga algo. Se ve todo rojo uniforme.} It is verified that the
+  parameters obtained during the optimization are adequate ($\alpha
+  =1.23$ and $N_{p}=63$).\notaL{Este comentario va en el texto, no en
+    el pie de figura} (c) Reflectance for non polarized light of the
+  optimized structure. (d) Comparison of the reflectance spectra
   calculated and measured at different angles of incidence. The gray band indicates the
   region in which the reflectance is greater than 95\%. Inset shows the
-top view photograph of the synthesized structure.}
+  top view photograph of the synthesized structure.\notaL{En mi
+    humilde opinión son demasiadas figuras en una sola, no
+    claramente relacionadas entre sí.}}
 \label{Fig2}
 \end{figure}
-To verify that the values obtained are optimal, in Fig. \ref{Fig2}(b), the average
-reflectances of the photonic structures designed with different parameters are mapped
-and, indeed, the values are in the area where R$_{\text{ave}}$ is maximum. Here, the
+In Fig. \ref{Fig2}(b)
+we show $\braket{R}$ for different values of $N_p$ and
+$\alpha$ to illustrate its dependence on the parameters, and
+to verify that our optimized values correspond indeed to the maximum. Here, the
 parameters $\lambda_{\text{min}}$, $\lambda_{\text{max}}$, $\beta$ and $A$ were
 adjusted, while $N_{p}$ and $\alpha$ varied from 30 to 200 periods and from 0.4 to 1.3,
-respectively. The calculated reflectance, R$\left( \lambda ,\theta \right) $, of the
-photonic structure is shown in Fig \ref{Fig2}(c). Here, the wavelength and incidence
-angle cover the ranges from 350 to 1400 nm, and from 0${{}^\circ}$ to 90${{}^\circ}$,
-respectively. Calculations indicate that the structure has a localized omnidirectional
-band gap from 1000 to 1200 nm, taken with a reflectance greater than 95$\%$. Due to
-experimental limitations, reflectance spectra for non polarized light are shown in all results. In Fig. \ref{Fig2}(d), the calculated and measured reflectance is compared
-at 10${{}^\circ}$, 20${{}^\circ}$, 30${{}^\circ}$, 40${{}^\circ}$, 50${{}^\circ}$
-and 60${{}^\circ}$ of incidence. In this angular range, the structure has a
+respectively. \notaL{Ya no me quedó claro. Hay que decir arriba cuales
+  son los parámetros que se variaron durante la optimización original. ¿Fueron
+  $N_p$, $\lambda_{min}$, $\lambda_{\max}$, $A$, $\alpha$ y $beta$,
+  todos ellos? Creo que no es claro. Si fue así, hay que distinguir
+  las longitudes de onda del ajuste de las del rango en que
+  optimizaste la reflectancia}
+The calculated reflectance, $R(\lambda ,\theta)$ of the optimized
+photonic structure is shown in Fig \ref{Fig2}(c) for wavelengths and incidence
+angles covering the ranges from 350 to 1400 nm, and from $0^\circ$ to $90^\circ$,
+respectively. Calculations indicate that the structure is an omnidirectional
+mirror with a  reflectance $R>0.95$ within a band from 1000 to 1200
+nm. \notaL{La zona gris en la figura va más allá de 1200.} We
+fabricated a sample corresponding to our
+optimized structure and measured its reflectance spectra at several
+incidence angles $\theta$. Due to
+experimental limitations, we restrict our results to the case of
+non-polarized light.
+In Fig. \ref{Fig2}(d), the calculated and
+measured reflectance are compared
+for $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$, $50^\circ$
+and $60^\circ$. In this angular range, the structure has a
 quasi-omnidirectional band gap (R$\left(\lambda,\theta\right)>95\%$) located from
-980 to 1340 nm. The numerical and experimental spectral line shapes at different
-angles are in good agreement. For wavelengths greater than 700 nm and lying between
-10${{}^\circ}$ to 40${{}^\circ}$ of incidence angle, the difference in spectra is
-less than $5\%$. For angles of incidence greater than 40 degree, although their
-characteristics are similar, the measured spectrum demonstrates relatively less
-reflectance than calculated reflectance. This difference can be attributed, in part,
-to the scattering of light between each of the actual interfaces, which generally
-have some roughness \cite{Theiss1994,Chavez2020}.
+980 to 1340 nm. \notaL{Aquí hay un error: el experimento salió ¡mejor
+  que la teoría! (ver arriba) Algo hay mal en la descripción, pues la
+  figura muestra al experlimento abajo de la teoría.}  The
+numerical and experimental spectral line shapes at different
+angles are in good agreement. For $\lambda>700$nm and
+$10^\circ<\theta<40^\circ$ the spectra differs by
+less than $5\%$. For $\theta>40^\circ$ both spectra agree
+qualitatively but the measured reflectance is lower that than the
+calculated one. This difference can be attributed, in part,
+to the scattering of light at the actual interfaces, which generally
+have some roughness \cite{Theiss1994,Chavez2020} which we have not
+accounted for in our theory.\notaL{Quizás aquí puedas citar el
+  artículo de Guillermo Ortiz y mío reciente {\em Rough 1D  Photonic
+    Crystals: a transfer matrix approach}, Leandro Missoni, Guillermo
+  Ortiz, María Martinez Ricci, Victor Toranzos y W. Luis Mochan,
+  Optical Materials {\bf 109}, 110012 (2020)
+{\tt https://doi.org/10.1016/j.optmat.2020.110012}}
+
+\notaL{Aquí voy.}
 

### 2021-01-04 PaperVictor.tex
Llegué a mirror stacking

@@
     poster miniatura. ¿La ilustración a la derecha está a escala o
-    es esquemática? ¿La necesitamos? Está tan chica que es ilegible}
+    es esquemática? ¿La necesitamos? Está tan chica que es
+    ilegible}\notaL{¿Qué es eso de $\lambda+1$? Creo que está mal}
   (b) Average reflectance of the structures designed with different
@@
 
-\notaL{Aquí voy.}
-
-Due to the absorptive nature of Si in the UV and visible region, it is relatively
+Due to the disipative nature of Si in the UV and the visible region, it is relatively
 difficult to design porous silicon omnidirectional mirrors in that region.
 However, in the IR region, it is relatively easy to obtain highly reflective
-and even omnidirectional photonic structures over a wide range. Therefore,
-the average reflectance was optimized using the function $f_{1}$ (Eq. (\ref{F1}))
-in the region of 850 to 3000 nm. It was found that the best value for
-$\alpha $ is 1.2 and the minimum thickness is 60.4 $\mu$m, distributed in
-90 periods. The complete design of the structure (named as ST-B) is graphed in Fig.
+and even omnidirectional photonic structures over a wide
+range. \notaL{Está rara la lógica: ¿optimizamos en esa región porque
+  es fácil o usamos $f_1$ porque optimizar es fácil? Quizás primero
+  debamos decir que nos interesa esa región y que como es fácil,
+  usamos $f_1$.}
+Therefore,
+the reflectance average in the region of 850 to 3000 nm and for all
+angles was optimized using the function $f_{1}$ (Eq. (\ref{F1})), yielding
+$\alpha=1.2$ with $N_p=90$ and a thickness of 60.4 $\mu$m. \notaL{Aquí
+  me vuelve a confundir. ¿90 es el ancho óptimo o
+  es el ancho mínimo que permitió... qué?} The resulting design
+wavelengths of the structured, designated as ST-B, \notaL{¿Por qué se llaman así? ¿Qué significa
+  ST?} are shown in Fig.
 \ref{Fig3}(a).
@@
 \end{center}
-\caption{(a) Distribution of $\protect\lambda _{j}$ in the $j$-th period
-modulated by the optimization of the function $f_{1}$ for the design of the
-multilayer structure of 90 periods. (b) Mapping of the average reflectance
-of the structures designed with different values of the $\protect\alpha $
-and $N_{p}$ parameters. The optimized parameters are $\protect\alpha =1.2$
-and 90 periods. (c) Mapping the calculated reflectance of the designed
-structure with the optimized values for non polarized light. (d) Comparison of
-reflectance spectra calculated and measured at different angles of incidence. The
-gray band indicates the region in which the reflectance is greater than 95$\%$. Inset
-there is a photograph of the synthesized structure.}
+\caption{(a) Design wavelengths $\lambda_j$ as a function of period
+  number $j$ for sample ST-B. (b) Average reflectance $\braket{R}$
+for different values of the parameters $\alpha$
+and $N_p$ parameters. \notaL{Cambia el letrero en la figura} The
+optimized parameters $\protect\alpha =1.2$
+and $N_p=90$ are displayed as a white spot.\notaL{No se ve que sea el
+  óptimo. Quizás se necesiten línes de contorno más juntas.} (c)
+Calculated reflectance of the optimized
+structure for non polarized light.\notaL{¿QUé indica la raya punteada
+  y el letrero en la figura?} (d) Comparison of
+the calculated and measured spectra  for several angles of incidence. The
+gray band indicates the region in which the reflectance is greater than 95$\%$. Inset:
+photograph of the synthesized structure.}
 \label{Fig3}
@@
 
-In Fig \ref{Fig3}(b) the average reflectance of structures
-designed with different values of $\alpha$ and $N_{p}$ is mapped. As in the
+\notaL{Tengo los mismos comentarios que para la figura previa.}
+Fig \ref{Fig3}(b) shows $\braket{R}$ for
+different values of $\alpha$ and $N_{p}$. As in the
 previous case, the optimized parameters are within the zone of maximum
-average reflectance. The reflectance calculation shows that this structure
-has a wide quasi-omnidirectional gap that goes from 850 to 3000 nm and from
-0${{}^\circ}$ to 70${{}^\circ}$ of incidence; the corresponding contour plot is
-shown in Fig. \ref{Fig3}(c) and its average reflectance between $850-3000$ nm is
-greater than 95\%. The measured and calculated reflectance spectra have very
-similar characteristics as shown in Fig \ref{Fig3}(d).  The synthesized PS
-multilayered 1D photonic structure has a quasi omnidirectional (from 0${{}^\circ}$
-to 60${{}^\circ}$) band gap of approximately 1800 nm. The difference
+average reflectance. \notaL{No debería ser el mismísimo máximo y no
+  nada más en la zona?} The reflectance calculation  is
+shown in Fig. \ref{Fig3}(c).  This structure
+has a wide quasi-omnidirectional gap with $R(\lambda,\theta)>0.95$
+with $\lambda$ from 850 to 3000 nm and $\theta$ from
+$0^\circ$ to $70^\circ$.\notaL{Me da la impresión que confundías
+  promedio con reflectancia} The measured and calculated reflectance
+are compared  for several angles in Fig \ref{Fig3}(d). The synthesized PS
+multilayered 1D photonic structure behaves as a quasi omnidirectional
+mirror for $0^\circ\le\theta\le 60^\circ$ with a bandwidth of approximately 1800 nm. The difference
 between the calculated and measured spectra at the longer wavelengths can be
-attributed to a thickness gradient along the depth, which is more pronounced in
+attributed to a thickness gradient along the depth,\notaL{No entiendo:
+  está diseñada para tener un gradiente de ancho. Te refieres a un
+  gradiente adicional al diseñado?} which is more pronounced in
 the lower layers due to the restricted diffusivity of the electrolyte
-through the structure itself \cite{Negro2003,Vincent1993} and interface roughness.
+through the structure itself \cite{Negro2003,Vincent1993} and
+interface roughness \notaL{No se entiende si este es otro efecto o si
+  la rugosidad produce un gradiente de anchos}.
 

### 2021-01-04 PaperVictor.tex
Finish revision.

@@
   la rugosidad produce un gradiente de anchos}.
-
-\subsection{Photonic structure with sub-mirrors stacking}
+y
+\subsection{Photonic structure with sub-mirrors stacking}\label{ss:stacked}
 
 Another technique to design Bragg mirrors in a wide range of the
-electromagnetic spectrum is by stacking sub-mirrors at different
+electromagnetic spectrum is by stacking sub-mirrors tuned to different
 wavelengths \cite{DelRio2018,Agarwal2003}. Such grouping must meet the condition
-imposed by the dispersion relation, $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is
-the period, which corresponds to the actual thickness of the sub-mirror, $\pm K$
+imposed by the dispersion relation,\notaL{No se entiende, ¿de qué la gira
+la relación de dispersión? Es la relación de dispersión ¿de qué? Falta
+una explicación!} $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is
+the period, which corresponds to the actual thickness of the
+sub-mirror\notaL{Por qué? El espejo podría tener varios periodos.}, $\pm K$
 represents a 1D Bloch's vector corresponding to a wave that propagates along
-$z$-direction \cite{Mochan1987,Mochan1988,Perez2018}, and T$\text{r}$ denotes the
+the $z$-direction \cite{Mochan1987,Mochan1988,Perez2018}, and T$\text{r}$ denotes the
 trace. This equation is bounded by the minimum and maximum values that the cosine
@@
 M\right) \right\vert$ is $>2$, it indicates that this frequency will not
-be able to propagate through the structure.
+be able to propagate through the structure. \notaL{Las ideas están
+  bien, pero está muy mal explicado, en desorden}
 
-The ideal stack of sub-mirrors would be that PBG of the $j$-th mirror begins
-at the edge of the PBG of the $j-1$-th mirror, until the desired interval has been
+The ideal stack of sub-mirrors would be that edge where the PBG of the $j$-th mirror begins
+is close to the  edge of the where the PBG of the $j-1$-th mirror
+ends, and sufficient mirrors are stacked until the desired interval
+bandwidth has been
 covered. However, this arrangement does not give the maximum average reflectance due to
-the decrease in the reflectance at each intersection of the two PBGs. On the other hand,
+the decrease in the reflectance at each intersection of the two
+PBGs.\notaL{QUé es una intersección de PBG? Escribe para que el lector
+  entienda} On the other hand,
 the number of periods of each sub-mirror is an important parameter due to its direct
@@
 $<\lambda_{D}<$650 nm, two periods , for 650 $<\lambda_{D}<$800 nm, three, and for
-$\lambda_{D}>$ 800 nm, the number of periods was variable (Fig. \ref{Fig4}(a)).
+$\lambda_{D}>$ 800 nm, the number of periods was variable
+(Fig. \ref{Fig4}(a)). \notaL{No entendí el argumento, ni cómo
+  dterminaste para qué lambdas se usan tantos o cuántos periodos. ¿Fue
+  prueba y error? ¿Fue una optimización?}\notaL{Por cierto,
+  ¿optimizaste qué tanto traslapar espectros sucesivos o usaste la
+  regla de que se toquen los bordes de banda?}
 \begin{figure}[tbph]
@@
 \end{center}
-\caption{(a) Diagram showing the distribution of sub-mirrors and the corresponding
-number of periods in a PS multilayer. (b) Maximization of the average reflectance as
+\caption{\notaL{Stack, no stak. ¿Qué significa la región rugosa que
+    rodea la estructura?} (a) Diagram showing the distribution
+  of sub-mirrors and the corresponding
+number of periods in a PS multilayer.\notaL{Esto no es un cartel. No
+  entiendo qué pretende ilustrar el panel (a)} (b) Maximization of the average reflectance as
 a function of the overlap photonic band gap for the structures formed by sub-mirrors
-with a fixed number of periods (3 and 4), and for structures with the design of (a)
-using 3 and 6 periods for the tuned sub-mirrors in $\lambda>800$ nm. (c) Mapping the
-calculated reflectance of the designed structure with the optimized values for non
-polarized light. (d) Comparison of reflectance spectra calculated and measured at
-different angles of incidence. The gray band indicates the region in which the
-reflectance is greater than 95$\%$. Inset shows the top view photograph of the
+with a fixed number of periods \notaL{No has explicado a qué te
+  refieres con esta optimización. No has explicado qué es el overlap
+  photonic band gap. Esto parece tomado de un cartel, pero el artículo
+debe ser autocontenido; no estás ahí parado para explicar.}(3 and 4),
+and for structures with the design of (a)
+using 3 and 6 periods for the tuned sub-mirrors in $\lambda>800$
+nm.\notaL{No entendí nada.} (c)
+Calculated reflectance for the optimized structure for non
+polarized light. (d) Comparison between the measured and calculated
+reflectance spectra at several angles of incidence. The gray band indicates the region in which the
+reflectance is greater than 95$\%$. Inset shows a photograph with a top view of the
 synthesized structure.}
@@
 910, 1020, 1150, 1290, 1450, 1630, 1830, 2060, 2320, 2610 and 2860 nm  with periods
-of 1 (400, 460 nm), 2(510, 570, 640 nm), 3 (720 nm) and 6 (810 nm and above).
+of 1 (400, 460 nm), 2(510, 570, 640 nm), 3 (720 nm) and 6 (810 nm and
+above).\notaL{Sugiero reescribir tratando de que la explicación sea clara}
 
 The reflectance mapping shown in Fig \ref{Fig4}(c) reveals a quasi omnidirectional
-band gap from 950 to 2900 nm, taking into account 0${{}^\circ}$ to 60${{}^\circ}$ of
-incidence. It is also observed that at incidence angles $>$70${{}^\circ}$, for long
+mirror in the range from 950 to 2900 nm, for $\theta$ between
+$0^\circ$ and $60^\circ$. It is also observed that at incidence angles $>$70${{}^\circ}$, for long
 wavelengths the reflectance decreases and has oscillations, which are attributed to
 the greater penetration of the electromagnetic field within the structure, as shown
-by Puente-D\'{\i}az, et al \cite{Puente2020}. Furthermore, in supplementary
-information we show the transfer matrix trace calculations as a function of the
-wavelength and the incidence angle for the ST-C photonic structure using the TE and
-TM polarization. In Fig \ref{Fig4}(d) the calculated and measured reflectance
-corresponding to the structure ST-C, at different angles of incidence is compared.
-Although, the quasi omnidirectional band gap of the synthesized structure is
-slightly less than that calculated (located from 950 to 2750 nm), the measured PBG
-is almost twice as compared to the recently reported similar structures
+by Puente-D\'{\i}az, et al \cite{Puente2020}. Furthermore, in the supplementary
+information we show the trace of the transfer matrix as function of the
+wavelength and the incidence angle for the ST-C photonic structure for TE and
+TM polarizations.\notaL{¿Para qué ponemos esta información
+  suplementaria? ¿Qué aprenderá el lector de ella?} In Fig
+\ref{Fig4}(d) we compare the calculated and measured reflectance
+for the structure ST-C, at several angles of incidence.
+Although, the quasi omnidirectional wavelength range of the synthesized structure is
+slightly smaller than the calculated one, from 950 to 2750 nm, the measured PBG
+is almost twice as wide as those of recently reported similar structures
 (\cite{DelRio2018,Chavez2020}).
 
-Finally, table 2 shows some porous silicon based ODBMs designed to operate in the
+Finally, table 2 shows some porous silicon based ODBMs \notaL{Me
+  preocupa un poco la nomenclatura: si no son periódicos, ¿son espejos
+  de Bragg?} designed to operate in the
 NIR region and the width of the omnidirectional band gap is compared with the
@@
 based structures ST-B and ST-C have the widest gap width, being 1.8 times greater
-than recently reported works.
+than recently reported works.\notaL{Es justa la comparación? Ellos
+  estaban tratando de hacer un espejo de espectro muy amplio y no
+  pudieron hacerlo tan ancho como nosotros o simplemente estaban
+  haciendo otra cosa?}
 
@@
 
-We have demonstrated the formation of highly reflective PS multilayer photonic
-structures optimized using two types of design techniques for maximal reflectance
-and minimal thickness in the NIR region. With \textit{chirped}-type Bragg mirrors,
+We have designed, fabricated and characterized highly reflective PS multilayer photonic
+structures with a wide spectral range, optimized using two techniques for maximal reflectance
+and minimal thickness in the NIR region \notaL{Parte del trabajo no
+  fue NIR.} With \textit{chirped}-type
+Bragg\notaL{Tengo la duda sobre llamarles Bragg} mirrors,
 two regions of the electromagnetic spectrum were analyzed. The first region (350nm -
-1400 nm), optimized through an increasing function resulted in an average
-reflectance $>85\%$ with the quasi omnidirectional PBG of 360 nm centered at 1160 nm
-(980-1340 nm) for the angular range 0-60${{}^\circ}$ and more than 50$\%$ of
-reflectance from 550-980nm. The second structure was designed for 850-3000 nm
-wavelength range and the synthesized structure with optimized parameters resulted in
-the average reflectance of $~91\%$ with q-OD bandgap from 980 to 2780 nm and a
-thickness of 60.4 $\mu$m. The other design technique consisting of sub-mirrors
-stacks (designed at different wavelengths), was optimized for maximum average
-reflectance with respect to the percentage overlap of the PBG for each sub-mirror. A
-multilayer structure using the optimized parameters with sub-mirrors stack method
-was obtained with the average reflectance of $~95\%$ and a thickness of 41.5 $\mu$m.
-Furthermore, this structure revealed a 1800 nm q-OD PBG, centered at 1850 nm, in
-angular range 0-60${{}^\circ}$. Therefore, this second technique was found to be
-better due to the decreased thickness (by a factor of $~1.5$) of the framework and
+1400 nm), optimized through an increasing function resulted in a
+reflectance $R>0.85$ with a range of 360 nm centered at 1160 nm
+(980-1340 nm) for the angular range $0-60^\circ$ and $R>0.50$ of
+reflectance from 550-980nm. The second structure was designed for a
+wavelength range from 850-3000 nm
+and the synthesized structure with optimized parameters resulted in
+the average reflectance of $~91\%$ with q-OD \notaL{No definiste q-OD
+  nunca} bandgap from 980 to 2780 nm and a
+thickness of 60.4 $\mu$m. The other design technique consists of
+stacking sub-mirrors
+tuned to different wavelengths, and was optimized for a maximum average
+reflectance using  the overlap of the gap of succesive sub-mirrors as
+the optimization parameter. We obtained
+a reflectance $R>0.95$ and a thickness of 41.5 $\mu$m within a
+wavelength range of 1800 nm centered at 1850 nm, with  an
+angular range $0-60^\circ$. Therefore, we found this second technique to be
+better as it yields thinner structures by a factor of $~1.5$ and
 increased average reflectance. Additionally, the analysis techniques developed here
 can be used to optimize reflectance with other refractive index contrasts in PS
-multilayers or different other systems composed of other types of materials. Such
+multilayers or in systems composed of other types of materials. Such
 proposed structures could be used as mirrors for solar concentrators, flat focusing

### 2021-01-07 PaperVictor.tex
Revise abstract

@@
+% !TeX spellcheck = en_US
 \documentclass{article}
@@
 \newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
-\newcommand{\notaVCG}[1]{{\bf \em \color{orange}VCG: #1}}
+\newcommand{\notaV}[1]{{\bf \em \color{orange}VCG: #1}}
 \definecolor{Addtext}{RGB}{0,0,255}
@@
 can be synthesized by a simple electrochemical technique. We
-maximize the reflectance $\braket{R}$ \notaL{El promedio no depende
+maximize the average \notaV{Agregue} reflectance $\braket{R}$ \notaL{El promedio no depende
   de lambda ni theta, y prom es castellano}   of PS-based
-mirrors  averaged over a wide wavelength
+mirrors within \notaV{Agregue y quite "averaged over"} a wide wavelength
 and angular range, for different
@@
 electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
-structures and by \textit{stacking} sub-mirrors. We found \notaL{No
+structures and by \textit{stacking} sub-mirrors. We find \notaL{No
   estoy seguro del tiempo} that
-chirped structures were better suited for the Vis stacked
-sub-mirrors for the NIR region. We design, fabricate and test some
+chirped structures are more suitable for the Vis range, while stacked
+sub-mirrors are better for the NIR region. \notaV{Corregi oracion} We design, fabricate and test some
 optimized omnidirectional structures with less than 100
@@
 \notaL{Hay que checar que la puntuación vaya después de las citas,
-  para este estilo de citas entre corchetes} have
+  para este estilo de citas entre corchetes} \notaV{Comentario atendido} have
 reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
-TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al., \cite{Park2003}
+TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al. \cite{Park2003},
 used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
@@
 respectively, to obtain a 150 nm wide omnidirectional band centered at
-1750 nm. Furthermore, Jena et al., \cite{Jena2019}
+1750 nm. Furthermore, Jena et al. \cite{Jena2019},
 used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
@@
 multilayer systems it is usual to employ the transfer matrix
-method\notaL{reference}. Assuming the system is 1D, with variations
+method \notaL{reference} \cite{Pochi2005, Ariza2011} \notaV{Agregue dos referencias}. 
+Assuming the system is 1D, with variations
 only along the $z$ directions, and that the polarization of light is either
@@
 where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
-  explicarlas, y no creo que sean importantes para el lector} are the elements
+  explicarlas, y no creo que sean importantes para el lector} \notaV{Tiene raz\'{o}, esto se debe diferenciar en la informacion suplementaria} are the elements
 of the transfer matrix which transfer
@@
 TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
-  estaban en la fórmula} The complex refractive index of the porous
+  estaban en la fórmula} \notaV{Realmente inclu\'{i} la transmitancia solo por completez (no inclu\'{i} c\'{a}lculo alguno)} The complex refractive index of the porous
 layers were obtained through the Bruggeman's effective medium theory, which
@@
 dispersion relation is analyzed.
-}
+} \notaV{De acuerdo}
 

### 2021-01-07 PaperVictor.tex
Revise abstr

@@
 are consequently organized into photonic bands. Analogous to electrons in a
-crystal, their propagation will be forbidden if their energy lies
+crystal, their propagation is \notaV{Quite "will be"} forbidden if their energy lies
 within certain regions known as photonic band gaps (PBG's). Thus, the
@@
 corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
-thicknesses of is quarter-wavelength
-$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at some chosen nominal
+thicknesses are \notaV{Modifique "of is"} quarter-wavelength
+$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a \notaV{Quite "some chosen"} nominal
 wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
@@
 the layers as a function of their depth, producing
-\textit{chirped}-type \cite{Zipock1997}
-structures. An alternative is to stack BM's, such that their PBG
-overlap each other, resulting in a wider high-reflection band
-\cite{Xifre2009}.
+\textit{chirped}-type structures \cite{Zipock1997}.
+Another alternative is to stack BMs, in such a way that their reflection bands partially
+overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
+\notaV{Se modifico la oracion "An alternative is to stack BM's, such that their PBG
+overlap each other, resulting in a wider high-reflection band"}. 
 \notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
@@
 
-Till now, different deposition techniques have been used to obtain omnidirectional
-BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
-electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
+On the other hand, different fabrication techniques have been used to obtain omnidirectional
+mirrors (ODM) that operate on the visible and/or near infrared (Vis-NIR) range of the
+electromagnetic spectrum. \notaV{Se modifico la oracion "Till now, different deposition 
+techniques have been used to obtain omnidirectional BM (ODBM) that operate on 
+the visible and near infrared (Vis-NIR) range of the electromagnetic spectrum."} 
+For example, Chen et al. \cite{Chen1999},
 \notaL{Hay que checar que la puntuación vaya después de las citas,
-  para este estilo de citas entre corchetes} \notaV{Comentario atendido} have
-reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
-TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al. \cite{Park2003},
-used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
-followed by its conversion to
-GaAs/Al$_{2}$O$_{3}$ layers by selective
-oxidation of the AlAs layers, to obtain an ODBM with a band from 710 to 950
-nm. On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
+  para este estilo de citas entre corchetes} reported the fabrication of a 
+6-pair TiO$_{2}$/SiO$_{2}$ structure \notaV{Se cambio "have reported"} with
+ an OD band of about 70 nm in the NIR range, employing sol-gel deposition 
+method. Park et al. \cite{Park2003}, used molecular beam epitaxy to 
+grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
+GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs 
+layers, to obtain an OD with a band from 710 to 950 nm. 
+On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
 coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
@@
 _{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
-layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved ODBM from
+layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
 592 to 668 nm. However, these techniques are expensive and they
 require sophisticated equipment and long fabrication times. Using PS
-is an attractive alternative, as PS may be fabricated by simple
+is an attractive alternative, since it can be easily manufactured by 
+electrochemical etching of crystalline Si in a hydrofluoric 
+acid based electrolyte, to obtain a sponge-like nanostructure composed 
+of Si and air. By modulating the supplied current and its application 
+time to the electrochemical reaction, it is possible to obtain 
+multilayer structures allowing for fabrication ODM \cite{Xifre2015,Pavesi2000}.
+\notaV{Se replanteo la idea "as PS may be fabricated by simple
 electrochemical etching during short times of
@@
 ease of fabrication of PS make it an excellent candidate to develop
-multilayered optical devices \cite{Xifre2015,Pavesi2000}.
+multilayered optical devices."}
 Although optical filters \cite{Estevez2009,Ariza2014} are the most common
@@
 for photoluminescence control \cite{Antunez2014}. Recently, the study of
-quasi-omnidirectional Bragg mirrors has
-increased due to their possible application
-as a flat lens \cite{Kozar2017,Cheng2018}.\notaL{Lens o mirror, no
-  puede ser ambas? De verdad esto es lo que más lo ha popularizado?}
-PS based dielectric
-optical filters, quasi-ODBM and ODBM have been extensively studied in different
+chirped multilayer structures \notaV{Modifique "quasi-omnidirectional Bragg mirrors"} has
+increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
+\notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
+PS based dielectric optical filters, quasi-ODBM and ODBM have been extensively studied in different
 regions of the electromagnetic spectrum, such as the ultraviolet (UV)
-\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR)
-\cite{Bruyant2003}. However, to obtain the desirable high index of refraction
+\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003}. 
+However, to obtain the desirable high index of refraction
 contrast, layers of high porosity have to be employed, so that the
@@
 very large number of layers, unfeasible. For this reason, in this work
-we study different strategies to produce photonic mirrors
-that have a large reflectance over a wide band-width with a relatively
-small thickness and refractive index contrast. Specifically, our aim
-is to maximize the reflectance $R$ averaged over a wide range of
-wavelengths $\lambda$ and angles of incidence $\theta$.
+we study different strategies to produce multilayer \notaV{photonic} mirrors
+that have a large reflectance omnidirectional band \notaV{over a wide band-width}
+with relatively small thickness and refractive index contrast. 
+\notaV{Se omite la frase "Specifically, our aim is to maximize the 
+reflectance $R$ averaged over a wide range of wavelengths $\lambda$ 
+and angles of incidence $\theta$", la idea general esta en la oracion anterior}
 

### 2021-01-08 PaperVictor.tex
Revise Seccion de teoria

@@
 \newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
-\newcommand{\notaV}[1]{{\bf \em \color{orange}VCG: #1}}
+\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
 \definecolor{Addtext}{RGB}{0,0,255}
@@
 
-\section{Theory}\label{s:theory}
+\section{Numerical simulation} \label{s:theory}
+
+\notaV{Propuesto por Dr. David, se omite "Theory"}
 
 \notaL{Pon etiquetas a todo para poderlo referir}
-For the analysis of the propagation of electromagnetic fields through
-multilayer systems it is usual to employ the transfer matrix
-method \notaL{reference} \cite{Pochi2005, Ariza2011} \notaV{Agregue dos referencias}. 
-Assuming the system is 1D, with variations
-only along the $z$ directions, and that the polarization of light is either
-transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
-  sería de 4x4}, the
-transfer matrix $M\left(z_{2},z_{1}\right)$ is
-a 2x2 matrix that relates the components of the electric $E_{\| }$
-and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
-evaluated at $z_2$ to their value at $z_{1}$,
+
+\notaV{Parrafos reescritos por Dr. David}
+
+In this paper, two techniques are developed to design 
+multilayer photonic structures. In the first, the wavelength 
+($\lambda _{j}$), at which the $j$-th period of the structure 
+is designed, is modulated by an increasing function. This can 
+be as simple or complex as you like. The proposed function was 
+optimized with the Minuit module of PDL (Perl Data Language) \cite{minuit}. 
+The other technique for proposing highly reflective structures 
+over a wide region of the electromagnetic spectrum is to stack
+sub-mirrors tuned to different wavelengths. For each 
+sub-mirror the dispersion relation is analyzed.
+
+For the analysis of the propagation of electromagnetic fields 
+through multilayer systems, we employ the transfer matrix 
+method based on Puente-Díaz et al., formalism \cite{Puente2020}. 
+In spite some equivalent formulations have been proposed to 
+obtain the optical properties of multilayer systems 
+\cite{Mochan1987,Ortiz2020,Chavez2020}, here we use a 
+recently developed formalism for the numerically stable 
+calculation of the reflectance of large multilayer systems. 
+Briefly describing, 
+we assume a 1D system with variations along the $z$ direction 
+and consider an incident linearly polarized beam of light 
+(either TE or TM polarization) that propagates throughout 
+the structure. The reflectance and transmittance are given by 
+$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$, respectively, with
+\begin{equation}
+	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
+		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
+\end{equation}%
+and
+\begin{equation}
+	t=\frac{2Z_{\zeta
+	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
+\end{equation}%
+where $Z_0$ and $Z_s$ are the impedances of the vacuum 
+and the substrate, respectively. $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ is choosen for 
+TE polarization while $\beta=\text{Re}Z_{s}/ 
+\text{Re}Z_{0}$ for TM polarization. The upper sign 
+$-$ in Eq. (\ref{rBloch}) and the subscript 
+$\zeta =s$ in Eq. (\ref{tBloch}) are chosen for 
+the case of TE polarization, while the lower sign 
+$+$ and the subscript $\zeta =0$ correspond to TM 
+polarization. Furthermore, $M_{ij}$ are the elements
+of the transfer matrix which relates
+the electromagnetic fields of all interfaces in the structure through
+\begin{equation}
+	M=\frac{1}{Z^{+}-Z^{-}}\left( 
+	\begin{array}{cc}
+		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  & 
+		-2iZ^{+}Z^{-}\sin KD \\ 
+		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
+		iKD\right) 
+	\end{array}%
+	\right) \text{.}  \label{MsBloch}
+\end{equation}
+In this case, $Z^{\pm }$ can be obtained as 
+\begin{equation}
+	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
+\end{equation}%
+being 
+\begin{equation}
+	\Lambda _{-}=\frac{1}{2}\text{tr}\widetilde{M}\pm i\sqrt{1-\left( \text{tr}\widetilde{M}/2\right)
+		^{2}}\text{,}  \label{LBloch}
+\end{equation}%
+where the sign that satisfies the relation $\left\vert \Lambda
+_{-}\right\vert >1$, and $\Lambda _{+}=\Lambda _{-}^{-1}$ is chosen.
+Moreover, tr corresponds to the trace and $\widetilde{M}_{ij}$ $\left( i,j=1,2\right) 
+$ denote the elements of the usual transfer matrix $\widetilde{M}$ of the $N$-layer
+system, that is, 
+\begin{equation}
+	\widetilde{M} =\Pi _{j=1}^{N}%
+	\begin{bmatrix}
+		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\ 
+		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
+	\end{bmatrix}%
+	,  \label{Mcoef}
+\end{equation}%
+where 
+\begin{equation}
+	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
+\end{equation}%
+is the normal component (to the interfaces) of the wave vector, $Z_{j}$ is
+the corresponding surface impedance, $Y_{j}=1/Z_{j}$ is the surface
+admittance, $\epsilon _{j}=n_{j}^{2}$ is the permitivity (for simplicity we
+assumed all media were nonmagnetic, with permeability $\mu _{i}=1$), $%
+q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
+the wavelength $\lambda $ and 
+\begin{equation}
+	Q=n_{0}q\sin \theta _{i}  \label{Snell}
+\end{equation}%
+is the projection of wavevector onto the interfaces, 
+which is conserved according to Snell's law, with 
+$\theta _{i}$ the angle of incidence. The surface 
+impedances are given by $Z_{j}=q/k_{j}$ for TE 
+polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for 
+TM polarization. Moreover, sub-index $0$ and $s$ 
+refer to the incident and substrate media, respectively.
+The complex refractive index of the porous layers were 
+obtained through the Bruggeman's effective medium 
+theory, which has been reported to adequately reproduce 
+the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.
+
+\notaV{Se omite "For the analysis of the propagation of 
+electromagnetic fields through multilayer systems it is 
+usual to employ the transfer matrix method \notaL{reference} 
+\cite{Pochi2005, Ariza2011}. Assuming the system is 1D, with 
+variations only along the $z$ directions, and that the 
+polarization of light is either transverse electric (TE) or 
+transverse magnetic (TM)\notaL{si no, la matriz   sería de 4x4}, 
+the transfer matrix $M\left(z_{2},z_{1}\right)$ is a 2x2 matrix 
+that relates the components of the electric $E_{\| }$ and 
+magnetic  $H_{\|}$ fields parallel to the $xy$ plane evaluated 
+at $z_2$ to their value at $z_{1}$,
 \begin{equation*}
@@
 \end{equation*}%
-Many equivalent formulations have been proposed to obtain and use $M$
-\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
-for the numerically stable calculation of the reflectance of large
-multilayer systems, as
-proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
-supplementary information. The
-explicit expressions for the optical coefficients are:
+Many equivalent formulations have been proposed to obtain and use $M$ \cite{Mochan1987,Ortiz2020,Chavez2020}.
+Here we use a recently developed formalism for the numerically stable calculation of the reflectance of large multilayer systems, as proposed by Puente-Díaaz, et al.
+\cite{Puente2020}, summarized in the supplementary information.
+The explicit expressions for the optical coefficients are:
 \begin{equation}
@@
 \end{equation}%
-where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
-  explicarlas, y no creo que sean importantes para el lector} \notaV{Tiene raz\'{o}, esto se debe diferenciar en la informacion suplementaria} are the elements
-of the transfer matrix which transfer
-the fields from its surface interface with vacuum at $z_0$ towards the
-substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
-surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
-of the reflected and transmitted fields, where we choose the $F$'s as electric
-fields for (TE) polarization and magnetic fields
-for transverse magnetic polarization (TM). The upper sign $-$ in
-Eq. (\ref{rBloch}) and the subscript $\alpha =s$
-in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
-the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
-polarization, respectively.
-The reflectance is given by
-$R=|r|^{2}$ and the
-transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
-=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
-TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
-  estaban en la fórmula} \notaV{Realmente inclu\'{i} la transmitancia solo por completez (no inclu\'{i} c\'{a}lculo alguno)} The complex refractive index of the porous
-layers were obtained through the Bruggeman's effective medium theory, which
-has been reported to adequately reproduce the PS optical parameters
-\cite{Giusseppe2011,Pap2006,Estrada2018}.
-
-\notaL{Creo que esto debería estar más adelante:
-  After the next section, two techniques are developed to design multilayer
-photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
-the $j$-th period of the structure is designed, is modulated by an
-increasing function. This can be as simple or complex as you like. The
-proposed function was optimized with the Minuit module of PDL (Perl Data
-Language) \cite{minuit}. The other technique for proposing highly reflective
-structures over a wide region of the electromagnetic spectrum is to stack
-sub-mirrors tuned to different wavelengths. For each sub-mirror the
-dispersion relation is analyzed.
-} \notaV{De acuerdo}
+where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido 
+necesario explicarlas, y no creo que sean importantes para 
+el lector} are the elements of the transfer matrix which 
+relates the electromagnetic fields of all interfaces in 
+the structure through transfer the fields from its surface 
+interface with vacuum at $z_0$ towards the substrate at $z_s$,
+$Z_0$ is the surface impedance of vacuum and $Z_s$ is the 
+surface impedance of the substrate, and we define $r=F_r/F_i$ 
+and $t=F_t/F_i$ in terms of the reflected and transmitted 
+fields, where we choose the $F$'s as electric fields for 
+(TE) polarization and magnetic fields for transverse 
+magnetic polarization (TM).  The upper sign $-$ in Eq. 
+(\ref{rBloch}) and the subscript $\alpha =s$ in Eq. 
+(\ref{tBloch}) are chosen for the case of TE polarization, 
+while the lower sign $+$ and the subscript $\zeta =0$ 
+correspond to TM polarization, respectively. The reflectance 
+is given by $R=|r|^{2}$ and the transmittance by 
+$T=\beta \left\vert  t\right\vert ^{2}$ with 
+$\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization 
+and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for TM 
+polarization.\notaL{En el cálculo, ¿tomaste las partes 
+reales? No estaban en la fórmula} The complex refractive 
+index of the porous layers were obtained through the 
+Bruggeman's effective medium theory, which has been 
+reported to adequately reproduce the PS optical 
+parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.}
 

### 2021-01-08 PaperVictor.tex
Revise parte experimental

@@
 PC behaves as a mirror if illuminated by light with frequencies
-withinin a PBG. For several applications it is useful to fabricate
+within in a PBG. For several applications it is useful to fabricate
 {\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
@@
 wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
-With this electrolyte, the minimum and maximum porosities that can be
-obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de
-  aquí, pues lo discutes abajo:(gravimetrically obtained)}, using
-current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$,
-respectively. However, as it is not desirable to use very high
+\notaV{Se omite "With this electrolyte, the minimum and maximum porosities that can be obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de   aquí, pues lo discutes abajo:(gravimetrically obtained)}, using current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$, respectively.}
+However, as it is not desirable to use very high
 porosity contrasts due to structure fragility and electrolyte
 diffusivity problems \cite{Ariza2011}, the current
-densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, with
-corresponding
-porosities of 51\% and 76\%, respectively. The porosity was calibrated
-\notaL{Creo que no muestras curvas de calibración: calibration curves were
-acquired} through a gravimetric technique as follows: single layers of porous
+densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, 
+with corresponding porosities of 51\% and 76\%, respectively.
+\notaV{Se reescribe "The porosity was calibrated \notaL{Creo que no 
+muestras curvas de calibración: calibration curves were acquired}
+through a gravimetric technique as follows: single layers of porous
 silicon were synthesized under similar conditions applying a constant
-current for a time \notaL{cuánto tiempo para la calibración?}  and were weighed to
-obtain their mass $m_i$
-before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
-dissolving the already formed porous silicon layer ($m_{3}$), to obtain
-the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.
-The etching
-rate of PS was obtained by synthetizing single layers under similar
-conditions and measuring their thicknesses through Scanning Electron
-Microscopy (SEM). Absolute reflectivity measurements were carried out
-with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
-angle universal reflectance accessory (URA) for different incident
-angles $\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$,
-$40^{\circ }$, $50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
-minimum values of $\theta _{i}$ were constrained by the angular range of the
+current for a time \notaL{cuánto tiempo para la calibración?} and
+were weighed to obtain their mass $m_i$ before ($m_{1}$) and after 
+($m_{2}$) the electrochemical attack, and after dissolving the already
+formed porous silicon layer ($m_{3}$), to obtain the porosity as 
+$p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.}
+The porosity of the layers was obtained by a previous calibration
+curve through a gravimetric technique \cite{Pap2006} 
+\notaV{Si es que se adjunta (further details see supplementary
+information), sino ya se ha mencionado en otros articulos}. The 
+etching rate of PS was obtained by synthetizing single layers under 
+similar conditions and measuring their thicknesses through Scanning 
+Electron Microscopy (SEM). Absolute reflectivity measurements were 
+carried out with a Perkin Elmer Lambda 950 UV/Visible 
+spectrophotometer with a variable angle universal reflectance 
+accessory (URA) for different incident angles $\theta _{i}=10^{\circ 
+}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and 
+$60^{\circ }$ using non-polarized light. The maximum and minimum 
+values of $\theta _{i}$ were constrained by the angular range of the 
 equipment accessory URA.

### 2021-01-17 PaperVictor.tex
Segunda version revisada

--- 2021-01-07 PaperVictor.tex
@@
 \usepackage{cite}
-\usepackage{authblk}
-\usepackage{xcolor}
-\usepackage{braket}
 \newif{\ifmover}
 \newif{\ifquitar}
+\usepackage{authblk}
 \renewcommand{\Affilfont}{\small}
+\usepackage{xcolor}
 \newcommand{\notaL}[1]{{\color{orange}L: #1}}
 \newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
-\newcommand{\notaV}[1]{{\bf \em \color{orange}VCG: #1}}
+\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
 \definecolor{Addtext}{RGB}{0,0,255}
@@
 Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
-\affil[3]{Facultad de Ciencias Fìsico Matem\'{a}ticas,
+\affil[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
 Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
@@
 \affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
-Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
+Potos\'{i}, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
 S.L.P., 78210, M\'{e}xico.}
@@
 devices based on multilayered structures, since high and low porosity layers
-can be synthesized by a simple electrochemical technique. We
-maximize the average \notaV{Agregue} reflectance $\braket{R}$ \notaL{El promedio no depende
-  de lambda ni theta, y prom es castellano}   of PS-based
-mirrors within \notaV{Agregue y quite "averaged over"} a wide wavelength
-and angular range, for different
-porosity contrasts, and we minimize their thickness. Optimization is
-performed in the visible (Vis) and near infrarred (NIR) regions of the
-electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
-structures and by \textit{stacking} sub-mirrors. We find \notaL{No
-  estoy seguro del tiempo} that
-chirped structures are more suitable for the Vis range, while stacked
-sub-mirrors are better for the NIR region. \notaV{Corregi oracion} We design, fabricate and test some
-optimized omnidirectional structures with less than 100
-periods.
+can be synthesized by a simple electrochemical technique. In the present work, the 
+average reflectance $<$R$>$ of PS-based mirrors is maximized within a wide 
+wavelength and angular range, for different porosity contrasts. Optimization is 
+performed to maximize the reflectance for minimum  thickness of the structure in the 
+visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The 
+mirrors are designed using \textit{chirped}-type structures and \textit{stacking} 
+sub-mirrors. The chirped structures are found to be more suitable for the Vis range, 
+while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication 
+and testing of some optimized omnidirectional structures with less than 100 periods has 
+been demonstrated.
 \end{abstract}
@@
 
-Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
-  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
-structures have been extensively investigated due
+Photonic crystal (PC)-based structures have been extensively investigated due
 to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
@@
 are consequently organized into photonic bands. Analogous to electrons in a
-crystal, their propagation is \notaV{Quite "will be"} forbidden if their energy lies
+crystal, their propagation is forbidden if their energy lies
 within certain regions known as photonic band gaps (PBG's). Thus, the
 PC behaves as a mirror if illuminated by light with frequencies
-withinin a PBG. For several applications it is useful to fabricate
+within in a PBG. For several applications it is useful to fabricate
 {\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
@@
 corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
-thicknesses are \notaV{Modifique "of is"} quarter-wavelength
-$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a \notaV{Quite "some chosen"} nominal
+thicknesses are quarter-wavelength
+$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
 wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
@@
 overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
-\notaV{Se modifico la oracion "An alternative is to stack BM's, such that their PBG
-overlap each other, resulting in a wider high-reflection band"}. 
-\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
-  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
-  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
-  que no son periódicos, tal vez 'brecha prohibida' no es un buen
-  término. Más bien, queremos hablar del ancho de banda del espejo,
-  i.e., la región en que es buen reflector.}
 
-On the other hand, different fabrication techniques have been used to obtain omnidirectional
-mirrors (ODM) that operate on the visible and/or near infrared (Vis-NIR) range of the
-electromagnetic spectrum. \notaV{Se modifico la oracion "Till now, different deposition 
-techniques have been used to obtain omnidirectional BM (ODBM) that operate on 
-the visible and near infrared (Vis-NIR) range of the electromagnetic spectrum."} 
-For example, Chen et al. \cite{Chen1999},
+On the other hand, different fabrication techniques have been used to obtain omnidirectional (OD) mirrors that operate on the visible and/or near infrared (Vis-NIR) range of the electromagnetic spectrum.
+For example, Chen et al.
+\cite{Chen1999},
 \notaL{Hay que checar que la puntuación vaya después de las citas,
 	para este estilo de citas entre corchetes} reported the fabrication of a 
-6-pair TiO$_{2}$/SiO$_{2}$ structure \notaV{Se cambio "have reported"} with
+6-pair TiO$_{2}$/SiO$_{2}$ structure with
 an OD band of about 70 nm in the NIR range, employing sol-gel deposition 
@@
 of Si and air. By modulating the supplied current and its application 
-time to the electrochemical reaction, it is possible to obtain 
-multilayer structures allowing for fabrication ODM \cite{Xifre2015,Pavesi2000}.
-\notaV{Se replanteo la idea "as PS may be fabricated by simple
-electrochemical etching during short times of
-crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
-sponge-like nanostructure composed of Si and air. By modulating in
-time the applied current, the porosity of the PS, and thus its
-refractive index, can be modulated
-along its depth. This allows the design and fabrication of 1D-PC's with PS, to
-control the propagation of light in a dielectric medium. The low cost and
-ease of fabrication of PS make it an excellent candidate to develop
-multilayered optical devices."}
+time during the electrochemical reaction, it is possible to obtain 
+multilayer structures allowing for fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
 Although optical filters \cite{Estevez2009,Ariza2014} are the most common
@@
 for photoluminescence control \cite{Antunez2014}. Recently, the study of
-chirped multilayer structures \notaV{Modifique "quasi-omnidirectional Bragg mirrors"} has
+chirped multilayer structures has
 increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
 \notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
-PS based dielectric optical filters, quasi-ODBM and ODBM have been extensively studied in different
+PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
 regions of the electromagnetic spectrum, such as the ultraviolet (UV)
-\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003}. 
+\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} region. 
 However, to obtain the desirable high index of refraction
-contrast, layers of high porosity have to be employed, so that the
-resulting structures may be fragile, making large structures, with a
+contrast, layers of high porosity have to be employed, which makes the
+resulting structures relatively fragile. In addition, use of high porosity makes the fabrication of large structures, with a
 very large number of layers, unfeasible. For this reason, in this work
-we study different strategies to produce multilayer \notaV{photonic} mirrors
-that have a large reflectance omnidirectional band \notaV{over a wide band-width}
+we study different strategies to produce multilayered mirrors
+with high reflectance omnidirectional band 
 with relatively small thickness and refractive index contrast. 
@@
 fabrication of these structures. In Sec. \ref{s:res} we present the numerical
-and experimental results for our proposed structures and compare
-them to previous reports. We obtained significantly larger band-widths
-with significantly thinner structures. \notaL{Dejo para resultados y
+and experimental results corresponding to our proposed structures and compare
+them to previous reports. We obtained significantly large band-widths
+with relatively thinner structures than reported before. \notaL{Dejo para resultados y
 	conclusiones los detalles de con quién comparamos y qué salió.}
@@
 
-\section{Theory}\label{s:theory}
+\section{Numerical simulation} \label{s:theory}
 
+\notaV{Nombre de la sección propuesta por Dr. David}
 \notaL{Pon etiquetas a todo para poderlo referir}
-For the analysis of the propagation of electromagnetic fields through
-multilayer systems it is usual to employ the transfer matrix
-method \notaL{reference} \cite{Pochi2005, Ariza2011} \notaV{Agregue dos referencias}. 
-Assuming the system is 1D, with variations
-only along the $z$ directions, and that the polarization of light is either
-transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
-  sería de 4x4}, the
-transfer matrix $M\left(z_{2},z_{1}\right)$ is
-a 2x2 matrix that relates the components of the electric $E_{\| }$
-and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
-evaluated at $z_2$ to their value at $z_{1}$,
-\begin{equation*}
-\left(
-\begin{array}{c}
-E_{\|} \\
-H_{\| }%
-\end{array}%
-\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
-\begin{array}{c}
-E_{\| } \\
-H_{\| }%
-\end{array}%
-\right) _{z_{1}}.
-\end{equation*}%
-Many equivalent formulations have been proposed to obtain and use $M$
-\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
-for the numerically stable calculation of the reflectance of large
-multilayer systems, as
-proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
-supplementary information. The
-explicit expressions for the optical coefficients are:
+\notaV{Parrafos reescritos por Dr. David}
+
+In this paper, two techniques are developed to design 
+multilayer photonic structures. In the first, the wavelength 
+($\lambda _{j}$), at which the $j$-th period of the structure 
+is designed, is modulated by an increasing function. This can 
+be as simple or complex as you like. The proposed function was used to
+optimize $<$R$>$ with the Minuit module of PDL (Perl Data Language) \cite{minuit}. 
+The other technique for proposing highly reflective structures 
+over a wide region of the electromagnetic spectrum is to stack
+sub-mirrors tuned to different wavelengths. For each 
+sub-mirror the dispersion relation is analyzed.
+
+For the analysis of the propagation of electromagnetic fields 
+through multilayer systems, we employ the transfer matrix 
+method based on Puente-Díaz et al. formalism \cite{Puente2020}. 
+In spite some equivalent formulations have been proposed to 
+obtain the optical properties of multilayer systems 
+\cite{Mochan1987,Ortiz2020,Chavez2020}, here we use a 
+recently developed formalism for the numerically stable 
+calculation of the reflectance of large multilayer systems. 
+Briefly describing, 
+we assume a 1D system with variations along the $z$ direction 
+and consider an incident linearly polarized beam of light 
+(either TE or TM polarization) that propagates throughout 
+the structure. The reflectance and transmittance are given by 
+$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$,
+respectively, with \cite{Puente2020}
 \begin{equation}
@@
 \begin{equation}
-t=\frac{2Z_{\alpha
+	t=\frac{2Z_{\zeta
 	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
 \end{equation}%
-where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
-  explicarlas, y no creo que sean importantes para el lector} \notaV{Tiene raz\'{o}, esto se debe diferenciar en la informacion suplementaria} are the elements
-of the transfer matrix which transfer
-the fields from its surface interface with vacuum at $z_0$ towards the
-substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
-surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
-of the reflected and transmitted fields, where we choose the $F$'s as electric
-fields for (TE) polarization and magnetic fields
-for transverse magnetic polarization (TM). The upper sign $-$ in
-Eq. (\ref{rBloch}) and the subscript $\alpha =s$
-in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
-the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
-polarization, respectively.
-The reflectance is given by
-$R=|r|^{2}$ and the
-transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
-=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
-TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
-  estaban en la fórmula} \notaV{Realmente inclu\'{i} la transmitancia solo por completez (no inclu\'{i} c\'{a}lculo alguno)} The complex refractive index of the porous
-layers were obtained through the Bruggeman's effective medium theory, which
-has been reported to adequately reproduce the PS optical parameters
-\cite{Giusseppe2011,Pap2006,Estrada2018}.
+where $Z_0$ and $Z_s$ are the impedances of the vacuum 
+and the substrate, respectively. $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ is chosen for 
+TE polarization while $\beta=\text{Re}Z_{s}/ 
+\text{Re}Z_{0}$ for TM polarization. The upper sign 
+$-$ in Eq. (\ref{rBloch}) and the subscript 
+$\zeta =s$ in Eq. (\ref{tBloch}) are chosen for 
+the case of TE polarization, while the lower sign 
+$+$ and the subscript $\zeta =0$ correspond to TM 
+polarization. Moreover, sub-index $0$ and $s$ 
+refer to the incident and substrate media, respectively.
+Furthermore, $M_{ij}$ are the elements
+of the transfer matrix which relates
+the electromagnetic fields of all interfaces in the structure through
 
-\notaL{Creo que esto debería estar más adelante:
-  After the next section, two techniques are developed to design multilayer
-photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
-the $j$-th period of the structure is designed, is modulated by an
-increasing function. This can be as simple or complex as you like. The
-proposed function was optimized with the Minuit module of PDL (Perl Data
-Language) \cite{minuit}. The other technique for proposing highly reflective
-structures over a wide region of the electromagnetic spectrum is to stack
-sub-mirrors tuned to different wavelengths. For each sub-mirror the
-dispersion relation is analyzed.
-} \notaV{De acuerdo}
+\begin{equation}
+\resizebox{\textwidth}{!}{$\displaystyle{
+	M=\frac{1}{Z^{+}-Z^{-}} \left( 
+	\begin{array}{cc}
+		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  & 
+		-2iZ^{+}Z^{-}\sin KD \\ 
+		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
+		iKD\right) 
+	\end{array}%
+	\right) \text{.}}$}  
+\label{MsBloch}
+\end{equation}
+%}
+In this case, $Z^{\pm }$ can be obtained as 
+\begin{equation}
+	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
+\end{equation}%
+being 
+\begin{equation}
+	\Lambda _{-}=\frac{1}{2}\text{tr}\widetilde{M}\pm i\sqrt{1-\left( \text{tr}\widetilde{M}/2\right)
+		^{2}}\text{,}  \label{LBloch}
+\end{equation}%
+where the sign that satisfies the relation $\left\vert \Lambda
+_{-}\right\vert >1$, and $\Lambda _{+}=\Lambda _{-}^{-1}$ is chosen.
+Moreover, tr corresponds to the trace and $\widetilde{M}_{ij}$ $\left( i,j=1,2\right) 
+$ denote the elements of the usual transfer matrix $\widetilde{M}$ of the $N$-layer
+system, that is, 
+\begin{equation}
+	\widetilde{M} = \prod \limits_{j=1}^{N}%
+	\begin{bmatrix}
+		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\ 
+		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
+	\end{bmatrix}%
+	,  \label{Mcoef}
+\end{equation}%
+where 
+\begin{equation}
+	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
+\end{equation}%
+is the normal component (to the interfaces) of the wave vector, $Z_{j}$ is
+the corresponding surface impedance, $Y_{j}=1/Z_{j}$ is the surface
+admittance, $\epsilon _{j}=n_{j}^{2}$ is the permitivity (for simplicity we
+assumed all media were nonmagnetic, with permeability $\mu _{i}=1$), $%
+q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
+the wavelength $\lambda $ and 
+\begin{equation}
+	Q=n_{0}q\sin \theta _{i}  \label{Snell}
+\end{equation}%
+is the projection of wavevector onto the interfaces, 
+which is conserved according to Snell's law, with 
+$\theta _{i}$ the angle of incidence. The surface 
+impedances are given by $Z_{j}=q/k_{j}$ for TE 
+polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for 
+TM polarization. The complex refractive index of the porous layers were 
+obtained through the Bruggeman's effective medium 
+theory, which has been reported to adequately reproduce 
+the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.
 
@@
 wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
-With this electrolyte, the minimum and maximum porosities that can be
-obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de
-  aquí, pues lo discutes abajo:(gravimetrically obtained)}, using
-current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$,
-respectively. However, as it is not desirable to use very high
+However, as it is not desirable to use very high
 porosity contrasts due to structure fragility and electrolyte
 diffusivity problems \cite{Ariza2011}, the current
-densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, with
-corresponding
-porosities of 51\% and 76\%, respectively. The porosity was calibrated
-\notaL{Creo que no muestras curvas de calibración: calibration curves were
-acquired} through a gravimetric technique as follows: single layers of porous
-silicon were synthesized under similar conditions applying a constant
-current for a time \notaL{cuánto tiempo para la calibración?}  and were weighed to
-obtain their mass $m_i$
-before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
-dissolving the already formed porous silicon layer ($m_{3}$), to obtain
-the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.
-The etching
-rate of PS was obtained by synthetizing single layers under similar
-conditions and measuring their thicknesses through Scanning Electron
-Microscopy (SEM). Absolute reflectivity measurements were carried out
-with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
-angle universal reflectance accessory (URA) for different incident
-angles $\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$,
-$40^{\circ }$, $50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
-minimum values of $\theta _{i}$ were constrained by the angular range of the
+densities were chosen as 35 and 305 $\text{mA}/\text{cm}^{2}$, 
+with corresponding porosities of 51\% and 76\%, respectively.
+The porosity of the layers was obtained by a previous calibration
+curve through a gravimetric technique \cite{Pap2006}. The 
+etching rate of PS was obtained by synthetizing single layers under 
+similar conditions and measuring their thicknesses through Scanning 
+Electron Microscopy (SEM). Absolute reflectivity measurements were 
+carried out with a Perkin Elmer Lambda 950 UV/Visible 
+spectrophotometer with a variable angle universal reflectance 
+accessory (URA) for different incident angles $\theta _{i}=10^{\circ 
+}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and 
+$60^{\circ }$ using non-polarized light. The maximum and minimum 
+values of $\theta _{i}$ were constrained by the angular range of the 
 equipment accessory URA.
@@
 
-In this section we presents optimized calculations of the reflectance
+In this section we present optimized calculations of the reflectance
 of different multilayered omnidirectional wide-band mirrors and we
-compare the results to spectra taken from
+compare the results with experimental spectra taken from
 the corresponding samples at several angles of
@@
 
-\notaL{Quizás esto se pueda incluir por aquí.:
-  After the next section, two techniques are developed to design multilayer
-photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
-the $j$-th period of the structure is designed, is modulated by an
-increasing function. This can be as simple or complex as you
-like. {\tiny The
-proposed function was optimized with the Minuit module of PDL (Perl Data
-Language) \cite{minuit}.} The other technique for proposing highly reflective
-structures over a wide region of the electromagnetic spectrum is to stack
-sub-mirrors tuned to different wavelengths. For each sub-mirror the
-dispersion relation is analyzed.
-}
 \subsection{Chirped-type Bragg mirrors}\label{ss:chirped}
@@
 \begin{equation}
-\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f(j/N_p)),\label{Dis}
+\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
 \end{equation}%
-where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and {\em
-  design} wavelengths respectively, $N_p$ is the index of the deepst
-pair of layers and $f(x)$ is some smooth function
-that goes from 0 to 1 as its argument goes from surface ($x=0$) to the
-substrate ($x=1)$. We only consider increasing functions $f$ due to
-the high absorption of PS in the ultraviolet region
-which decreases in the visible and becomes negligible in the near
-infrared, so, the
-first periods are syntonized in the UV-Vis regions. We consider the
+where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
+maximum {\em design} wavelengths respectively, $N_p$ is the number of periods in the structure and $f(\xi)$ is some smooth function that 
+goes from 0 to 1 as its argument goes from surface ($\xi=0$) to the 
+substrate ($\xi=1)$. We only consider increasing functions $f$ due to 
+the high absorption of PS in the ultraviolet region which decreases in 
+the visible and becomes negligible in the near infrared, so, the first 
+periods are syntonized in the UV-Vis regions. We consider the 
 following classes of functions:
 \begin{equation}
-f_{1}\left( x\right) =x^{\alpha },  \label{F1}
+f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
 \end{equation}
 \begin{equation}
-f_{2}\left( x\right) =A\left( x^{\alpha }+x^{\beta}\right)
+f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
 \label{F2}
@@
 \begin{equation}
-f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
+f_{3}\left(\xi\right) =Ax^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
 \end{equation}
-where $\alpha$, $\beta$ and $A$ are parameters to optimize. The function
+where $\alpha$, $\beta$ and $A$ are parameters to optimize \notaV
+{Agregue} in order to maximize the average reflectance. The function
 $f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
-restricting  $\alpha>0$. The functions $f_2$ are arithmetic averages
+restricting  $\alpha>0$. The function $f_2$ is an arithmetic averages
 of two functions of the type $f_{1}$ with different
-powers $\alpha$ and $beta$ \notaL{A ¿no debe ser 1/2 a fuerza, para
-  que $f_2(1)=1$?}. The functions $f_{3}$ (Eq. (\ref{F3})) are
-designed so that the power $\alpha$ dominates close to the surface and
-the power $\beta$ close to the substrate, to allow different behaviors
-at the UV and at the IR end of the spectrum. The reflectance
-$R(\lambda,\theta)$ of the resulting structures was calculated in
-the wavelength range from 350 to 1400 nm and for angles of incidence
-from normal ($0^\circ$)  to grazing ($90^\circ$) incidence and
-averaged to yield $\braket{R}$. The parameters $\alpha$, $\beta$
-and $\gamma$ were then optimized to maximize the average
-reflectance. The calculations were done using the Perl Data Language
-(PDL) and its interface to the MINUIT minimization
-package\cite{minuit}.The optimized parameters corresponding to a
-porosity contrast of
-51/76\% are shown
-in Table 1.  In the supplementary information we include the
-parameters for porosity contrasts of $30/76\%$ and $42/76\%$.
-\begin{table}
-\includegraphics[width=\textwidth]{F2TableOptimized.pdf}
-\caption{Optimized parameters yielding the highest average reflectance
-  $\braket{R}$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs.
-  (\ref{F1}) - (\ref{F3}))}
+powers $\alpha$ and $\beta$ \notaL{A ¿no debe ser 1/2 a fuerza, para
+que $f_2(1)=1$? \notaV{Si}}. The function $f_{3}$ (Eq. (\ref{F3})) is 
+designed so that the first addend dominates near the surface and the 
+second addend prevails near the substrate, to allow different behaviors 
+at the edges \notaV{Omitted "at UV and IR end"} of the spectrum. 
+\notaV{Se replanteo el resto del parrafo} The parameters 
+that were optimized to obtain the maximum average reflectance were 
+$\alpha$, $\beta$, $A$ and $N_{p}$. The reflectance $R(\lambda, 
+\theta)$ of the resulting structures was calculated in two regions of 
+the electromagnetic spectrum. The first region was chosen from 350 to 
+1400 nm and second one was selected from 400 to 3000 nm, both in the 
+angular range of $0^\circ$ to $90^\circ$. Additionally, in the first 
+region the minimum design wavelength was optimized and the maximum 
+design wavelength was set at 1400 nm, while in the second region the 
+wavelengths were set at 850 and 3000 nm, respectively. The 
+calculations were carried out using the Perl Data Language (PDL) and 
+its interface with the MINUIT \cite{minuit} minimization package. The 
+optimized parameters corresponding to a porosity contrast of 51 and 76\% 
+are shown in Table \ref{tab:tableA}.
+
+\notaV {En caso de ser necesario "In the supplementary information we include the parameters for the porosity tests of $30/76 \% $ and $42/76 \%$."}
+
+\notaV{Se replanteo el contenido}
+
+\begin{table}[!ht]
+	\begin{center}
+		\label{tab:tableA}
+\caption{Optimized parameters yielding the highest average reflectance $<$R$>$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs. (\ref{F1}) - (\ref{F3}))}
+		\resizebox{\textwidth}{!}{ 
+		\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+			\hline % <-- Toprule here
+			\textbf{Func-}&\multicolumn{3}{|c|}{\textbf{Parameters}} &\textbf{Periods}&\textbf{Thick-}&\textbf{OD}&\textbf{$\lambda_{0}$}&\textbf{$R_{Ave}$}\\
+		\textbf{tion}&$\alpha$&$\beta$&A&$N_{p}$&\textbf{ness} ($\mu$m)& \textbf{width} ($\mu$m)&($\mu$m)&$\%$\\
+			\hline
+			$f_{1}$&0.24&---&---&222&86.1&0.30&1.150&89\\
+			$f_{2}$&0.37&1.06&---&102&35.9&0.22&1.110&88\\
+			\textcolor{red}{$f_{3}$}&\textcolor{red}{1.23}&\textcolor{red}{0.54}&\textcolor{red}{0.18}&\textcolor{red}{63}&\textcolor{red}{21.6}&\textcolor{red}{0.25}&\textcolor{red}{1.125}&\textcolor{red}{89}\\
+			\hline
+			\textcolor{red}{$f_{1}$}&\textcolor{red}{1.20}&\textcolor{red}{---} &\textcolor{red}{---} & \textcolor{red}{90}&\textcolor{red}{60.4}&\textcolor{red}{2.15}&\textcolor{red}{1.925}&\textcolor{red}{92}\\
+			$f_{2}$&1.08&1.86&--- &105&61.7&2.00&2.000&89\\
+			$f_{3}$&1.01&1.95&0.20&102&62.3&2.05&1.975&90\\
+			\hline
+		\end{tabular}
+	}
+	\end{center}
 \end{table}
-\notaL{Sugiero poner aquí una tabla de latex, editable, en lugar de
-  una figura}
+
 \notaL{No es claro en el texto cómo se obtiene $N_p$. Se mencionaba
@@
   vez que se maximizaba la reflectancia. ¿Fue minuit? ¿Fue a ojo?}
+\notaV{$N_{p}$ lo proporciona minuit para cada una de las funciones propuestas y del m\'{i}nimo lo tom\'{e} para hacer el experimento}
 
-According to table I, the structure (named as ST-A)\notaL{Este nombre
-  no está en la tabla. ¿Qué significa el acrónimo?} that has the
-maximum average reflectance with the minimum thickness is the one designed
-with the function $f_{3}$ (Eq. (\ref{F3})) with parameters
-$\alpha=1.23$, $\beta=0.54$ and $A=0.18$, which is shown in
-Fig. \ref{Fig2}(a). \notaL{Si queremos que $x_j$ vaya de 0 a 1 habría
-  que numerar $j$ de 0 a $N_p-1$, y dividir entre $N_p-1$ en lugar de 1 a $N_p$ y
-  dividir entre $Np$. Parece que no lo hiciste así, entonces habría que
-  revisar un poco la discusión arriba}.
-\begin{figure}
+According to table \ref{tab:tableA}, in the first region, the function 
+$f_{3}$ modulates the best distribution of the periods in the smallest 
+thickness and the proposed photonic structure has the highest 
+reflectance. Furthermore, this structure has an OD gap with a reflectance 
+$R>0.90$ of 250 nm centered at 1125 nm, as shown in Fig. \ref{Fig1}(b). This 
+structure will be synthesized and we will call it S-1. In the second region, the 
+proposed structures have very similar thicknesses and reflectance 
+spectra; however, the one with the smallest thickness and the maximum 
+reflectance is the one designed from the function $f_{1}$. This 
+structure will also be synthesized and we will call it S-2. The 
+calculated reflectance spectra of S-2 are shown in Fig. \ref{Fig1}(d). 
+This structure has a very wide region where $ R(\lambda, \theta)> 
+0.90$, which is located from 850 to 3000 nm and in an angular range 
+of $0^\circ$ to $70^\circ$. So, we can say that S-2 has a 
+quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm. On the other hand, 
+the profiles of the functions (with the optimized parameters) that 
+modulate the distribution of the $j-th$ period tuned to the $\lambda_ 
+{j}$, in the first analysis region, are shown in Fig. \ref{Fig1}(a). 
+In Fig. \ref{Fig1}(c), the profiles of the functions related to the 
+second region are plotted. In these figures, it is observed that the 
+profiles are very similar in each region of analysis. For example, in 
+the first analysis region, it is necessary that the photonic 
+structures have the least number of periods tuned in the areas where 
+the SP is absorbing and that they are the first periods of the 
+structure. In the second region, it is only necessary that the periods 
+have an adequate ordering.
+\begin{figure}[!ht]
+		\label{Fig1}
 	\begin{center}
-\includegraphics[width=\textwidth]{F3OptimizedVis.pdf}
+		\includegraphics[width=\textwidth]{F1Alternativa.pdf}
 	\end{center}
-\caption{(a)Design wavelength $\lambda_{j}$ vs. period number $j$-th
-  for the optimized structure ST-A with 63-periods.\notaL{Parece un
-    poster miniatura. ¿La ilustración a la derecha está a escala o
-    es esquemática? ¿La necesitamos? Está tan chica que es
-    ilegible}\notaL{¿Qué es eso de $\lambda+1$? Creo que está mal}
-  (b) Average reflectance of the structures designed with different
-  values of $\alpha$ and $N_{p}$.\notaL{Por qué en la misma figura?
-    ¿Cuál es el propósito de incluir esta? Cambia el cbrange para que
-    el color diga algo. Se ve todo rojo uniforme.} It is verified that the
-  parameters obtained during the optimization are adequate ($\alpha
-  =1.23$ and $N_{p}=63$).\notaL{Este comentario va en el texto, no en
-    el pie de figura} (c) Reflectance for non polarized light of the
-  optimized structure. (d) Comparison of the reflectance spectra
-  calculated and measured at different angles of incidence. The gray band indicates the
-  region in which the reflectance is greater than 95\%. Inset shows the
-  top view photograph of the synthesized structure.\notaL{En mi
-    humilde opinión son demasiadas figuras en una sola, no
-    claramente relacionadas entre sí.}}
+	\caption{Profiles of the optimized functions that modulate the distribution of the $j-th$ period tuned to the design $\lambda_ {j}$ for the analyzed structures in the region (a) from 350 to 1400 nm and (c) from 400 to 3000 nm.
+Reflectance spectra of the optimized structures in the region (b) from 350 to 1400 nm and (d) from 400 to 3000 nm.
+The dotted lines delimit the area where R $> 90\%$ and the dashed lines indicate the quasi-OD region.
+In the first region there is an OD gap and in the second region there is a quasi OD gap.
+Calculations are for non-polarized light.}
+\end{figure}
+
+We fabricate the optimized structures (S-1 and S-2) and measure their 
+reflectance spectra at various angles of incidence $\theta$. Due to 
+experimental limitations, we restrict our results to the case of 
+unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured 
+reflectance are compared from 350 to 1400 nm for different angles of 
+incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$, 
+$50^\circ$, and $60^\circ$) for S-1. They have very similar 
+characteristics. For example, for $\lambda>700$ nm and 
+$10^\circ < \theta < 40^\circ$, the spectrum differs by less than $5\%$ and for 
+$\theta > 40^\circ$ both spectra are qualitatively consistent but the 
+measured reflectance is less than the calculated one. This difference 
+can be attributed, in part, to the scattering of light at real 
+interfaces, which generally have a certain roughness 
+\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into 
+account in our theory. Reflectance was measured using unpolarized 
+light. Due to the limitations of the spectrophotometer, it is not 
+possible to perform measurements for $\theta>60^\circ$ and thus 
+check the OD gap. Therefore, in this angular range, we will limit 
+ourselves to saying that the structure has a quasi-omni-directional 
+bandgap (R$\left(\lambda,\theta \right)>90\%$) located between 980 and 
+1340 nm.
+\begin{figure}[!ht]
 	\label{Fig2}
+	\begin{center}
+		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
+	\end{center}
+	\caption{Reflectance spectra calculated and measured at different 
+	angles of incidence for structure (a) S-1 and (b) S-2.
+Reflectance spectra are for non-polarized light.
+The gray band indicates the region where the reflectance is greater than  $90\%$.
+This region corresponds to the quasi OD gap of the structure.
+Inset: photograph of the synthesized structure.}
 \end{figure}
-In Fig. \ref{Fig2}(b)
-we show $\braket{R}$ for different values of $N_p$ and
-$\alpha$ to illustrate its dependence on the parameters, and
-to verify that our optimized values correspond indeed to the maximum. Here, the
-parameters $\lambda_{\text{min}}$, $\lambda_{\text{max}}$, $\beta$ and $A$ were
-adjusted, while $N_{p}$ and $\alpha$ varied from 30 to 200 periods and from 0.4 to 1.3,
-respectively. \notaL{Ya no me quedó claro. Hay que decir arriba cuales
-  son los parámetros que se variaron durante la optimización original. ¿Fueron
-  $N_p$, $\lambda_{min}$, $\lambda_{\max}$, $A$, $\alpha$ y $beta$,
-  todos ellos? Creo que no es claro. Si fue así, hay que distinguir
-  las longitudes de onda del ajuste de las del rango en que
-  optimizaste la reflectancia}
-The calculated reflectance, $R(\lambda ,\theta)$ of the optimized
-photonic structure is shown in Fig \ref{Fig2}(c) for wavelengths and incidence
-angles covering the ranges from 350 to 1400 nm, and from $0^\circ$ to $90^\circ$,
-respectively. Calculations indicate that the structure is an omnidirectional
-mirror with a  reflectance $R>0.95$ within a band from 1000 to 1200
-nm. \notaL{La zona gris en la figura va más allá de 1200.} We
-fabricated a sample corresponding to our
-optimized structure and measured its reflectance spectra at several
-incidence angles $\theta$. Due to
-experimental limitations, we restrict our results to the case of
-non-polarized light.
-In Fig. \ref{Fig2}(d), the calculated and
-measured reflectance are compared
-for $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$, $50^\circ$
-and $60^\circ$. In this angular range, the structure has a
-quasi-omnidirectional band gap (R$\left(\lambda,\theta\right)>95\%$) located from
-980 to 1340 nm. \notaL{Aquí hay un error: el experimento salió ¡mejor
-  que la teoría! (ver arriba) Algo hay mal en la descripción, pues la
-  figura muestra al experlimento abajo de la teoría.}  The
-numerical and experimental spectral line shapes at different
-angles are in good agreement. For $\lambda>700$nm and
-$10^\circ<\theta<40^\circ$ the spectra differs by
-less than $5\%$. For $\theta>40^\circ$ both spectra agree
-qualitatively but the measured reflectance is lower that than the
-calculated one. This difference can be attributed, in part,
-to the scattering of light at the actual interfaces, which generally
-have some roughness \cite{Theiss1994,Chavez2020} which we have not
-accounted for in our theory.\notaL{Quizás aquí puedas citar el
-  artículo de Guillermo Ortiz y mío reciente {\em Rough 1D  Photonic
-    Crystals: a transfer matrix approach}, Leandro Missoni, Guillermo
-  Ortiz, María Martinez Ricci, Victor Toranzos y W. Luis Mochan,
-  Optical Materials {\bf 109}, 110012 (2020)
-{\tt https://doi.org/10.1016/j.optmat.2020.110012}}
 
-Due to the disipative nature of Si in the UV and the visible region, it is relatively
-difficult to design porous silicon omnidirectional mirrors in that region.
-However, in the IR region, it is relatively easy to obtain highly reflective
-and even omnidirectional photonic structures over a wide
-range. \notaL{Está rara la lógica: ¿optimizamos en esa región porque
-  es fácil o usamos $f_1$ porque optimizar es fácil? Quizás primero
-  debamos decir que nos interesa esa región y que como es fácil,
-  usamos $f_1$.}
-Therefore,
-the reflectance average in the region of 850 to 3000 nm and for all
-angles was optimized using the function $f_{1}$ (Eq. (\ref{F1})), yielding
-$\alpha=1.2$ with $N_p=90$ and a thickness of 60.4 $\mu$m. \notaL{Aquí
-  me vuelve a confundir. ¿90 es el ancho óptimo o
-  es el ancho mínimo que permitió... qué?} The resulting design
-wavelengths of the structured, designated as ST-B, \notaL{¿Por qué se llaman así? ¿Qué significa
-  ST?} are shown in Fig.
-\ref{Fig3}(a).
-\begin{figure}[tbph]
+On the other hand, Fig. \ref{Fig2}(b) shows the comparison of the 
+calculated reflectance spectra and the spectra measured in the range 
+from 400 to 3000 nm and the aforementioned incidence angles for S-2. 
+These spectra are also very similar. The difference between the 
+calculated and measured spectra at longer wavelengths, can be 
+attributed to an increase of imperfections such as wavy layers and 
+more roughness for deeper layers, due to a more restricted diffusivity 
+of the electrolyte as the thickness of the structure is increased 
+\cite{Negro2003,Vincent1993}. According to the results obtained, this 
+structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm 
+centered at 1880 nm.
+
+\subsection{Photonic structure with sub-mirrors stacking}\label{ss:stacked}
+
+Another technique for designing structures that reflect across a wide range of the 
+electromagnetic spectrum is to stack sub-mirrors tuned to different wavelengths. For 
+example, Agarwal et al. \cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
+first select the $\lambda_{1}$ value from the initial sub-mirror, then subsequent 
+$\lambda$ values obey a simple relation $\lambda_{i+1} + \lambda_{i}=2+i$, where $i$ 
+represents the sub-mirror number. Furthermore, Estrada-Wiese et al. \cite{DelRio2018} 
+developed a method that combines three stochastic optimization algorithms together with 
+a  narrow space search methodology to obtain a customized and optimized 
+PC configuration.
+
+In this technique, we continue to use the 
+propagation of Bloch waves in periodic structures, since this allows 
+us to know the frequencies that cannot propagate through the 
+structure. These are obtained by analyzing the expression
+\begin{equation}
+	 \cos (KD) = \frac{1}{2} \text{Tr}M,   \label{Dispersion}
+\end{equation}
+where $D$ is the thickness of the sub-mirror, $\pm K$ 
+represents the Bloch vector that propagates in the sub-mirror 
+\cite{Mochan1987, Mochan1988, Perez2018}, Tr denotes the trace 
+and $M$ is the matrix given by Eq. \ref{MsBloch}. This equation 
+is limited by the minimum and maximum values that the 
+cosine function can take. Also, if the value of 
+$\left\vert\text {Tr} \left(M \right) \right\vert$ is $>2$, it 
+indicates that this frequency will not be able to propagate 
+through the structure.
+
+It is common to imagine that the stacking of the sub-mirrors is as 
+follows: that the PBG of the $j+1-th$ mirror starts at the edge of the 
+PBG of the $j-th$ mirror and stack enough mirrors until covered the 
+bandwidth of the desired range. However, with this configuration, the 
+reflectance has minimum values at each edge of to contiguous PBG.
+On the other hand, the number of periods of each sub-mirror is an 
+important parameter due to its direct dependence on the magnitude and 
+width of the photonic forbidden band. Since the structures are 
+synthesized using porous silicon, it is essential to minimize the 
+number of periods corresponding to the sub-mirrors of the visible 
+region. For these reasons, the design of the structure was carried 
+out in two different ways: in the first, constant periods were 
+considered and in the second, a constant number of periods was 
+assigned for the interval from 400 to 800 nm (a period for 
+$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm 
+and three periods for $650<\lambda_ {D}<800$ nm) and for 
+$\lambda_{D}>800$ nm, the number of periods was variable. In both 
+designs, the optimal overlap of two consecutive PBGs was obtained that 
+maximized reflectance. Reflectance spectra were calculated from 400 to 
+3000 nm in the spectral range of $0^\circ$ to $90^\circ$. 
+Table \ref{tab:table2} shows the number of periods of each sub-mirror 
+($Np_{se}$), the total number of stacked sub mirrors ($N_{se}$), the 
+thickness of the structure, the optimal overlap of two consecutive 
+PBGs and the average reflectance. The first block corresponds to 
+sub-mirrors with a constant number of periods, while the second block 
+corresponds to sub-mirrors with a variable number of periods according 
+to the design wavelength. 
+\begin{table}[htbp]
+	\begin{center}
+		\caption{Parameters that maximize the reflectance of photonic structures.}
+		\label{tab:table2}
+		\begin{tabular}{|c|c|c|c|c|}
+			\hline % <-- Toprule here
+			\textbf{$Np_{se}$}&{\textbf{$Np_{se}$}} &\textbf{Thickness}&\textbf{Overlap}&\textbf{$R_{Ave}$}\\
+			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
+			\hline
+			1&98&43.2&95&91.0\\
+			3&31&42.5&81&91.8\\
+			5&17&41.9&68&92.0\\
+			\hline
+			4&25&38.7&74&92.3\\			\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
+			10&13&45.4&56&95.34\\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}
+
+According to table \ref{tab:table2}, the structure that has the highest 
+reflectance is in the second block. We will call this structure S-3. In 
+S-3, the overlap of two consecutive PBGs is $78\%$, their thickness is 
+41.5 $\mu$ m, and the average reflectance is $95.3\%$. Additionally, 
+S-3 is made up of 18 sub-mirrors tuned to the following wavelengths 
+400, 460, 510, 570, 640, 720,810,910, 1020, 1150, 1290, 1450, 1630, 
+1830, 2060, 2320, 2610, and 2860 nm. The calculated and measured 
+reflectance spectra of S-3 are shown in Fig. \ref{Fig3}.
+\begin{figure}[!ht]
 \begin{center}
 \includegraphics[width=\textwidth]
-{F4OptimizedNIRPC.pdf}
+{F3Alternativa.pdf}
 \end{center}
-\caption{(a) Design wavelengths $\lambda_j$ as a function of period
-  number $j$ for sample ST-B. (b) Average reflectance $\braket{R}$
-for different values of the parameters $\alpha$
-and $N_p$ parameters. \notaL{Cambia el letrero en la figura} The
-optimized parameters $\protect\alpha =1.2$
-and $N_p=90$ are displayed as a white spot.\notaL{No se ve que sea el
-  óptimo. Quizás se necesiten línes de contorno más juntas.} (c)
-Calculated reflectance of the optimized
-structure for non polarized light.\notaL{¿QUé indica la raya punteada
-  y el letrero en la figura?} (d) Comparison of
-the calculated and measured spectra  for several angles of incidence. The
-gray band indicates the region in which the reflectance is greater than 95$\%$. Inset:
-photograph of the synthesized structure.}
+\caption{ (a) Calculated reflectance for the optimized structure S-3. (b) Comparison 
+	between the measured and calculated reflectance spectra at several angles of 
+	incidence. Reflectance spectra are for non-polarized light. The gray band indicates 
+	the region in which the reflectance is greater than 90$\%$.  Inset shows a 
+	photograph with a top view of the synthesized structure.}
 \label{Fig3}
@@
 
-\notaL{Tengo los mismos comentarios que para la figura previa.}
-Fig \ref{Fig3}(b) shows $\braket{R}$ for
-different values of $\alpha$ and $N_{p}$. As in the
-previous case, the optimized parameters are within the zone of maximum
-average reflectance. \notaL{No debería ser el mismísimo máximo y no
-  nada más en la zona?} The reflectance calculation  is
-shown in Fig. \ref{Fig3}(c).  This structure
-has a wide quasi-omnidirectional gap with $R(\lambda,\theta)>0.95$
-with $\lambda$ from 850 to 3000 nm and $\theta$ from
-$0^\circ$ to $70^\circ$.\notaL{Me da la impresión que confundías
-  promedio con reflectancia} The measured and calculated reflectance
-are compared  for several angles in Fig \ref{Fig3}(d). The synthesized PS
-multilayered 1D photonic structure behaves as a quasi omnidirectional
-mirror for $0^\circ\le\theta\le 60^\circ$ with a bandwidth of approximately 1800 nm. The difference
-between the calculated and measured spectra at the longer wavelengths can be
-attributed to a thickness gradient along the depth,\notaL{No entiendo:
-  está diseñada para tener un gradiente de ancho. Te refieres a un
-  gradiente adicional al diseñado?} which is more pronounced in
-the lower layers due to the restricted diffusivity of the electrolyte
-through the structure itself \cite{Negro2003,Vincent1993} and
-interface roughness \notaL{No se entiende si este es otro efecto o si
-  la rugosidad produce un gradiente de anchos}.
-y
-\subsection{Photonic structure with sub-mirrors stacking}\label{ss:stacked}
+The reflectance mapping shown in Fig. \ref{Fig3}(a) reveals a quasi omnidirectional 
+mirror in the range from 950 to 2900 nm, and angular range between $0^\circ$ and 
+$60^\circ$. It is also observed that at incidence angles $>$70${{}^\circ}$, for long 
+wavelengths the reflectance decreases and has oscillations, which are attributed to the 
+greater penetration of the electromagnetic field within the structure, as shown by 
+Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the 
+calculated and measured reflectance for the structure S-3, at several angles of 
+incidence. Although, the quasi omnidirectional wavelength range of the synthesized 
+structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured 
+PBG is almost twice as wide as a recently reported PS chirped structure \cite{Chavez2020}.
 
-Another technique to design Bragg mirrors in a wide range of the
-electromagnetic spectrum is by stacking sub-mirrors tuned to different
-wavelengths \cite{DelRio2018,Agarwal2003}. Such grouping must meet the condition
-imposed by the dispersion relation,\notaL{No se entiende, ¿de qué la gira
-la relación de dispersión? Es la relación de dispersión ¿de qué? Falta
-una explicación!} $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is
-the period, which corresponds to the actual thickness of the
-sub-mirror\notaL{Por qué? El espejo podría tener varios periodos.}, $\pm K$
-represents a 1D Bloch's vector corresponding to a wave that propagates along
-the $z$-direction \cite{Mochan1987,Mochan1988,Perez2018}, and T$\text{r}$ denotes the
-trace. This equation is bounded by the minimum and maximum values that the cosine
-function can take. Furthermore, if  the value of $\left\vert \text{Tr}\left(
-M\right) \right\vert$ is $>2$, it indicates that this frequency will not
-be able to propagate through the structure. \notaL{Las ideas están
-  bien, pero está muy mal explicado, en desorden}
+Finally, table \ref{tab:table3} shows some porous silicon based OD mirrors designed to operate in the NIR 
+region and the width of the omnidirectional band gap is compared with the structures 
+analyzed in the present study. The table reveals that the porous silicon based 
+structures ST-B and ST-C have the widest gap width, being 1.36 times greater than the 
+largest reported work until now in the NIR region \cite{Wu2021}.
 
-The ideal stack of sub-mirrors would be that edge where the PBG of the $j$-th mirror begins
-is close to the  edge of the where the PBG of the $j-1$-th mirror
-ends, and sufficient mirrors are stacked until the desired interval
-bandwidth has been
-covered. However, this arrangement does not give the maximum average reflectance due to
-the decrease in the reflectance at each intersection of the two
-PBGs.\notaL{QUé es una intersección de PBG? Escribe para que el lector
-  entienda} On the other hand,
-the number of periods of each sub-mirror is an important parameter due to its direct
-dependence on the magnitude and  width of  the photonic band gap.  As the structures
-were synthesized using porous silicon, it is essential to minimize the number of
-periods corresponding to the visible region sub-mirrors. Also, in the supplementary
-information we show the reflectance calculations for structures composed of sub
-mirrors with a constant number of periods, in these cases ODBMs are not obtained.
-For these reasons, the number of periods for each mirror was chosen as follows: for
-design wavelengths less than 500 nm ($\lambda_{D}<$500 nm), one period, for 500
-$<\lambda_{D}<$650 nm, two periods , for 650 $<\lambda_{D}<$800 nm, three, and for
-$\lambda_{D}>$ 800 nm, the number of periods was variable
-(Fig. \ref{Fig4}(a)). \notaL{No entendí el argumento, ni cómo
-  dterminaste para qué lambdas se usan tantos o cuántos periodos. ¿Fue
-  prueba y error? ¿Fue una optimización?}\notaL{Por cierto,
-  ¿optimizaste qué tanto traslapar espectros sucesivos o usaste la
-  regla de que se toquen los bordes de banda?}
-\begin{figure}[tbph]
-\begin{center}
-\includegraphics[width=\textwidth]
-{F6OptimizedNIRSE.pdf}
-\end{center}
-\caption{\notaL{Stack, no stak. ¿Qué significa la región rugosa que
-    rodea la estructura?} (a) Diagram showing the distribution
-  of sub-mirrors and the corresponding
-number of periods in a PS multilayer.\notaL{Esto no es un cartel. No
-  entiendo qué pretende ilustrar el panel (a)} (b) Maximization of the average reflectance as
-a function of the overlap photonic band gap for the structures formed by sub-mirrors
-with a fixed number of periods \notaL{No has explicado a qué te
-  refieres con esta optimización. No has explicado qué es el overlap
-  photonic band gap. Esto parece tomado de un cartel, pero el artículo
-debe ser autocontenido; no estás ahí parado para explicar.}(3 and 4),
-and for structures with the design of (a)
-using 3 and 6 periods for the tuned sub-mirrors in $\lambda>800$
-nm.\notaL{No entendí nada.} (c)
-Calculated reflectance for the optimized structure for non
-polarized light. (d) Comparison between the measured and calculated
-reflectance spectra at several angles of incidence. The gray band indicates the region in which the
-reflectance is greater than 95$\%$. Inset shows a photograph with a top view of the
-synthesized structure.}
-\label{Fig4}
-\end{figure}
-
-Therefore, in this work the overlap percentage of the PBGs of the first and second
-mirror, second and third mirror, and so on, is also optimized. Fig \ref{Fig4}(b)
-shows the optimization results in terms of maximum average reflectance with respect
-to the PBG overlap at different sub-mirror periods, keeping them fixed (3, 4) or
-variable (1, 2  and 3) for $\lambda<500$(1 period), $500<\lambda<650$ nm (2
-periods), $650<\lambda<800$ nm (3 periods) and $\lambda>800$ (3, 6 periods). For
-example, the calculations corresponding to the reflectance spectra of the structures
-formed using sub-mirrors with constant periods (3 and 4) revealed a lower average
-reflectance as compared to the structure formed with variable periods. The 1D
-photonic structure with the highest average reflectance (named as ST-C)  is the one
-designed with variable periods and contemplates 6 periods for each sub-mirror in the
-NIR region. In the optimized structure designed for 400-3000 nm range, the photonic
-band gap overlap is around 78$\%$, thickness is 41.5 $\mu $m and the average
-reflectance is 95.3$\%$, when the  electromagnetic waves are incident from
-0${{}^\circ}$ to 89 ${{}^\circ}$. The optimized photonic structure is made up of 18
-sub-mirrors tuned to the following wavelengths 400, 460, 510, 570, 640, 720,810,
-910, 1020, 1150, 1290, 1450, 1630, 1830, 2060, 2320, 2610 and 2860 nm  with periods
-of 1 (400, 460 nm), 2(510, 570, 640 nm), 3 (720 nm) and 6 (810 nm and
-above).\notaL{Sugiero reescribir tratando de que la explicación sea clara}
-
-The reflectance mapping shown in Fig \ref{Fig4}(c) reveals a quasi omnidirectional
-mirror in the range from 950 to 2900 nm, for $\theta$ between
-$0^\circ$ and $60^\circ$. It is also observed that at incidence angles $>$70${{}^\circ}$, for long
-wavelengths the reflectance decreases and has oscillations, which are attributed to
-the greater penetration of the electromagnetic field within the structure, as shown
-by Puente-D\'{\i}az, et al \cite{Puente2020}. Furthermore, in the supplementary
-information we show the trace of the transfer matrix as function of the
-wavelength and the incidence angle for the ST-C photonic structure for TE and
-TM polarizations.\notaL{¿Para qué ponemos esta información
-  suplementaria? ¿Qué aprenderá el lector de ella?} In Fig
-\ref{Fig4}(d) we compare the calculated and measured reflectance
-for the structure ST-C, at several angles of incidence.
-Although, the quasi omnidirectional wavelength range of the synthesized structure is
-slightly smaller than the calculated one, from 950 to 2750 nm, the measured PBG
-is almost twice as wide as those of recently reported similar structures
-(\cite{DelRio2018,Chavez2020}).
-
-Finally, table 2 shows some porous silicon based ODBMs \notaL{Me
-  preocupa un poco la nomenclatura: si no son periódicos, ¿son espejos
-  de Bragg?} designed to operate in the
-NIR region and the width of the omnidirectional band gap is compared with the
-structures analyzed in the present study. The table reveals that the porous silicon
-based structures ST-B and ST-C have the widest gap width, being 1.8 times greater
-than recently reported works.\notaL{Es justa la comparación? Ellos
-  estaban tratando de hacer un espejo de espectro muy amplio y no
-  pudieron hacerlo tan ancho como nosotros o simplemente estaban
-  haciendo otra cosa?}
-
-\begin{table}[h!]
+\begin{table}[!ht]
 	\begin{center}
 		\caption{Summary of the development in porous silicon based ODBMs designed in the NIR region.}
-		\label{tab:table1}
-		\begin{tabular}{c|c|c|c}
+		\label{tab:table3}
+		\begin{tabular}{|c|c|c|c|}
 			\hline % <-- Toprule here
@@
 			\hline % <-- Midrule here
-Bruyant, et al \cite{Bruyant2003}. & 2003 & 1100-1440 & 340 \\
-Xifre-P\'{e}rez, et al \cite{Xifre2005}. & 2004 & 1297-1615 & 318\\
-Estevez, et al \cite{Estevez2009}. & 2009 & 950-1456 & 506 \\
-Chavez, et al \cite{Chavez2020}. & 2020 & 1000-2000 & 1000 \\
+Bruyant, et al. \cite{Bruyant2003} & 2003 & 1100-1440 & 340 \\
+Xifre-P\'{e}rez, et al. \cite{Xifre2005} & 2004 & 1297-1615 & 318\\
+Estevez, et al. \cite{Estevez2009} & 2009 & 950-1456 & 506 \\
+Chavez, et al. \cite{Chavez2020} & 2020 & 1000-2000 & 1000 \\
+Wu, et al. \cite{Wu2021} &2021&1284-2605&1321 \\
 			\hline % <-- Bottomrule here
@@
 \section{Conclusion}\label{s:conc}
+\notaV {Se replantean las conclusiones}.
 
-We have designed, fabricated and characterized highly reflective PS multilayer photonic
-structures with a wide spectral range, optimized using two techniques for maximal reflectance
-and minimal thickness in the NIR region \notaL{Parte del trabajo no
-  fue NIR.} With \textit{chirped}-type
-Bragg\notaL{Tengo la duda sobre llamarles Bragg} mirrors,
-two regions of the electromagnetic spectrum were analyzed. The first region (350nm -
-1400 nm), optimized through an increasing function resulted in a
-reflectance $R>0.85$ with a range of 360 nm centered at 1160 nm
-(980-1340 nm) for the angular range $0-60^\circ$ and $R>0.50$ of
-reflectance from 550-980nm. The second structure was designed for a
-wavelength range from 850-3000 nm
-and the synthesized structure with optimized parameters resulted in
-the average reflectance of $~91\%$ with q-OD \notaL{No definiste q-OD
-  nunca} bandgap from 980 to 2780 nm and a
-thickness of 60.4 $\mu$m. The other design technique consists of
-stacking sub-mirrors
-tuned to different wavelengths, and was optimized for a maximum average
-reflectance using  the overlap of the gap of succesive sub-mirrors as
-the optimization parameter. We obtained
-a reflectance $R>0.95$ and a thickness of 41.5 $\mu$m within a
-wavelength range of 1800 nm centered at 1850 nm, with  an
-angular range $0-60^\circ$. Therefore, we found this second technique to be
-better as it yields thinner structures by a factor of $~1.5$ and
-increased average reflectance. Additionally, the analysis techniques developed here
-can be used to optimize reflectance with other refractive index contrasts in PS
-multilayers or in systems composed of other types of materials. Such
-proposed structures could be used as mirrors for solar concentrators, flat focusing
-reflectors, thermal regulators, or, if defects are included, as filters or remote
+We have designed, fabricated and characterized highly 
+reflective q-OD (angular range of $0-60^\circ$) 
+multilayer structures, with a wide spectral range, 
+optimized through two techniques: chirping and stacking 
+Bragg-type sub-structures. Numerical calculations were 
+carried out by employing the transfer matrix method, 
+incorporating a Perl Minuit module in order to maximize 
+the average reflectance of the structures. Some of the 
+optimized structures were manufactured with PS dielectric 
+multilayers and compared with their simulations. For the 
+chirping method, a couple of structures were fabricated, 
+one with thicknesses of 21.6 $\mu$m and other with thickness 
+of 60.4 $\mu$m, resulting in reflectivity q-OD bands of 
+360 nm and 1800 nm, centered at 1160 nm and 1925 nm, 
+respectively. For staking sub-structures method we 
+obtained a 41.5 $\mu$m thickness mirror with a q-OD 
+band of 1800 nm centered at 1850 nm. Therefore, the second technique is found to be better as it results in structures with relatively
+less thickness  along with noticeable improvement 
+in average reflectance. Additionally, the analysis 
+techniques developed here can be used to optimize 
+reflectance with other refractive index contrasts 
+in PS multilayers or in different systems with other 
+types of materials. Such proposed structures could 
+be used as mirrors for solar concentrators, flat 
+focusing reflectors, thermal regulators, or, if 
+defects are included, as filters or remote 
 chemical/biosensors with a wide angular independent response.
@@
 This work was partially supported by Consejo Nacional de Ciencia y
-Tecnolog\'{i}a through grant No. \textbf{256243} and C\'{a}tedras
+Tecnolog\'{i}a through grant No. 256243, C\'{a}tedras
 Conacyt program 1577, and by DGAPA-PAPIIT UNAM under grant IN111119. 
+HPA also express his gratitude to the Coordinaci\'{o}n 
+de la Investigaci\'{o}n Cient\'{i}fica de la Universidad 
+Michoacana de San Nicol\'{a}s de Hidalgo. 
 %\end{acknowledgments}

### 2021-01-18 PaperVictor.tex
Revise VIctor's version

@@
 \usepackage{amsmath}
+\usepackage{braket}
 \usepackage[utf8]{inputenc}
@@
 can be synthesized by a simple electrochemical technique. In the present work, the
-average reflectance $<$R$>$ of PS-based mirrors is maximized within a wide 
-wavelength and angular range, for different porosity contrasts. Optimization is 
+average reflectance $\braket{R}$ \notaL{No entiendo por qué insisten
+  en no usar tipografía matemática para símbolos como $R$. Los
+  símbolos de menor y mayor no corresponden a los de promediar.}. of PS-based mirrors is maximized within a wide
+wavelength and angular range for different porosity contrasts. Optimization is
 performed to maximize the reflectance for minimum  thickness of the structure in the
 visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The
-mirrors are designed using \textit{chirped}-type structures and \textit{stacking} 
+mirrors are designed \notaL{No entiendo para qué haber cambiado el
+  modo de activo a pasivo; es mucho mejor el activo.} using \textit{chirped}-type structures and \textit{stacking}
 sub-mirrors. The chirped structures are found to be more suitable for the Vis range,
 while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication
-and testing of some optimized omnidirectional structures with less than 100 periods has 
+and testing of some optimized omnidirectional structures with less
+than 100 pairs of layers \notaL{Quizás periods no sea correcto, pues
+  no son periódicos} has
 been demonstrated.
@@
 corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
-thicknesses are quarter-wavelength
+thicknesses corresponds to a quarter of a wavelength
 $n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
@@
 Another alternative is to stack BMs, in such a way that their reflection bands partially
-overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
+overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.
 
-On the other hand, different fabrication techniques have been used to obtain omnidirectional (OD) mirrors that operate on the visible and/or near infrared (Vis-NIR) range of the electromagnetic spectrum.
-For example, Chen et al.
-\cite{Chen1999},
-\notaL{Hay que checar que la puntuación vaya después de las citas,
-	para este estilo de citas entre corchetes} reported the fabrication of a 
+On the other hand, different fabrication techniques have been used to
+obtain omnidirectional (OD) mirrors that operate on the visible and/or
+near infrared (Vis-NIR) range of the electromagnetic spectrum. For
+example, Chen et al. \cite{Chen1999},
+reported the fabrication of a
 6-pair TiO$_{2}$/SiO$_{2}$ structure with
@@
 is an attractive alternative, since it can be easily manufactured by
-electrochemical etching of crystalline Si in a hydrofluoric 
+electrochemical etching crystalline Si in an hydrofluoric
 acid based electrolyte, to obtain a sponge-like nanostructure composed
@@
 time during the electrochemical reaction, it is possible to obtain
-multilayer structures allowing for fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
+multilayered structures allowing for the fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
 Although optical filters \cite{Estevez2009,Ariza2014} are the most common
@@
 increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
-\notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
 PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
@@
 with relatively small thickness and refractive index contrast.
-\notaV{Se omite la frase "Specifically, our aim is to maximize the 
-	reflectance $R$ averaged over a wide range of wavelengths $\lambda$ 
-	and angles of incidence $\theta$", la idea general esta en la oracion anterior}
 
-This paper is organized as follows. In Sec. \ref{s:theory} \notaL{No uses números,
-	usa referencias a etiquetas para numerar y referir todo} we develop the
+This paper is organized as follows. In Sec. \ref{s:theory} we develop the
 methods used to design and calculate the reflectance spectra of the PS
@@
 them to previous reports. We obtained significantly large band-widths
-with relatively thinner structures than reported before. \notaL{Dejo para resultados y
-	conclusiones los detalles de con quién comparamos y qué salió.}
+with relatively thinner structures than reported before.
 Finally, we discuss our conclusions in Section \ref{s:conc}.
 
-\section{Numerical simulation} \label{s:theory}
+%\section{Numerical simulation} \label{s:theory}
+\section{Theory} \label{s:theory}
+\notaV{Nombre de la sección propuesta por Dr. David}
+\notaL{Estoy en desacuerdo con el título Numerical simulations. Un
+  cálculo no es en general una simulación.}
+\notaV{Parrafos reescritos por Dr. David}
+\notaL{¿Por qué reescribir toda la teoría? ¿Por qué dar tanta teoría?}
 
-\notaV{Nombre de la sección propuesta por Dr. David}
-\notaL{Pon etiquetas a todo para poderlo referir}
-\notaV{Parrafos reescritos por Dr. David}
-
-In this paper, two techniques are developed to design 
+We develop two techniques to design
 multilayer photonic structures. In the first, the wavelength
-($\lambda _{j}$), at which the $j$-th period of the structure 
-is designed, is modulated by an increasing function. This can 
-be as simple or complex as you like. The proposed function was used to
-optimize $<$R$>$ with the Minuit module of PDL (Perl Data Language) \cite{minuit}. 
-The other technique for proposing highly reflective structures 
-over a wide region of the electromagnetic spectrum is to stack
-sub-mirrors tuned to different wavelengths. For each 
-sub-mirror the dispersion relation is analyzed.
+($\lambda _{j}$) to which the $j$-th pair of layers is tuned is modulated by
+a given function of $j$. Several functions are proposed and their
+parameters are optimized to maximize the $\braket{R}$ averaged over
+wavelength and angle over a suitable range.
+To that end we employed the Minuit module of the Perl Data Language (PDL) \cite{minuit}.
+The other technique we employed consisted in stacking
+sub-mirrors tuned to different wavelengths, chosen so that their
+spectral ranges overlap. For each submirror, the spectral range was
+obtained from the dispersion relation of a corresponding periodic
+structure.
 
 For the analysis of the propagation of electromagnetic fields
-through multilayer systems, we employ the transfer matrix 
-method based on Puente-Díaz et al. formalism \cite{Puente2020}. 
-In spite some equivalent formulations have been proposed to 
-obtain the optical properties of multilayer systems 
-\cite{Mochan1987,Ortiz2020,Chavez2020}, here we use a 
-recently developed formalism for the numerically stable 
-calculation of the reflectance of large multilayer systems. 
-Briefly describing, 
-we assume a 1D system with variations along the $z$ direction 
+through multilayer systems, we employ a variant of the transfer matrix
+method based on the formalism of Puente-Díaz et al. \cite{Puente2020}.
+Its advantage over other formally equivalent approaches
+\cite{Mochan1987,Ortiz2020,Chavez2020} is that it allows a
+numerically stable
+calculation of the reflectance even of very large multilayer systems,
+even in the presence of absorption.
+We assume  the system has  variations only along the $z$ direction
 and consider an incident linearly polarized beam of light
@@
 \begin{equation}
-	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
+	r=\sigma \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
 		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
@@
 \begin{equation}
-	t=\frac{2Z_{\zeta
-	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
+	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
 \end{equation}%
-where $Z_0$ and $Z_s$ are the impedances of the vacuum 
-and the substrate, respectively. $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ is chosen for 
-TE polarization while $\beta=\text{Re}Z_{s}/ 
-\text{Re}Z_{0}$ for TM polarization. The upper sign 
-$-$ in Eq. (\ref{rBloch}) and the subscript 
-$\zeta =s$ in Eq. (\ref{tBloch}) are chosen for 
-the case of TE polarization, while the lower sign 
-$+$ and the subscript $\zeta =0$ correspond to TM 
-polarization. Moreover, sub-index $0$ and $s$ 
-refer to the incident and substrate media, respectively.
-Furthermore, $M_{ij}$ are the elements
-of the transfer matrix which relates
-the electromagnetic fields of all interfaces in the structure through
-
+where $Z_0$ and $Z_s$ are the surface impedances of vacuum
+and substrate, respectively, $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$,
+$\sigma=-1$ and
+$\zeta =Z_s$ for
+TE polarization, while $\beta=\text{Re}Z_{s}/
+\text{Re}Z_{0}$, $\sigma=+1$, and $\zeta =Z_0$ for TM
+polarization.
+Here, $M_{ij}$ are the elements
+of the reconstructed transfer matrix
 \begin{equation}
@@
 \end{equation}
-%}
-In this case, $Z^{\pm }$ can be obtained as 
+which relates the electromagnetic fields at the substrate to those at
+the surface,
+Here, $Z^{\pm }$ are the surface impedances of the multilayered system
+for fields propagating toward the substrate ($+$) or towards vacuum
+($-$), and are given by
 \begin{equation}
@@
 \end{equation}%
-being 
+where
 \begin{equation}
-	\Lambda _{-}=\frac{1}{2}\text{tr}\widetilde{M}\pm i\sqrt{1-\left( \text{tr}\widetilde{M}/2\right)
+	\Lambda _{-}=\frac{1}{2}\text{Tr}\,\widetilde{M}\pm
+        i\sqrt{1-\left( \text{Tr}\,\widetilde{M}/2\right)
 		^{2}}\text{,}  \label{LBloch}
 \end{equation}%
-where the sign that satisfies the relation $\left\vert \Lambda
-_{-}\right\vert >1$, and $\Lambda _{+}=\Lambda _{-}^{-1}$ is chosen.
-Moreover, tr corresponds to the trace and $\widetilde{M}_{ij}$ $\left( i,j=1,2\right) 
-$ denote the elements of the usual transfer matrix $\widetilde{M}$ of the $N$-layer
-system, that is, 
+is chosen to satisfy the inequality $\left\vert \Lambda
+_{-}\right\vert >1$, and $\Lambda _{+}=1/\Lambda _{-}$, and Tr denotes
+the trace. $\widetilde{M}$ denotes the usual transfer matrix
 \begin{equation}
 	\widetilde{M} = \prod \limits_{j=1}^{N}%
-	\begin{bmatrix}
+	\begin{pmatrix}
 		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\
 		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
-	\end{bmatrix}%
-	,  \label{Mcoef}
+	\end{pmatrix}%
+	\label{Mcoef}
 \end{equation}%
-where 
+of the multilayered system, where
 \begin{equation}
@@
 \end{equation}%
-is the normal component (to the interfaces) of the wave vector, $Z_{j}$ is
-the corresponding surface impedance, $Y_{j}=1/Z_{j}$ is the surface
-admittance, $\epsilon _{j}=n_{j}^{2}$ is the permitivity (for simplicity we
-assumed all media were nonmagnetic, with permeability $\mu _{i}=1$), $%
-q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
+is the normal component of the wave vector whithin the $j$-th layer, $Z_{j}$ is
+its surface impedance, $Y_{j}=1/Z_{j}$ its surface
+admittance, $\epsilon _{j}=n_{j}^{2}$ its permitivity (for simplicity we
+assumed all media were nonmagnetic, with permeability $\mu _{i}=1$),
+$q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
 the wavelength $\lambda $ and
@@
 
+\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
+  qué damos tanto detalle sobre cómo se calculó, dado que todo está en
+  la referencia.}
 \section{Experimental details}\label{s:exp}
@@
 with corresponding porosities of 51\% and 76\%, respectively.
-The porosity of the layers was obtained by a previous calibration
-curve through a gravimetric technique \cite{Pap2006}. The 
+These porosities were obtained through previously obtained calibration
+curves using a gravimetric technique \cite{Pap2006}. The
 etching rate of PS was obtained by synthetizing single layers under
@@
 
+\notaL{Aquí quitaron un comentario mío. ¿Ya no es relevante? ¿Ya se
+  explicó cómo se hizo el diseño?}
 \subsection{Chirped-type Bragg mirrors}\label{ss:chirped}
@@
 Here we study multilayered structures where the thicknesses for each
-pair $j=0\ldots N_p$ of layers are tuned to a wavelength $\lambda_j$ which changes
+pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
 gradually with the depth of the layer, according to
 \begin{equation}
-\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
+\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
 \end{equation}%
 where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
-maximum {\em design} wavelengths respectively, $N_p$ is the number of periods in the structure and $f(\xi)$ is some smooth function that 
+maximum {\em design} wavelengths respectively, $N_p$ is the number of
+periods  in the structure and $f(\xi)$ is some smooth function that
 goes from 0 to 1 as its argument goes from surface ($\xi=0$) to the
@@
 the visible and becomes negligible in the near infrared, so, the first
-periods are syntonized in the UV-Vis regions. We consider the 
+periods are tuned in the UV-Vis regions. We consider the
 following classes of functions:
@@
 \end{equation}
-where $\alpha$, $\beta$ and $A$ are parameters to optimize \notaV
-{Agregue} in order to maximize the average reflectance. The function
+where $\alpha$, $\beta$ and $A$ are parameters to optimize
+to maximize the average reflectance $\braket{R}$. The function
 $f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
-restricting  $\alpha>0$. The function $f_2$ is an arithmetic averages
+restricting  $\alpha>0$. The function $f_2$ is an arithmetic average
 of two functions of the type $f_{1}$ with different
-powers $\alpha$ and $\beta$ \notaL{A ¿no debe ser 1/2 a fuerza, para
-que $f_2(1)=1$? \notaV{Si}}. The function $f_{3}$ (Eq. (\ref{F3})) is 
-designed so that the first addend dominates near the surface and the 
-second addend prevails near the substrate, to allow different behaviors 
-at the edges \notaV{Omitted "at UV and IR end"} of the spectrum. 
-\notaV{Se replanteo el resto del parrafo} The parameters 
-that were optimized to obtain the maximum average reflectance were 
-$\alpha$, $\beta$, $A$ and $N_{p}$. The reflectance $R(\lambda, 
-\theta)$ of the resulting structures was calculated in two regions of 
-the electromagnetic spectrum. The first region was chosen from 350 to 
-1400 nm and second one was selected from 400 to 3000 nm, both in the 
-angular range of $0^\circ$ to $90^\circ$. Additionally, in the first 
-region the minimum design wavelength was optimized and the maximum 
-design wavelength was set at 1400 nm, while in the second region the 
-wavelengths were set at 850 and 3000 nm, respectively. The 
+powers $\alpha$ and $\beta$. The function $f_{3}$ (Eq. (\ref{F3})) is
+designed so that the first term dominates near the surface and the
+second near the substrate, to allow different behaviors
+at the edges of the spectrum.
+The parameters
+$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize $\braket{R}$. The reflectance $R(\lambda,
+\theta)$ was calculated for non-polarized light in two regions of
+the electromagnetic spectrum. The first region, $\mathcal R_1$,  was chosen from 350 to
+1400 nm and second one $\mathcal R_2$ was selected from 400 to 3000 nm, both in the
+angular range of $0^\circ$ to $90^\circ$. For $\mathcal R_1$ we took
+$\lambda_{\min}$ as a parameter to be optimized while $\lambda_{\max}$
+was fixed at 1400 nm. For $\mathcal R_2$ we fixed both $\lambda_{\min}=850$nm and $\lambda_{\min}=3000$nm. The
 calculations were carried out using the Perl Data Language (PDL) and
 its interface with the MINUIT \cite{minuit} minimization package. The
-optimized parameters corresponding to a porosity contrast of 51 and 76\% 
+optimized parameters corresponding to low and high porosities $p_l=0.51$ and $p_h=0.76$
 are shown in Table \ref{tab:tableA}.
@@
 
-\begin{table}[!ht]
+\begin{table}
 	\begin{center}
 		\label{tab:tableA}
-\caption{Optimized parameters yielding the highest average reflectance $<$R$>$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs. (\ref{F1}) - (\ref{F3}))}
+\caption{Optimized parameters yielding the highest average reflectance $\braket{R}$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs. (\ref{F1}) - (\ref{F3}))}
 		\resizebox{\textwidth}{!}{
@@
 			\hline % <-- Toprule here
-			\textbf{Func-}&\multicolumn{3}{|c|}{\textbf{Parameters}} &\textbf{Periods}&\textbf{Thick-}&\textbf{OD}&\textbf{$\lambda_{0}$}&\textbf{$R_{Ave}$}\\
+			\textbf{Func-}&\multicolumn{3}{|c|}{\textbf{Parameters}} &\textbf{Periods}&\textbf{Thick-}&\textbf{OD}&\textbf{$\lambda_{0}$}&$\braket{R}$\\
 		\textbf{tion}&$\alpha$&$\beta$&A&$N_{p}$&\textbf{ness} ($\mu$m)& \textbf{width} ($\mu$m)&($\mu$m)&$\%$\\
@@
 
-\notaL{No es claro en el texto cómo se obtiene $N_p$. Se mencionaba
-  una minimización del ancho, pero no recuerdo cómo se minimizó a la
-  vez que se maximizaba la reflectancia. ¿Fue minuit? ¿Fue a ojo?}
-\notaV{$N_{p}$ lo proporciona minuit para cada una de las funciones propuestas y del m\'{i}nimo lo tom\'{e} para hacer el experimento}
-
-According to table \ref{tab:tableA}, in the first region, the function 
-$f_{3}$ modulates the best distribution of the periods in the smallest 
-thickness and the proposed photonic structure has the highest 
-reflectance. Furthermore, this structure has an OD gap with a reflectance 
-$R>0.90$ of 250 nm centered at 1125 nm, as shown in Fig. \ref{Fig1}(b). This 
-structure will be synthesized and we will call it S-1. In the second region, the 
-proposed structures have very similar thicknesses and reflectance 
-spectra; however, the one with the smallest thickness and the maximum 
-reflectance is the one designed from the function $f_{1}$. This 
-structure will also be synthesized and we will call it S-2. The 
-calculated reflectance spectra of S-2 are shown in Fig. \ref{Fig1}(d). 
+The function
+$f_{3}$ yields after optimization the highest $\braket{R}$ in the
+region $\mathcal R_1$ with the thinnest structure (see table
+\ref{tab:tableA}). Furthermore, this structure has a calculated OD gap
+\notaL{I'm unsure about the nomenclature ``gap''. I guess it is
+  theoretical, right?}
+of 250 nm centered at 1125 nm with a
+reflectance
+$R>0.90$, as shown in Fig. \ref{Fig1}(b). We
+synthesized a structure  designated {\em sample $S_1$} corresponding
+to these results. For the region $\mathcal R_2$ the
+resulting structures have similar thicknesses and attain similar reflectance
+spectra, though the one with the smallest thickness and the maximum
+reflectance is that obtained from the family $f_{1}$. We
+also synthesized the corresponding
+structure and designated it {\em sample $S_2$}. The
+calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
 This structure has a very wide region where $ R(\lambda, \theta)>
-0.90$, which is located from 850 to 3000 nm and in an angular range 
-of $0^\circ$ to $70^\circ$. So, we can say that S-2 has a 
-quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm. On the other hand, 
-the profiles of the functions (with the optimized parameters) that 
-modulate the distribution of the $j-th$ period tuned to the $\lambda_ 
-{j}$, in the first analysis region, are shown in Fig. \ref{Fig1}(a). 
-In Fig. \ref{Fig1}(c), the profiles of the functions related to the 
-second region are plotted. In these figures, it is observed that the 
-profiles are very similar in each region of analysis. For example, in 
-the first analysis region, it is necessary that the photonic 
-structures have the least number of periods tuned in the areas where 
-the SP is absorbing and that they are the first periods of the 
-structure. In the second region, it is only necessary that the periods 
-have an adequate ordering.
-\begin{figure}[!ht]
+0.90$, which goes from 850 to 3000 nm in an angular range
+from $0^\circ$ to $70^\circ$. Thus, it has a
+quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm.
+The functions $f_i$ optimized for the region $\mathcal R_1$ are shown
+in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
+in Fig. \ref{Fig1}(c). The profiles $f_i$ are qualitatively
+similar. For example, for $\mathcal R_1$ the optimal photonic
+structures have a small number of periods tuned to the wavelengths where
+silicon has a large absorption, i.e.,  the first periods of the
+structure. For $\mathcal R_2$ it is only necessary that the periods
+have an adequate ordering. \notaL{No entendí qué hay que comentar en
+  este caso}
+\begin{figure}
   \label{Fig1}
@@
   \end{center}
-	\caption{Profiles of the optimized functions that modulate the distribution of the $j-th$ period tuned to the design $\lambda_ {j}$ for the analyzed structures in the region (a) from 350 to 1400 nm and (c) from 400 to 3000 nm.
-Reflectance spectra of the optimized structures in the region (b) from 350 to 1400 nm and (d) from 400 to 3000 nm.
-The dotted lines delimit the area where R $> 90\%$ and the dashed lines indicate the quasi-OD region.
-In the first region there is an OD gap and in the second region there is a quasi OD gap.
-Calculations are for non-polarized light.}
+  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
+    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
+    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
+    for non-polarized light
+    vs. wavelength and angle of incidence of the structure
+    optimized for the region $\mathcal R_1$ (panel b) and
+    $\mathcal R_2$ (panel d). The dotted lines
+    delimit the area where $R> 90\%$ and the dashed lines
+    indicate the quasi-OD region. In the first region there is
+    an OD gap and in the second region there is a quasi OD
+    gap.}
 \end{figure}
 
-We fabricate the optimized structures (S-1 and S-2) and measure their 
-reflectance spectra at various angles of incidence $\theta$. Due to 
+We measured the reflectance spectra of samples $S_1$ and $S_2$
+at various angles of incidence $\theta$. Due to
 experimental limitations, we restrict our results to the case of
 unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured
-reflectance are compared from 350 to 1400 nm for different angles of 
+reflectance corresponding to sample $S_1$ are compared from 350 to 1400 nm for different angles of
 incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
-$50^\circ$, and $60^\circ$) for S-1. They have very similar 
-characteristics. For example, for $\lambda>700$ nm and 
-$10^\circ < \theta < 40^\circ$, the spectrum differs by less than $5\%$ and for 
-$\theta > 40^\circ$ both spectra are qualitatively consistent but the 
-measured reflectance is less than the calculated one. This difference 
-can be attributed, in part, to the scattering of light at real 
-interfaces, which generally have a certain roughness 
+$50^\circ$, and $60^\circ$). The spectra are qualitatively similar,
+and for $\lambda>700$ nm and
+$10^\circ < \theta < 40^\circ$, they agree quantitatively, with a
+difference smaller than $5\%$. \notaL{Yo no veo nada especial en 40 grados: and for
+$\theta > 40^\circ$ both spectra are qualitatively consistent}  The
+measured reflectance is lower than the calculated one, more so at
+small wavelengths and large angles. This difference
+may be partially attributed to the scattering of light due to the
+roughness present at the sample
 \cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
-account in our theory. Reflectance was measured using unpolarized 
-light. Due to the limitations of the spectrophotometer, it is not 
-possible to perform measurements for $\theta>60^\circ$ and thus 
-check the OD gap. Therefore, in this angular range, we will limit 
-ourselves to saying that the structure has a quasi-omni-directional 
-bandgap (R$\left(\lambda,\theta \right)>90\%$) located between 980 and 
+account in our theory. Due to the limitations of our
+spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
+check the OD gap. Nevertheless, our results allow us to conclude that
+the structure has a quasi-omni-directional
+bandgap (R$\left(\lambda,\theta \right)>0.90$) between 980 and
 1340 nm.
-\begin{figure}[!ht]
+\begin{figure}
 	\label{Fig2}
@@
 	\end{center}
-	\caption{Reflectance spectra calculated and measured at different 
-	angles of incidence for structure (a) S-1 and (b) S-2.
-Reflectance spectra are for non-polarized light.
-The gray band indicates the region where the reflectance is greater than  $90\%$.
-This region corresponds to the quasi OD gap of the structure.
-Inset: photograph of the synthesized structure.}
+	\caption{Reflectance spectra for non-polarized light calculated and measured at different
+	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
+        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
+        (panel a)  and $S_2$ (panel b). The gray band indicates the
+        region where the reflectance is greater than  $0.90$,
+        corresponding to the quasi OD gap of the
+        structure. Inset: photograph of the synthesized structure.}
 \end{figure}
-
-On the other hand, Fig. \ref{Fig2}(b) shows the comparison of the 
-calculated reflectance spectra and the spectra measured in the range 
-from 400 to 3000 nm and the aforementioned incidence angles for S-2. 
-These spectra are also very similar. The difference between the 
-calculated and measured spectra at longer wavelengths, can be 
+In Fig. \ref{Fig2}(b) we compare the
+calculated and measured spectra of sample $S_2$ in the range
+from 400 to 3000 nm.
+Both spectra are very similar, with some differences at long
+wavelengths which can be
 attributed to an increase of imperfections such as wavy layers and
@@
 of the electrolyte as the thickness of the structure is increased
-\cite{Negro2003,Vincent1993}. According to the results obtained, this 
+\cite{Negro2003,Vincent1993}. According to our results, this
 structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm
@@
 
-Another technique for designing structures that reflect across a wide range of the 
-electromagnetic spectrum is to stack sub-mirrors tuned to different wavelengths. For 
+Another class of techniques for designing good reflectors across a wide spectral range
+is to stack sub-mirrors tuned to different wavelengths chosen with
+different criteria. For
 example, Agarwal et al. \cite{Agarwal2003} proposed to stack sub-mirrors as follows:
-first select the $\lambda_{1}$ value from the initial sub-mirror, then subsequent 
-$\lambda$ values obey a simple relation $\lambda_{i+1} + \lambda_{i}=2+i$, where $i$ 
-represents the sub-mirror number. Furthermore, Estrada-Wiese et al. \cite{DelRio2018} 
+tune the first sub-mirror to certain wavelength $\lambda_{1}$. Tune
+subsequent submirrors $j$ to wavelengths $\lambda_j$, chosen so that $\lambda_{j+1} +
+\lambda_{j}=2+j$ \notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
 developed a method that combines three stochastic optimization algorithms together with
@@
 
-In this technique, we continue to use the 
-propagation of Bloch waves in periodic structures, since this allows 
-us to know the frequencies that cannot propagate through the 
-structure. These are obtained by analyzing the expression
+We recall that for a periodic structure, the propagation of
+electromagnetic waves is described by the dispersion relation
 \begin{equation}
-	 \cos (KD) = \frac{1}{2} \text{Tr}M,   \label{Dispersion}
+	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
 \end{equation}
-where $D$ is the thickness of the sub-mirror, $\pm K$ 
-represents the Bloch vector that propagates in the sub-mirror 
-\cite{Mochan1987, Mochan1988, Perez2018}, Tr denotes the trace 
-and $M$ is the matrix given by Eq. \ref{MsBloch}. This equation 
-is limited by the minimum and maximum values that the 
-cosine function can take. Also, if the value of 
-$\left\vert\text {Tr} \left(M \right) \right\vert$ is $>2$, it 
-indicates that this frequency will not be able to propagate 
-through the structure.
+where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
+period of thickness $D$ \cite{Mochan1987, Mochan1988,
+  Perez2018}. \notaL{Tr was already defined and the reference to the
+  equation is wrong:  denotes the trace
+and $M$ is the matrix given by Eq. \ref{MsBloch}}. Thus,
+whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
+electromagnetic energy cannot propagate in the periodic system and we
+expect a high reflectance for a finite system made of a finite number
+of periods. This suggests the following design. We stack submirrors
+each made of a few periods of a periodic system such that its photonic band gap
+(PBG) overlaps the PBG of the previous and that of the next
+submirror. The number of periods of each sub-mirror is an
+important parameter. If it is too small, the sub-mirror would be
+partially transparent within the PBG. If it is too large, the
+resulting structure would be too thick. We followed two design
+strategies: In the first, we considered sub-mirrors each with the same
+number of periods. In the second, a different number of periods was
+assigned to each submirrors with a PBG center within different
+spectral regions: we used a single period for
+$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
+and three periods for $650<\lambda_ {D}<800$ nm.  and for
+$\lambda_{D}>800$ nm, the number of periods was variable.\notaL{No se
+  entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se
+  optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
+In both
+designs, the optimal overlap of two consecutive PBGs was obtained that
+maximized reflectance.\notaL{No quisiste decir average reflectance
+  $\braket{R}$?. Si sí, en qué rango promediaste?}
+Reflectance spectra were calculated for
+$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.
 
-It is common to imagine that the stacking of the sub-mirrors is as 
-follows: that the PBG of the $j+1-th$ mirror starts at the edge of the 
-PBG of the $j-th$ mirror and stack enough mirrors until covered the 
-bandwidth of the desired range. However, with this configuration, the 
-reflectance has minimum values at each edge of to contiguous PBG.
-On the other hand, the number of periods of each sub-mirror is an 
-important parameter due to its direct dependence on the magnitude and 
-width of the photonic forbidden band. Since the structures are 
-synthesized using porous silicon, it is essential to minimize the 
-number of periods corresponding to the sub-mirrors of the visible 
-region. For these reasons, the design of the structure was carried 
-out in two different ways: in the first, constant periods were 
-considered and in the second, a constant number of periods was 
-assigned for the interval from 400 to 800 nm (a period for 
-$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm 
-and three periods for $650<\lambda_ {D}<800$ nm) and for 
-$\lambda_{D}>800$ nm, the number of periods was variable. In both 
-designs, the optimal overlap of two consecutive PBGs was obtained that 
-maximized reflectance. Reflectance spectra were calculated from 400 to 
-3000 nm in the spectral range of $0^\circ$ to $90^\circ$. 
 Table \ref{tab:table2} shows the number of periods of each sub-mirror
-($Np_{se}$), the total number of stacked sub mirrors ($N_{se}$), the 
+($Np_{se}$),\notaL{Está difícil esta notación. ¿De dónde vienen la s y
+  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la
+  p?} the total number of stacked sub mirrors ($N_{se}$)
+\notaL{El encabezado de la tabla está mal}, the
 thickness of the structure, the optimal overlap of two consecutive
@@
 corresponds to sub-mirrors with a variable number of periods according
-to the design wavelength. 
+to the design wavelength.\notaL{No entiendo nada: qué dejaste fijo y
+  qué permitiste variar para optimizar en cada bloque de la tabla?}
 \begin{table}[htbp]
   \begin{center}
-		\caption{Parameters that maximize the reflectance of photonic structures.}
+    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
     \label{tab:table2}
@@
       \hline % <-- Toprule here
-			\textbf{$Np_{se}$}&{\textbf{$Np_{se}$}} &\textbf{Thickness}&\textbf{Overlap}&\textbf{$R_{Ave}$}\\
+      \textbf{$Np_{se}$}&{\textbf{$Np_{se}$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
 			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
@@
       \hline
-			4&25&38.7&74&92.3\\			\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
+      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
       10&13&45.4&56&95.34\\
@@
 According to table \ref{tab:table2}, the structure that has the highest
-reflectance is in the second block. We will call this structure S-3. In 
-S-3, the overlap of two consecutive PBGs is $78\%$, their thickness is 
-41.5 $\mu$ m, and the average reflectance is $95.3\%$. Additionally, 
-S-3 is made up of 18 sub-mirrors tuned to the following wavelengths 
+reflectance is in the second block, with an optimal overlap between
+consecutive PBGs of $78\%$, a thickness of
+41.5 $\mu$m, and  average reflectance $\braket{0.953}$. It is made up
+of 18 sub-mirrors tuned to the following wavelengths
 400, 460, 510, 570, 640, 720,810,910, 1020, 1150, 1290, 1450, 1630,
-1830, 2060, 2320, 2610, and 2860 nm. The calculated and measured 
-reflectance spectra of S-3 are shown in Fig. \ref{Fig3}.
-\begin{figure}[!ht]
+1830, 2060, 2320, 2610, and 2860 nm.
+We synthesized this structure and designated it {\em sample $S_3$}.
+Its calculated and measured
+reflectance spectra are shown in Fig. \ref{Fig3}.
+\begin{figure}
 \begin{center}
@@
 \end{center}
-\caption{ (a) Calculated reflectance for the optimized structure S-3. (b) Comparison 
-	between the measured and calculated reflectance spectra at several angles of 
-	incidence. Reflectance spectra are for non-polarized light. The gray band indicates 
-	the region in which the reflectance is greater than 90$\%$.  Inset shows a 
+\caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
+  as a function of wavelength $\lambda$ and incidence angle
+  $\theta$. (b) Measured and calculated reflectance spectra at several
+  angles of incidence $\theta=10^\circ$, $20^\circ$,
+  $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
+  the region in which the reflectance is greater than $R>0.90$.  Inset shows a
   photograph with a top view of the synthesized structure.}
@@
 
-The reflectance mapping shown in Fig. \ref{Fig3}(a) reveals a quasi omnidirectional 
-mirror in the range from 950 to 2900 nm, and angular range between $0^\circ$ and 
-$60^\circ$. It is also observed that at incidence angles $>$70${{}^\circ}$, for long 
+Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
+mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
+$60^\circ$. It is also observed that at incidence angles $\theta
+>70^\circ$ and long
 wavelengths the reflectance decreases and has oscillations, which are attributed to the
@@
 Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
-calculated and measured reflectance for the structure S-3, at several angles of 
+calculated and measured reflectance for the structure $S_3$ at several angles of
 incidence. Although, the quasi omnidirectional wavelength range of the synthesized
 structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
-PBG is almost twice as wide as a recently reported PS chirped structure \cite{Chavez2020}.
+PBG is almost twice as wide as a recently reported PS chirped
+structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? ¿Era
+  la mejor que había? Habría que decirlo}
 
-Finally, table \ref{tab:table3} shows some porous silicon based OD mirrors designed to operate in the NIR 
-region and the width of the omnidirectional band gap is compared with the structures 
+Finally, Table \ref{tab:table3} shows some porous silicon based OD mirrors designed to operate in the NIR
+region and the width of the omnidirectional band gaps are compared
+with those of the structures
 analyzed in the present study. The table reveals that the porous silicon based
-structures ST-B and ST-C have the widest gap width, being 1.36 times greater than the 
+structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
 largest reported work until now in the NIR region \cite{Wu2021}.
 
-\begin{table}[!ht]
+\begin{table}
   \begin{center}
-		\caption{Summary of the development in porous silicon based ODBMs designed in the NIR region.}
+    \caption{Development of porous silicon based ODBMs for the NIR region.}
     \label{tab:table3}
-		\begin{tabular}{|c|c|c|c|}
+    \begin{tabular}{ccccc}
       \hline % <-- Toprule here
-		\textbf{Reference}&\textbf{Year}&\textbf{ODBM range}&\textbf{ODBM width}\\
+      \multicolumn{2}{c}{\textbf{Reference}}&\textbf{Year}&\textbf{ODBM range}&\textbf{ODBM width}\\
                         & &(nm)&(nm)\\%&\textbf{ST-B}&\textbf{ST-C}\\
-			\hline % <-- Midrule here
-Bruyant, et al. \cite{Bruyant2003} & 2003 & 1100-1440 & 340 \\
-Xifre-P\'{e}rez, et al. \cite{Xifre2005} & 2004 & 1297-1615 & 318\\
-Estevez, et al. \cite{Estevez2009} & 2009 & 950-1456 & 506 \\
-Chavez, et al. \cite{Chavez2020} & 2020 & 1000-2000 & 1000 \\
-Wu, et al. \cite{Wu2021} &2021&1284-2605&1321 \\
-			\hline % <-- Bottomrule here
-			\begin{tabular}{c|c}
-					&ST-A\\
-					This article&ST-B\\
-				&ST-C\\
-			\end{tabular}&
-			\begin{tabular}{c}
-			\\
-			\\
-			\\
-			\end{tabular}&
-		\begin{tabular}{c}
-			980-1340\\
-			980-2780\\
-			950-2750\\
-		\end{tabular}&
-		\begin{tabular}{c}
-			360\\
-			1800\\
-			1800\\
-		\end{tabular}\\
-		\hline % <-- Bottomrule here
+      \hline
+      \multicolumn{2}{c}{Bruyant, et al. \cite{Bruyant2003}}& 2003 & 1100-1440 & 340 \\
+      \multicolumn{2}{c}{Xifre-P\'{e}rez, et al. \cite{Xifre2005}} & 2004 & 1297-1615 & 318\\
+      \multicolumn{2}{c}{Estevez, et al. \cite{Estevez2009}} & 2009 & 950-1456 & 506 \\
+      \multicolumn{2}{c}{Chavez, et al. \cite{Chavez2020}}& 2020 & 1000-2000 & 1000 \\
+      \multicolumn{2}{c}{Wu, et al. \cite{Wu2021}}&2021&1284-2605&1321 \\
+      \hline
+                  &$S_1$&&980-1340&360 \\
+      This work   &$S_2$&2021&980-2780&1800\\
+                  &$S_3$&&950-2750&1800\\
+      \hline
     \end{tabular}
@@
 \section{Conclusion}\label{s:conc}
-\notaV {Se replantean las conclusiones}.
 
-We have designed, fabricated and characterized highly 
-reflective q-OD (angular range of $0-60^\circ$) 
-multilayer structures, with a wide spectral range, 
-optimized through two techniques: chirping and stacking 
-Bragg-type sub-structures. Numerical calculations were 
-carried out by employing the transfer matrix method, 
-incorporating a Perl Minuit module in order to maximize 
-the average reflectance of the structures. Some of the 
-optimized structures were manufactured with PS dielectric 
-multilayers and compared with their simulations. For the 
-chirping method, a couple of structures were fabricated, 
-one with thicknesses of 21.6 $\mu$m and other with thickness 
-of 60.4 $\mu$m, resulting in reflectivity q-OD bands of 
-360 nm and 1800 nm, centered at 1160 nm and 1925 nm, 
-respectively. For staking sub-structures method we 
-obtained a 41.5 $\mu$m thickness mirror with a q-OD 
-band of 1800 nm centered at 1850 nm. Therefore, the second technique is found to be better as it results in structures with relatively
-less thickness  along with noticeable improvement 
-in average reflectance. Additionally, the analysis 
-techniques developed here can be used to optimize 
-reflectance with other refractive index contrasts 
-in PS multilayers or in different systems with other 
-types of materials. Such proposed structures could 
-be used as mirrors for solar concentrators, flat 
-focusing reflectors, thermal regulators, or, if 
-defects are included, as filters or remote 
-chemical/biosensors with a wide angular independent response.
+We have designed, fabricated and characterized highly reflective quasi
+omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
+spectral range, optimized through two techniques: chirping and
+stacking of Bragg-type sub-structures. Numerical calculations were
+carried out employing the transfer matrix method and we optimized the
+design parameters to maximize the average reflectance of the
+structures. We manufactured some of the optimized structures with
+porous silicon
+dielectric multilayers and compared their measured  optical properties
+to the results of calculations. For the
+chirping method, a couple of structures were fabricated, one with
+a thicknesses of 21.6 $\mu$m and another with a thickness of 60.4 $\mu$m,
+resulting in reflectivity q-OD bandwidthso of 360nm and 1800nm centered
+at 1160nm and 1925nm, respectively. For the stacked sub-structures
+method we obtained a 41.5$\mu$m thickness mirror with a q-OD
+bandwidth of
+1800nm centered at 1850nm. Therefore, the second technique is found
+to be better as it results in thiner structures with a noticeable
+improvement in the average
+reflectance. Additionally, the analysis techniques developed here can
+be used to optimize the reflectance for other refractive index contrasts
+in PS multilayers or in different systems with other types of
+materials. Such proposed structures could be used as mirrors for solar
+concentrators, flat focusing reflectors, thermal regulators, or, if
+defects are included, as filters or remote chemical/biosensors with a
+wide angular independent response.
 

### 2021-01-19 PaperVictor.tex
Atendi comentarios de Dr. Mochán

@@
   en no usar tipografía matemática para símbolos como $R$. Los
-  símbolos de menor y mayor no corresponden a los de promediar.}. of PS-based mirrors is maximized within a wide
+  símbolos de menor y mayor no corresponden a los de promediar.}
+\notaV{Fue un error mio. No habia agregado el paquete "braquet"}. of PS-based mirrors is maximized within a wide
 wavelength and angular range for different porosity contrasts. Optimization is
 performed to maximize the reflectance for minimum  thickness of the structure in the
-visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The
-mirrors are designed \notaL{No entiendo para qué haber cambiado el
-  modo de activo a pasivo; es mucho mejor el activo.} using \textit{chirped}-type structures and \textit{stacking}
+visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum. We design the
+mirrors  \notaL{No entiendo para qué haber cambiado el
+  modo de activo a pasivo; es mucho mejor el activo.} 
+\notaV{Cambie la oracion a voz activa} using \textit{chirped}-type structures and \textit{stacking}
 sub-mirrors. The chirped structures are found to be more suitable for the Vis range,
@@
 
-We develop two techniques to design
-multilayer photonic structures. In the first, the wavelength
-($\lambda _{j}$) to which the $j$-th pair of layers is tuned is modulated by
-a given function of $j$. Several functions are proposed and their
-parameters are optimized to maximize the $\braket{R}$ averaged over
-wavelength and angle over a suitable range.
-To that end we employed the Minuit module of the Perl Data Language (PDL) \cite{minuit}.
-The other technique we employed consisted in stacking
-sub-mirrors tuned to different wavelengths, chosen so that their
-spectral ranges overlap. For each submirror, the spectral range was
-obtained from the dispersion relation of a corresponding periodic
-structure.
+\notaV{Regreso el parrafo de la primera versi\'{o}n}
 
-For the analysis of the propagation of electromagnetic fields
-through multilayer systems, we employ a variant of the transfer matrix
-method based on the formalism of Puente-Díaz et al. \cite{Puente2020}.
-Its advantage over other formally equivalent approaches
-\cite{Mochan1987,Ortiz2020,Chavez2020} is that it allows a
-numerically stable
-calculation of the reflectance even of very large multilayer systems,
-even in the presence of absorption.
-We assume  the system has  variations only along the $z$ direction
-and consider an incident linearly polarized beam of light
-(either TE or TM polarization) that propagates throughout
-the structure. The reflectance and transmittance are given by
-$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$,
-respectively, with \cite{Puente2020}
+For the analysis of the propagation of electromagnetic fields through
+multilayer systems it is usual to employ the transfer matrix
+method \cite{PerezA2004,Pochi2005} \notaL{reference}. Assuming the system is 1D, with variations
+only along the $z$ directions, and that the polarization of light is either
+transverse electric (TE) or transverse magnetic (TM), the
+transfer matrix $M\left(z_{2},z_{1}\right)$ is
+a 2x2 matrix that relates the components of the electric $E_{\| }$
+and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
+evaluated at $z_2$ to their value at $z_{1}$,
+\begin{equation*}
+	\left(
+	\begin{array}{c}
+		E_{\|} \\
+		H_{\| }%
+	\end{array}%
+	\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
+	\begin{array}{c}
+		E_{\| } \\
+		H_{\| }%
+	\end{array}%
+	\right) _{z_{1}}.
+\end{equation*}%
+Many equivalent formulations have been proposed to obtain and use $M$
+\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
+for the numerically stable calculation of the reflectance of large
+multilayer systems, as
+proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
+supplementary information. The
+explicit expressions for the optical coefficients are:
 \begin{equation}
-	r=\sigma \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
+	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
 		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
@@
 \begin{equation}
-	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
+	t=\frac{2Z_{\alpha
+	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
 \end{equation}%
-where $Z_0$ and $Z_s$ are the surface impedances of vacuum
-and substrate, respectively, $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$,
-$\sigma=-1$ and
-$\zeta =Z_s$ for
-TE polarization, while $\beta=\text{Re}Z_{s}/
-\text{Re}Z_{0}$, $\sigma=+1$, and $\zeta =Z_0$ for TM
-polarization.
-Here, $M_{ij}$ are the elements
-of the reconstructed transfer matrix
-\begin{equation}
-\resizebox{\textwidth}{!}{$\displaystyle{
-	M=\frac{1}{Z^{+}-Z^{-}} \left(
-	\begin{array}{cc}
-		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  &
-		-2iZ^{+}Z^{-}\sin KD \\
-		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
-		iKD\right)
-	\end{array}%
-	\right) \text{.}}$}
-\label{MsBloch}
-\end{equation}
-which relates the electromagnetic fields at the substrate to those at
-the surface,
-Here, $Z^{\pm }$ are the surface impedances of the multilayered system
-for fields propagating toward the substrate ($+$) or towards vacuum
-($-$), and are given by
-\begin{equation}
-	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
-\end{equation}%
-where
-\begin{equation}
-	\Lambda _{-}=\frac{1}{2}\text{Tr}\,\widetilde{M}\pm
-        i\sqrt{1-\left( \text{Tr}\,\widetilde{M}/2\right)
-		^{2}}\text{,}  \label{LBloch}
-\end{equation}%
-is chosen to satisfy the inequality $\left\vert \Lambda
-_{-}\right\vert >1$, and $\Lambda _{+}=1/\Lambda _{-}$, and Tr denotes
-the trace. $\widetilde{M}$ denotes the usual transfer matrix
-\begin{equation}
-	\widetilde{M} = \prod \limits_{j=1}^{N}%
-	\begin{pmatrix}
-		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\
-		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
-	\end{pmatrix}%
-	\label{Mcoef}
-\end{equation}%
-of the multilayered system, where
-\begin{equation}
-	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
-\end{equation}%
-is the normal component of the wave vector whithin the $j$-th layer, $Z_{j}$ is
-its surface impedance, $Y_{j}=1/Z_{j}$ its surface
-admittance, $\epsilon _{j}=n_{j}^{2}$ its permitivity (for simplicity we
-assumed all media were nonmagnetic, with permeability $\mu _{i}=1$),
-$q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
-the wavelength $\lambda $ and
-\begin{equation}
-	Q=n_{0}q\sin \theta _{i}  \label{Snell}
-\end{equation}%
-is the projection of wavevector onto the interfaces,
-which is conserved according to Snell's law, with
-$\theta _{i}$ the angle of incidence. The surface
-impedances are given by $Z_{j}=q/k_{j}$ for TE
-polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for
-TM polarization. The complex refractive index of the porous layers were
-obtained through the Bruggeman's effective medium
-theory, which has been reported to adequately reproduce
-the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.
+where $M_{ij}$ are the elements
+of the transfer matrix which transfer
+the fields from its surface interface with vacuum at $z_0$ towards the
+substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
+surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
+of the reflected and transmitted fields, where we choose the $F$'s as electric
+fields for (TE) polarization and magnetic fields
+for transverse magnetic polarization (TM). The upper sign $-$ in
+Eq. (\ref{rBloch}) and the subscript $\alpha =s$
+in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
+the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
+polarization, respectively.
+The reflectance is given by
+$R=|r|^{2}$ and the
+transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
+=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
+TM polarization. The complex refractive index of the porous
+layers were obtained through the Bruggeman's effective medium theory, which
+has been reported to adequately reproduce the PS optical parameters
+\cite{Giusseppe2011,Pap2006,Estrada2018}.
 
@@
   la referencia.}
+
 \section{Experimental details}\label{s:exp}
@@
   explicó cómo se hizo el diseño?}
+
+\notaV{En el siguiente parrafo se explican los procesos de diseño}
+
+We develop two techniques to design
+multilayer photonic structures. In the first, the wavelength
+($\lambda _{j}$) to which the $j$-th pair of layers is tuned is modulated by
+a given function of $j$. Several functions are proposed and their
+parameters are optimized to maximize the $\braket{R}$ averaged over
+wavelength and angle over a suitable range.
+To that end we employed the Minuit module of the Perl Data Language (PDL) \cite{minuit}.
+The other technique we employed consisted in stacking
+sub-mirrors tuned to different wavelengths, chosen so that their
+spectral ranges overlap. For each submirror, the spectral range was
+obtained from the dispersion relation of a corresponding periodic
+structure.
+
 \subsection{Chirped-type Bragg mirrors}\label{ss:chirped}
@@
   theoretical, right?}
+ \notaV{Podr\'{i}a utilizar el t\'{e}rmino "OD width" para referirme al ancho omnidireccional del espejo}
 of 250 nm centered at 1125 nm with a
@@
 silicon has a large absorption, i.e.,  the first periods of the
-structure. For $\mathcal R_2$ it is only necessary that the periods
-have an adequate ordering. \notaL{No entendí qué hay que comentar en
+structure. 
+\notaV{replanteo la idea: "For $\mathcal R_2$ it is only necessary that the periods have an adequate ordering.}
+\notaL{No entendí qué hay que comentar en
   este caso} 
+Due in $\mathcal R_2$, the absorption of porous silicon is negligible, the periods are distributed quasi-evenly.
+
 \begin{figure}
@@
 incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
-$50^\circ$, and $60^\circ$). The spectra are qualitatively similar,
-and for $\lambda>700$ nm and
-$10^\circ < \theta < 40^\circ$, they agree quantitatively, with a
-difference smaller than $5\%$. \notaL{Yo no veo nada especial en 40 grados: and for
-$\theta > 40^\circ$ both spectra are qualitatively consistent}  The
+$50^\circ$, and $60^\circ$). The spectra are qualitatively 
+similar, and for $\lambda>700$ nm and $10^\circ < \theta < 
+40^\circ$, they agree quantitatively, with a difference smaller 
+than $5\%$.
+\notaL{Yo no veo nada especial en 40 grados: and for
+$\theta > 40^\circ$ both spectra are qualitatively consistent} \notaV{De acuerdo. Se puede omitir}
+The
 measured reflectance is lower than the calculated one, more so at
@@
 is to stack sub-mirrors tuned to different wavelengths chosen with
-different criteria. For
-example, Agarwal et al. \cite{Agarwal2003} proposed to stack sub-mirrors as follows:
-tune the first sub-mirror to certain wavelength $\lambda_{1}$. Tune
-subsequent submirrors $j$ to wavelengths $\lambda_j$, chosen so that $\lambda_{j+1} +
-\lambda_{j}=2+j$ \notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
+different criteria. 
+\notaV{I rewrote this "For example, Agarwal et al. 
+	\cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
+	tune the first sub-mirror to certain wavelength $\lambda_{1}$. 
+	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
+	chosen so that $\lambda_{j+1} + \lambda_{j}=2+j$."} 
+For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic 
+structure in which she stacked 54 sub-mirrors as follows: the 
+first sub-mirror consisted of 2.5 periods and tuned it to 
+$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to the 
+wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1} 
++ \lambda_{j}=2+j$ with 4 periods for each of the following 
+periods.
+\notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
 developed a method that combines three stochastic optimization algorithms together with
@@
   equation is wrong:  denotes the trace
-and $M$ is the matrix given by Eq. \ref{MsBloch}}. Thus,
+and $M$ is the matrix given by Eq. \ref{MsBloch}}. \notaV{Entendido, gracias} Thus,
 whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
@@
 and three periods for $650<\lambda_ {D}<800$ nm.  and for
-$\lambda_{D}>800$ nm, the number of periods was variable.\notaL{No se
-  entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se
-  optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
-In both
-designs, the optimal overlap of two consecutive PBGs was obtained that
-maximized reflectance.\notaL{No quisiste decir average reflectance
-  $\braket{R}$?. Si sí, en qué rango promediaste?}
+$\lambda_{D} \geq 800$ nm, the number of periods was variable.
+\notaL{No se entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
+\notaV{Los números de periodos uno, dos, tres, los eleg\'{i} para 
+	que la estructura tenga pocos periodos en la region visible. 
+	Adem\'{a}s, del c\'{a}lculo de las Trazas y reflectancias de 
+	los subespejos individuales sintonizados de 1000 a 2500 nm, 
+	tambi\'{e}n tienen una regi\'{o}n de propagaci\'{o}n prohibida 
+	en el intervalo de 400 a 900 y la reflectancia es mayor al 
+	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf}
+In both designs, the optimal overlap of two consecutive PBGs was obtained that maximized reflectance.
+\notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
 Reflectance spectra were calculated for
@@
 
-Table \ref{tab:table2} shows the number of periods of each sub-mirror
-($Np_{se}$),\notaL{Está difícil esta notación. ¿De dónde vienen la s y
-  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la
-  p?} the total number of stacked sub mirrors ($N_{se}$)
-\notaL{El encabezado de la tabla está mal}, the
+Table \ref{tab:table2} shows the number of periods of each sub-mirror ($p$),
+\notaL{Está difícil esta notación. ¿De dónde vienen la s y
+  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
+the total number of stacked sub mirrors ($N_{se}$)
+\notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
 thickness of the structure, the optimal overlap of two consecutive
@@
 corresponds to sub-mirrors with a variable number of periods according
-to the design wavelength.\notaL{No entiendo nada: qué dejaste fijo y
-  qué permitiste variar para optimizar en cada bloque de la tabla?}
+to the design wavelength. \notaL{No entiendo nada: qué dejaste 
+	fijo y qué permitiste variar para optimizar en cada bloque de la tabla?}
+\notaV{En el primer bloque \'{u}nicamente se optimiz\'{o} el traslape de dos PBGs consecutivos.
+En el segundo bloque, se optimizaron el n\'{u}mero de periodos (de 4 a 10 periodos) de los subespejos sintonizados a $\lambda_{D} \geq 800$ nm y el traslape de dos PBGs consecutivas.}
 \begin{table}[htbp]
@@
       \hline % <-- Toprule here
-      \textbf{$Np_{se}$}&{\textbf{$Np_{se}$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
+      \textbf{$p$}&{\textbf{$N$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
 			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
@@
 of 18 sub-mirrors tuned to the following wavelengths
-400, 460, 510, 570, 640, 720,810,910, 1020, 1150, 1290, 1450, 1630,
-1830, 2060, 2320, 2610, and 2860 nm.
+400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450, 
+1630, 1830, 2060, 2320, 2610, and 2860 nm.
 We synthesized this structure and designated it {\em sample $S_3$}.
@@
 PBG is almost twice as wide as a recently reported PS chirped
-structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? ¿Era
-  la mejor que había? Habría que decirlo}
+structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? 
+	¿Era la mejor que había? Habría que decirlo}
+\notaV{S\'{i}, es la estructura, a base de SP, que tiene el mayor ancho OD}
 

### 2021-01-20 PaperVictor.tex
Corregi errores ortograficos

@@
 \notaL{Creo que no se ha explicado el proceso de diseño. No sé para
-  qué damos tanto detalle sobre cómo se calculó, dado que todo está en
-  la referencia.}
+  qué damos tanto detalle sobre cómo se calculó, dado que todo está en la referencia.}
+\notaV{El proceso de diseño se explica en la secci\'{o}n de discusi\'{o}n y \}resultados}
 
@@
 	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
-	chosen so that $\lambda_{j+1} + \lambda_{j}=2+j$."} 
+	chosen so that $\lambda_{j+1} - \lambda_{j}=2+j$."} 
 For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic 
@@
 wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1} 
-+ \lambda_{j}=2+j$ with 4 periods for each of the following 
-periods.
+- \lambda_{j}=2+j$ (with its suitable units) with 4 periods for 
+each of the following periods. 
 \notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
@@
 	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf} 
-In both designs, the optimal overlap of two consecutive PBGs was obtained that maximized reflectance.
+\notaV{Tambi\'{e}n fue a prueba y error}
+In both designs, the optimal overlap of two consecutive PBGs was 
+obtained that maximizes the average reflectance $\braket{R}$.
 \notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
@@
   la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
-the total number of stacked sub mirrors ($N_{se}$)
+the total number of stacked sub mirrors ($N$)
 \notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
@@
 calculated and measured reflectance for the structure $S_3$ at several angles of
-incidence. Although, the quasi omnidirectional wavelength range of the synthesized
-structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
-PBG is almost twice as wide as a recently reported PS chirped
-structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? 
+incidence. Although, the quasi omnidirectional wavelength range of 
+the synthesized structure is slightly smaller than the calculated 
+one, from 950 to 2750 nm, the measured PBG is almost twice as wide 
+as a recently reported PS chirped structure \cite{Chavez2020}, his 
+structure has the largest reported OD width.. 
+\notaL{Por qué comparamos con ésta? 
 	¿Era la mejor que había? Habría que decirlo}

### 2021-01-20 PaperVictor.tex
Revise Victor et al. revisions.

--- 2021-01-19 PaperVictor.tex
@@
 structure.
-\notaV{replanteo la idea: "For $\mathcal R_2$ it is only necessary that the periods have an adequate ordering.}
-\notaL{No entendí qué hay que comentar en
-  este caso} 
-Due in $\mathcal R_2$, the absorption of porous silicon is negligible, the periods are distributed quasi-evenly.
+As in $\mathcal R_2$ the absorption of porous silicon is negligible,
+the periods are distributed quasi-evenly. \notaL{Sigo sin
+  entender. ¿La absorción del silicio poroso depende de la muestra?
+  ¿Qué significa quasi-evenly? Quité el 'due', pues era mala redacción}
 
@@
 than $5\%$.
-\notaL{Yo no veo nada especial en 40 grados: and for
-$\theta > 40^\circ$ both spectra are qualitatively consistent} \notaV{De acuerdo. Se puede omitir}
 The
@@
 different criteria.
-\notaV{I rewrote this "For example, Agarwal et al. 
-	\cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
-	tune the first sub-mirror to certain wavelength $\lambda_{1}$. 
-	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
-	chosen so that $\lambda_{j+1} + \lambda_{j}=2+j$."} 
 For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic
-structure in which she stacked 54 sub-mirrors as follows: the 
-first sub-mirror consisted of 2.5 periods and tuned it to 
-$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to the 
+structure in which 54 sub-mirrors were stacked as follows:\notaL{I
+  changed to passive to avoid the fact that Agarwal did the stacking} the
+first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} tuned to
+$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to
 wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
-+ \lambda_{j}=2+j$ with 4 periods for each of the following 
-periods.
-\notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
+- \lambda_{j}=2+j$ (with its suitable units)\notaL{This is still
+  wrong and/or I don't understand. What are these suitable units? Why
+  the mistery? $j$ numbers
+  periods or sub-mirrors? Do you mean (2+j) nm, such as the sequence
+  700, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
+  $\lambda_{54}=700+2*53+54*55/2-1=2290$?} with 4 periods for
+each of the following periods.
+Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
 developed a method that combines three stochastic optimization algorithms together with
@@
 period of thickness $D$ \cite{Mochan1987, Mochan1988,
-  Perez2018}. \notaL{Tr was already defined and the reference to the
-  equation is wrong:  denotes the trace
-and $M$ is the matrix given by Eq. \ref{MsBloch}}. \notaV{Entendido, gracias} Thus,
+  Perez2018}. Thus,
 whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
@@
 partially transparent within the PBG. If it is too large, the
-resulting structure would be too thick. We followed two design
+resulting structure would be too thick. This is particularly important
+for submirrors tuned to shorter wavelengths, for which there is some
+absorption. We followed thus two design
 strategies: In the first, we considered sub-mirrors each with the same
-number of periods. In the second, a different number of periods was
-assigned to each submirrors with a PBG center within different
-spectral regions: we used a single period for
-$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
-and three periods for $650<\lambda_ {D}<800$ nm.  and for
-$\lambda_{D} \geq 800$ nm, the number of periods was variable.
-\notaL{No se entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
-\notaV{Los números de periodos uno, dos, tres, los eleg\'{i} para 
-	que la estructura tenga pocos periodos en la region visible. 
-	Adem\'{a}s, del c\'{a}lculo de las Trazas y reflectancias de 
-	los subespejos individuales sintonizados de 1000 a 2500 nm, 
-	tambi\'{e}n tienen una regi\'{o}n de propagaci\'{o}n prohibida 
-	en el intervalo de 400 a 900 y la reflectancia es mayor al 
-	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf}
-In both designs, the optimal overlap of two consecutive PBGs was obtained that maximized reflectance.
-\notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
-Reflectance spectra were calculated for
-$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.
+number $p$ of periods. In the second, a different number of periods was
+assigned to each submirror according to the center of its PBG: we chose
+a single period for those submirrors $j$ tuned to
+$\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
+three periods for $650<\lambda_ {j}<800$ nm, and for
+$\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
+4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para
+  cada subespejo?}
+In both designs, the degree of overlap of consecutive PBGs was
+taken as the parameter to be optimized in order to maximize
+the reflectance $\braket{R}$ averaged within the spectral and
+angular range $400\text{nm}\le
+\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.
 
-Table \ref{tab:table2} shows the number of periods of each sub-mirror ($p$),
-\notaL{Está difícil esta notación. ¿De dónde vienen la s y
-  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
-the total number of stacked sub mirrors ($N_{se}$)
-\notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
-thickness of the structure, the optimal overlap of two consecutive
-PBGs and the average reflectance. The first block corresponds to
-sub-mirrors with a constant number of periods, while the second block
-corresponds to sub-mirrors with a variable number of periods according
-to the design wavelength. \notaL{No entiendo nada: qué dejaste 
-	fijo y qué permitiste variar para optimizar en cada bloque de la tabla?}
-\notaV{En el primer bloque \'{u}nicamente se optimiz\'{o} el traslape de dos PBGs consecutivos.
-En el segundo bloque, se optimizaron el n\'{u}mero de periodos (de 4 a 10 periodos) de los subespejos sintonizados a $\lambda_{D} \geq 800$ nm y el traslape de dos PBGs consecutivas.}
+Table \ref{tab:table2} shows the optimized values of the average
+reflectance $\braket{R}$ for
+different choices of the number of periods $p$ of each sub-mirror, as
+discussed above, including the resulting number $N_m$ of stacked sub
+mirrors, the thickness $d$ of the structure, and the optimal
+overlap of consecutive PBGs. The first and second blocks correspond to
+the first and second strategies discussed above.
 \begin{table}[htbp]
   \begin{center}
-    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
+    \caption{Total number $N_m$ of stacked submirrors, thickness $d$,
+      overlap between consecutive PBG and average reflectance
+      $\braket{R}$ for optimized structures designed with a
+      number $p$ of periods per submirror (first block) or a number $p$
+      of periods for those submirrors tuned to wavelengths
+      $\lambda_j\geq 800$nm (second block, see text), for different
+      values of $p$. The parameters corresponding to the best design
+      are typeset in bold.}
     \label{tab:table2}
-    \begin{tabular}{|c|c|c|c|c|}
-      \hline % <-- Toprule here
-      \textbf{$p$}&{\textbf{$N$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
-			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
+    \begin{tabular}{ccccc}
+      $p$&$N_m$&$d (\mu\text{m})$&\% overlap&$\braket{R}$\\
+      \hline
       \hline
@@
       \hline
-      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
-      10&13&45.4&56&95.34\\
+      4&25&38.7&74&92.3\\
+      \bf 6&\bf 18&\bf 41.5&\bf 78&\bf 95.4\\
+      10&13&45.4&56&95.3\\
       \hline
@@
 consecutive PBGs of $78\%$, a thickness of
-41.5 $\mu$m, and  average reflectance $\braket{0.953}$. It is made up
-of 18 sub-mirrors tuned to the following wavelengths
+41.5 $\mu$m, and an average reflectance $\braket{0.954}$. It is made up
+of 18 sub-mirrors tuned to the wavelengths
 400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450,
@@
 calculated and measured reflectance for the structure $S_3$ at several angles of
-incidence. Although, the quasi omnidirectional wavelength range of the synthesized
-structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
-PBG is almost twice as wide as a recently reported PS chirped
-structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? 
-	¿Era la mejor que había? Habría que decirlo}
-\notaV{S\'{i}, es la estructura, a base de SP, que tiene el mayor ancho OD}
+incidence. Although, the quasi omnidirectional wavelength range of
+the synthesized structure, from 950 to 2750 nm, is slightly smaller than the calculated
+one, the measured PBG is almost twice as wide
+as a recently reported PS chirped structure \cite{Chavez2020}, which
+has the largest previously reported OD width.
 
-Finally, Table \ref{tab:table3} shows some porous silicon based OD mirrors designed to operate in the NIR
+Finally, Table \ref{tab:table3} shows some porous silicon based OD
+mirrors designed to operate in the NIRy
 region and the width of the omnidirectional band gaps are compared

### 2021-01-20 PaperVictor.tex
Revise everything

@@
 \begin{abstract}
-Porous silicon (PS) is a very versatile material for developing optical
+Porous silicon is a very versatile material for developing optical
 devices based on multilayered structures, since high and low porosity layers
-can be synthesized by a simple electrochemical technique. In the present work, the
-average reflectance $\braket{R}$ \notaL{No entiendo por qué insisten
-  en no usar tipografía matemática para símbolos como $R$. Los
-  símbolos de menor y mayor no corresponden a los de promediar.}
-\notaV{Fue un error mio. No habia agregado el paquete "braquet"}. of PS-based mirrors is maximized within a wide
-wavelength and angular range for different porosity contrasts. Optimization is
-performed to maximize the reflectance for minimum  thickness of the structure in the
-visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum. We design the
-mirrors  \notaL{No entiendo para qué haber cambiado el
-  modo de activo a pasivo; es mucho mejor el activo.}
-\notaV{Cambie la oracion a voz activa} using \textit{chirped}-type structures and \textit{stacking}
-sub-mirrors. The chirped structures are found to be more suitable for the Vis range,
-while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication
-and testing of some optimized omnidirectional structures with less
-than 100 pairs of layers \notaL{Quizás periods no sea correcto, pues
-  no son periódicos} has
-been demonstrated.
+can be synthesized by a simple electrochemical technique. In the present work, we design
+mirrors using \textit{chirped}-type structures and by stacking
+appropriately tuned sub-mirrors, and we optimize the design parameters
+to maximize the
+optical reflectance $\braket{R}$ averaged within a wide
+spectral range  covering the visible and near infrared regions, and
+within a wide angular range. The chirped structures are found to be
+more suitable for the visible range,
+while stacked sub-mirrors are found to be better for the NIR
+region. We design, fabricate and characterize
+some of the optimized omnidirectional structures with less
+than 100 pairs of layers. We obtained a structure that has the an
+omnidirectional spectral width larger than those previously
+reported.\notaL{Es cierto?}\notaL{Quité los acrónimos del resumen}
 \end{abstract}
@@
 Photons entering a PC interact with its periodically varying dielectric constant and
-are consequently organized into photonic bands. Analogous to electrons in a
+are consequently organized into photonic bands. In analogy to electrons in a
 crystal, their propagation is forbidden if their energy lies
@@
 within in a PBG. For several applications it is useful to fabricate
-{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
-mirrors is limited due to their relatively large absorption at
-visible and near infrared frequencies.  An attractive alternative
+{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
+The use of metallic
+mirrors is limited due to their relatively large absorption at the
+visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
 consists of low-absorption dielectric
@@
 example, Chen et al. \cite{Chen1999},
-reported the fabrication of a
-6-pair TiO$_{2}$/SiO$_{2}$ structure with
-an OD band of about 70 nm in the NIR range, employing sol-gel deposition
+reported the fabrication of a structure made of six pairs of
+ TiO$_{2}$/SiO$_{2}$  layers with
+an OD band of about 70 nm in the NIR range, employing a sol-gel deposition
 method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
 grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
-GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs
+GaAs/Al$_{2}$O$_{3}$ by selective oxidation of the AlAs
 layers, to obtain an OD with a band from 710 to 950 nm.
@@
 used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
-_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
+_{2}$ layers) and radio frequen cy magnetron sputtering (for SiO$_{2}$
 layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
 592 to 668 nm. However, these techniques are expensive and they
-require sophisticated equipment and long fabrication times. Using PS
+require sophisticated equipment and long fabrication times. Use of PS
 is an attractive alternative, since it can be easily manufactured by
 electrochemical etching crystalline Si in an hydrofluoric
-acid based electrolyte, to obtain a sponge-like nanostructure composed
+acid based electrolyte to obtain a sponge-like nanostructure composed
 of Si and air. By modulating the supplied current and its application
@@
 contrast, layers of high porosity have to be employed, which makes the
-resulting structures relatively fragile. In addition, use of high porosity makes the fabrication of large structures, with a
+resulting structures relatively fragile. In addition, use of high
+porosity makes the fabrication of large structures, with a
 very large number of layers, unfeasible. For this reason, in this work
@@
 them to previous reports. We obtained significantly large band-widths
-with relatively thinner structures than reported before.
+with relatively thinner structures than reported previously.
 Finally, we discuss our conclusions in Section \ref{s:conc}.
@@
 \section{Theory} \label{s:theory}
-\notaV{Nombre de la sección propuesta por Dr. David}
-\notaL{Estoy en desacuerdo con el título Numerical simulations. Un
-  cálculo no es en general una simulación.}
-\notaV{Parrafos reescritos por Dr. David}
-\notaL{¿Por qué reescribir toda la teoría? ¿Por qué dar tanta teoría?}
-
-\notaV{Regreso el parrafo de la primera versi\'{o}n}
 
 For the analysis of the propagation of electromagnetic fields through
-multilayer systems it is usual to employ the transfer matrix
-method \cite{PerezA2004,Pochi2005} \notaL{reference}. Assuming the system is 1D, with variations
+multilayered systems it is usual to employ the transfer matrix
+method \cite{PerezA2004,Pochi2005}. Assuming the system is 1D, with variations
 only along the $z$ directions, and that the polarization of light is either
@@
 \begin{equation}
-	t=\frac{2Z_{\alpha
-	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
+	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
 \end{equation}%
@@
 fields for (TE) polarization and magnetic fields
-for transverse magnetic polarization (TM). The upper sign $-$ in
-Eq. (\ref{rBloch}) and the subscript $\alpha =s$
-in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
-the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
-polarization, respectively.
+for transverse magnetic polarization (TM). Here, $\sigma=-1$ and
+$\zeta= Z_s$ for TE polarization, while
+$\sigma=1$ and $\zeta=Z_0$ for TM
+polarization.
 The reflectance is given by
@@
 \cite{Giusseppe2011,Pap2006,Estrada2018}.
-
-\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
-  qué damos tanto detalle sobre cómo se calculó, dado que todo está en la referencia.}
-\notaV{El proceso de diseño se explica en la secci\'{o}n de discusi\'{o}n y \}resultados}
 
@@
 
-\notaL{Aquí quitaron un comentario mío. ¿Ya no es relevante? ¿Ya se
-  explicó cómo se hizo el diseño?}
-
-\notaV{En el siguiente parrafo se explican los procesos de diseño}
-
 We develop two techniques to design
 multilayer photonic structures. In the first, the wavelength
-($\lambda _{j}$) to which the $j$-th pair of layers is tuned is modulated by
+($\lambda _{j}$) to which the $j$-th pair of layers is tuned is determined by
 a given function of $j$. Several functions are proposed and their
-parameters are optimized to maximize the $\braket{R}$ averaged over
-wavelength and angle over a suitable range.
-To that end we employed the Minuit module of the Perl Data Language (PDL) \cite{minuit}.
-The other technique we employed consisted in stacking
+parameters are optimized to maximize the reflectance $\braket{R}$ averaged over
+a given spectral and angular range.
+The second technique consisted in stacking
 sub-mirrors tuned to different wavelengths, chosen so that their
@@
 obtained from the dispersion relation of a corresponding periodic
-structure.
+structure. The degree of overlap was optimized to maximize $\braket{R}$.
+The optimizations were done employing the Minuit module  \cite{minuit}
+of the Perl Data Language (PDL) \notaL{cita}.
 
@@
 maximum {\em design} wavelengths respectively, $N_p$ is the number of
-periods  in the structure and $f(\xi)$ is some smooth function that
-goes from 0 to 1 as its argument goes from surface ($\xi=0$) to the
+periods  in the structure and $f(\xi)$ is a smooth function that
+goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
 substrate ($\xi=1)$. We only consider increasing functions $f$ due to
-the high absorption of PS in the ultraviolet region which decreases in
-the visible and becomes negligible in the near infrared, so, the first
+the high absorption of PS in the ultraviolet region, which decreases in
+the visible and becomes negligible in the near infrared, so, that the first
 periods are tuned in the UV-Vis regions. We consider the
@@
 \begin{equation}
-f_{3}\left(\xi\right) =Ax^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
+f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
 \end{equation}
-where $\alpha$, $\beta$ and $A$ are parameters to optimize
-to maximize the average reflectance $\braket{R}$. The function
-$f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
-restricting  $\alpha>0$. The function $f_2$ is an arithmetic average
+where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
+to maximize the average reflectance $\braket{R}$ over given spectral
+and angular ranges. The class
+$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
+increasing profiles, $f_2$ is the arithmetic mean
 of two functions of the type $f_{1}$ with different
-powers $\alpha$ and $\beta$. The function $f_{3}$ (Eq. (\ref{F3})) is
+powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
 designed so that the first term dominates near the surface and the
@@
 The parameters
-$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize $\braket{R}$. The reflectance $R(\lambda,
-\theta)$ was calculated for non-polarized light in two regions of
-the electromagnetic spectrum. The first region, $\mathcal R_1$,  was chosen from 350 to
-1400 nm and second one $\mathcal R_2$ was selected from 400 to 3000 nm, both in the
-angular range of $0^\circ$ to $90^\circ$. For $\mathcal R_1$ we took
-$\lambda_{\min}$ as a parameter to be optimized while $\lambda_{\max}$
-was fixed at 1400 nm. For $\mathcal R_2$ we fixed both $\lambda_{\min}=850$nm and $\lambda_{\min}=3000$nm. The
-calculations were carried out using the Perl Data Language (PDL) and
-its interface with the MINUIT \cite{minuit} minimization package. The
-optimized parameters corresponding to low and high porosities $p_l=0.51$ and $p_h=0.76$
+$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
+reflectance for non-polarized light $\braket{R}$ averaged in the
+angular range of $0^\circ$ to $90^\circ$ and either in the
+spectral region $\mathcal R_1$ from 350 to
+1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
+$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
+was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
+$\lambda_{\min}=850$nm and $\lambda_{\min}=3000$nm. \notaL{Any reason
+  for these choices? They seem arbitrary.}
+%The
+%calculations were carried out using the Perl Data Language (PDL)
+%\notaL{cita} and
+%its interface to the MINUIT \cite{minuit} minimization package.
+\notaL{Creo que ya habíamos mencionado esto}.
+The
+optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
 are shown in Table \ref{tab:tableA}.
-
-\notaV {En caso de ser necesario "In the supplementary information we include the parameters for the porosity tests of $30/76 \% $ and $42/76 \%$."}
-
-\notaV{Se replanteo el contenido}
-
+\notaV {En caso de ser necesario: Results for other
+  pairs of porosities, $30/76 \% $ and $42/76 \%$, are included as
+  supplementary information.}
 \begin{table}
-	\begin{center}
+  \centering
   \label{tab:tableA}
-\caption{Optimized parameters yielding the highest average reflectance $\braket{R}$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs. (\ref{F1}) - (\ref{F3}))}
-		\resizebox{\textwidth}{!}{
-		\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-			\hline % <-- Toprule here
-			\textbf{Func-}&\multicolumn{3}{|c|}{\textbf{Parameters}} &\textbf{Periods}&\textbf{Thick-}&\textbf{OD}&\textbf{$\lambda_{0}$}&$\braket{R}$\\
-		\textbf{tion}&$\alpha$&$\beta$&A&$N_{p}$&\textbf{ness} ($\mu$m)& \textbf{width} ($\mu$m)&($\mu$m)&$\%$\\
+  \addtolength{\tabcolsep}{-2pt}
+    \begin{tabular}{rrrrrrrrr}
+      Class&$\alpha$&$\beta$&A&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
       \hline
-			$f_{1}$&0.24&---&---&222&86.1&0.30&1.150&89\\
-			$f_{2}$&0.37&1.06&---&102&35.9&0.22&1.110&88\\
-			\textcolor{red}{$f_{3}$}&\textcolor{red}{1.23}&\textcolor{red}{0.54}&\textcolor{red}{0.18}&\textcolor{red}{63}&\textcolor{red}{21.6}&\textcolor{red}{0.25}&\textcolor{red}{1.125}&\textcolor{red}{89}\\
       \hline
-			\textcolor{red}{$f_{1}$}&\textcolor{red}{1.20}&\textcolor{red}{---} &\textcolor{red}{---} & \textcolor{red}{90}&\textcolor{red}{60.4}&\textcolor{red}{2.15}&\textcolor{red}{1.925}&\textcolor{red}{92}\\
-			$f_{2}$&1.08&1.86&--- &105&61.7&2.00&2.000&89\\
-			$f_{3}$&1.01&1.95&0.20&102&62.3&2.05&1.975&90\\
+      $f_{1}$     &0.24    &---      &---     &222   &86.1    &300    &1150    &89\\
+      $f_{2}$     &0.37    &1.06     &---     &102   &35.9    &220    &1110    &88\\
+      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
       \hline
+      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
+      $f_{2}$     &1.08    &1.86     &---     &105   &61.7    &2000    &2000    &89\\
+      $f_{3}$     &1.01    &1.95     &0.20    &102   &62.3    &2050    &1975    &90\\
     \end{tabular}
-	}
-	\end{center}
+  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
+    reflectance $\braket{R}$ averaged over the spectral ranges
+    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
+    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
+    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
+    of the structure and the omnidirectional spectral
+    width and center (ODW and ODC). \notaL{Para el primer rango habría que
+      especificar $\lambda_{min}$ también.}}
 \end{table}
@@
 $f_{3}$ yields after optimization the highest $\braket{R}$ in the
-region $\mathcal R_1$ with the thinnest structure (see table
-\ref{tab:tableA}). Furthermore, this structure has a calculated OD gap
-\notaL{I'm unsure about the nomenclature ``gap''. I guess it is
-  theoretical, right?}
- \notaV{Podr\'{i}a utilizar el t\'{e}rmino "OD width" para referirme al ancho omnidireccional del espejo}
-of 250 nm centered at 1125 nm with a
-reflectance
-$R>0.90$, as shown in Fig. \ref{Fig1}(b). We
+region $\mathcal R_1$ and with the thinnest structure. Furthermore, this
+structure has an
+omnidirectional spectral band (ODB), defined as the region for which
+$R>0.90$ for all angles,
+\notaL{Se me ocurre ODW, omnidirectional spectral width, ODB band, ODC center. Si están de
+  acuerdo, habría que rotular de nuevo las figuras.}
+of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). \notaL{¿Por
+  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna
+  referencia que defina dicho criterio?} We
 synthesized a structure designated {\em sample $S_1$} corresponding
@@
 resulting structures have similar thicknesses and attain similar reflectance
-spectra, though the one with the smallest thickness and the maximum
-reflectance is that obtained from the family $f_{1}$. We
+spectra,\notaL{es correcto spectra aquí, o nos referimos al promedio?}
+though the one with the smallest thickness and the maximum $\braket{R}$
+is that obtained from the family $f_{1}$. We
 also synthesized the corresponding
@@
 calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
-This structure has a very wide region where $ R(\lambda, \theta)>
-0.90$, which goes from 850 to 3000 nm in an angular range
+This structure has a very wide region where $R(\lambda, \theta)>
+0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
 from $0^\circ$ to $70^\circ$. Thus, it has a
-quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm.
-The functions $f_i$ optimized for the region $\mathcal R_1$ are shown
+quasi-ODW of 2150 nm centered at 1925 nm.
+The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
 in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
-in Fig. \ref{Fig1}(c). The profiles $f_i$ are qualitatively
+in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
 similar. For example, for $\mathcal R_1$ the optimal photonic
@@
 structure.
-As in $\mathcal R_2$ the absorption of porous silicon is negligible,
-the periods are distributed quasi-evenly. \notaL{Sigo sin
-  entender. ¿La absorción del silicio poroso depende de la muestra?
-  ¿Qué significa quasi-evenly? Quité el 'due', pues era mala redacción}
-
+As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
+far from a linear profile.
 \begin{figure}
@@
     $\mathcal R_2$ (panel d). The dotted lines
-    delimit the area where $R> 90\%$ and the dashed lines
-    indicate the quasi-OD region. In the first region there is
-    an OD gap and in the second region there is a quasi OD
+    indicate the ODB and the dashed lines
+    indicate the quasi-ODB.
     gap.}
@@
 
-We measured the reflectance spectra of samples $S_1$ and $S_2$
-at various angles of incidence $\theta$. Due to
-experimental limitations, we restrict our results to the case of
-unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured
-reflectance corresponding to sample $S_1$ are compared from 350 to 1400 nm for different angles of
-incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
-$50^\circ$, and $60^\circ$). The spectra are qualitatively
+In Fig. \ref{Fig2}(a) we present the calculated and measured
+reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
+nm for different angles of
+incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
+$50^\circ$, and $60^\circ$. The spectra are qualitatively
 similar, and for $\lambda>700$ nm and $10^\circ < \theta <
@@
 spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
-check the OD gap. Nevertheless, our results allow us to conclude that
-the structure has a quasi-omni-directional
-bandgap (R$\left(\lambda,\theta \right)>0.90$) between 980 and
+check the ODB. Nevertheless, our results allow us to conclude that
+the structure has a quasi-ODB from 980 and
 1340 nm.
@@
         region where the reflectance is greater than  $0.90$,
-        corresponding to the quasi OD gap of the
+        corresponding to the quasi OD band of the
         structure. Inset: photograph of the synthesized structure.}
@@
 \cite{Negro2003,Vincent1993}. According to our results, this
-structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm
+structure has a wide quasi-ODW of 1800 nm
 centered at 1880 nm.
@@
   periods or sub-mirrors? Do you mean (2+j) nm, such as the sequence
-  700, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
-  $\lambda_{54}=700+2*53+54*55/2-1=2290$?} with 4 periods for
+  $\lambda_1=700$, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
+  $\lambda_{54}=700+2*53+54*55/2-1=2290$?}with 4 periods for
 each of the following periods.
@@
 \end{equation}
-where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
+where $K$ is Bloch's vector and $\bm M$ the transfer matrix of a single
 period of thickness $D$ \cite{Mochan1987, Mochan1988,
@@
 whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
-electromagnetic energy cannot propagate in the periodic system and we
-expect a high reflectance for a finite system made of a finite number
-of periods. This suggests the following design. We stack submirrors
+electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
+photonic band gap within which we
+expect a high reflectance, even for a finite system made of only a few periods. This suggests
+the following design strategy. We stack submirrors
 each made of a few periods of a periodic system such that its photonic band gap
@@
 angular range $400\text{nm}\le
-\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.
+\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$. \notaL{¿Valdría la pena
+  definir este overlap?}
 
@@
 \begin{table}[htbp]
-  \begin{center}
-    \caption{Total number $N_m$ of stacked submirrors, thickness $d$,
-      overlap between consecutive PBG and average reflectance
-      $\braket{R}$ for optimized structures designed with a
-      number $p$ of periods per submirror (first block) or a number $p$
-      of periods for those submirrors tuned to wavelengths
-      $\lambda_j\geq 800$nm (second block, see text), for different
-      values of $p$. The parameters corresponding to the best design
-      are typeset in bold.}
+  \centering
   \label{tab:table2}
-    \begin{tabular}{ccccc}
+  \begin{tabular}{rrrrr}
     $p$&$N_m$&$d (\mu\text{m})$&\% overlap&$\braket{R}$\\
@@
     10&13&45.4&56&95.3\\
-      \hline
   \end{tabular}
-  \end{center}
+  \caption{Total number $N_m$ of stacked submirrors, thickness $d$,
+    overlap between consecutive PBG and average reflectance
+    $\braket{R}$ for optimized structures designed with a
+    number $p$ of periods per submirror (first block) or a number $p$
+    of periods for those submirrors tuned to wavelengths
+    $\lambda_j\geq 800$nm (second block, see text), for different
+    values of $p$. The parameters corresponding to the best design
+    are typeset in bold.}
 \end{table}
@@
 
-Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
+Fig. \ref{Fig3}(a) reveals a quasi-OD
 mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
@@
 >70^\circ$ and long
-wavelengths the reflectance decreases and has oscillations, which are attributed to the
+wavelengths the reflectance decreases and has oscillations, which we attribute to the
 greater penetration of the electromagnetic field within the structure, as shown by
@@
 as a recently reported PS chirped structure \cite{Chavez2020}, which
-has the largest previously reported OD width.
+has the largest previously reported ODW.
 
-Finally, Table \ref{tab:table3} shows some porous silicon based OD
-mirrors designed to operate in the NIRy
-region and the width of the omnidirectional band gaps are compared
+Finally, Table \ref{tab:table3} shows data from some porous silicon based OD
+mirrors designed to operate in the NIR
+region and the width of the OD bands are compared
 with those of the structures
@@
 structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
-largest reported work until now in the NIR region \cite{Wu2021}.
+largest reported work until now in the NIR region \cite{Wu2021}. \notaL{Creo que podríamos
+  echarla más crema a los tacos, dado que una muestra llega hasta 950, como la de Estevez, pero
+  con un ancho mucho mayor, y las otras dos llegan más al azul que las demás muestras previas y
+  con mejores anchos de banda}
 
 \begin{table}
-  \begin{center}
-    \caption{Development of porous silicon based ODBMs for the NIR region.}
+  \centering
   \label{tab:table3}
-    \begin{tabular}{ccccc}
-      \hline % <-- Toprule here
-      \multicolumn{2}{c}{\textbf{Reference}}&\textbf{Year}&\textbf{ODBM range}&\textbf{ODBM width}\\
-                        & &(nm)&(nm)\\%&\textbf{ST-B}&\textbf{ST-C}\\
+  \begin{tabular}{rrrrr}
+    Reference&Year&Sample&ODB (nm)&ODW (nm)\\
     \hline
-      \multicolumn{2}{c}{Bruyant, et al. \cite{Bruyant2003}}& 2003 & 1100-1440 & 340 \\
-      \multicolumn{2}{c}{Xifre-P\'{e}rez, et al. \cite{Xifre2005}} & 2004 & 1297-1615 & 318\\
-      \multicolumn{2}{c}{Estevez, et al. \cite{Estevez2009}} & 2009 & 950-1456 & 506 \\
-      \multicolumn{2}{c}{Chavez, et al. \cite{Chavez2020}}& 2020 & 1000-2000 & 1000 \\
-      \multicolumn{2}{c}{Wu, et al. \cite{Wu2021}}&2021&1284-2605&1321 \\
     \hline
-                  &$S_1$&&980-1340&360 \\
-      This work   &$S_2$&2021&980-2780&1800\\
-                  &$S_3$&&950-2750&1800\\
+    Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&340\\
+    Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-    &1297-1615&318\\
+    Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456 &506\\
+    Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&1000\\
+    Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&1321\\
     \hline
+                                            &    &$S_1$&980-1340&360 \\
+    This work                               &2021&$S_2$&980-2780&1800\\
+                                            &    &$S_3$&950-2750&1800\\
   \end{tabular}
-  \end{center}
+  \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
+    previously published works (first block) and for the different samples studied here (second
+    block. We show the attained omnidirectional bands (ODB) and their widths (ODW).}
 \end{table}
@@
 carried out employing the transfer matrix method and we optimized the
-design parameters to maximize the average reflectance of the
-structures. We manufactured some of the optimized structures with
+design parameters to maximize the reflectance averaged over different spectral ranges and for
+all angles. We manufactured some of the optimized structures with
 porous silicon
 dielectric multilayers and compared their measured  optical properties
-to the results of calculations. For the
-chirping method, a couple of structures were fabricated, one with
-a thicknesses of 21.6 $\mu$m and another with a thickness of 60.4 $\mu$m,
-resulting in reflectivity q-OD bandwidthso of 360nm and 1800nm centered
-at 1160nm and 1925nm, respectively. For the stacked sub-structures
-method we obtained a 41.5$\mu$m thickness mirror with a q-OD
-bandwidth of
+to the results of calculations. We fabricated two chirped structures
+with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
+resulting in quasi omnidirectional mirrors with bandwidths of 360nm and 1800nm centered
+at 1160nm and 1925nm, respectively.\notaL{Quité acrónimos de las conclusiones}. We fabricated a
+stacked structures  with a thickness of 41.5$\mu$m resulting in a quasi omnidirectional mirror
+with a bandwidth of
 1800nm centered at 1850nm. Therefore, the second technique is found
@@
 improvement in the average
-reflectance. Additionally, the analysis techniques developed here can
+reflectance.\notaL{No me es clara la conclusión, pues cada muestra fue diseñada para distintas
+  regiones. ¿Es justo compararlas? Quizás sólo debamos decir que los resultados fueron muy
+  buenos para las tres muestras. Si alguien quisiera diseñar un espejo específico, ¿sabrías qué
+estrategia recomendarle para su diseño?}
+Additionally, the analysis techniques developed here can
 be used to optimize the reflectance for other refractive index contrasts

### 2021-01-24 PaperVictor.tex
Atendi observaciones

@@
 reported.\notaL{Es cierto?}\notaL{Quité los acrónimos del resumen}
+\notaV{S\'{i}, la estructura m\'{a}s reciente tiene un ODW de 1321 nm (compuesta por LHM) y la \'{u}ltima estructura de SP tiene un ODW de 1000 nm; las nuestras tienen un ODW de 1800 nm.}
 \end{abstract}
@@
 The optimizations were done employing the Minuit module  \cite{minuit}
-of the Perl Data Language (PDL) \notaL{cita}.
+of the Perl Data Language (PDL) \cite{PDL1997}. \notaL{cita} \notaV{Listo}
 
@@
 was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
-$\lambda_{\min}=850$nm and $\lambda_{\min}=3000$nm. \notaL{Any reason
-  for these choices? They seem arbitrary.}
+$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm. \notaL{Any reason
+  for these choices?
+They seem arbitrary.} \notaV{El objetivo de elegir la primer regi\'{o} era comparar la estructura optimizada con el espejo blanco obtenido por Ariza \cite{Ariza2012}.
+La segunda regi\'{o}n la eleg\'{i} porque es uno de los rangos m\'{a}ximos que puedo medir (200-3300) nm.
+En principio puedo optimizar en una regi\'{o}n m\'{a}s amplia, pero solo quedar\'{i}a en el c\'{a}lculo sin su complemento experimental.}
 %The
@@
 %its interface to the MINUIT \cite{minuit} minimization package.
-\notaL{Creo que ya habíamos mencionado esto}.
+\notaL{Creo que ya habíamos mencionado esto} \notaV{S\'{i}, oraci\'{o}n repetida}.
 The
@@
 are shown in Table \ref{tab:tableA}.
-\notaV {En caso de ser necesario: Results for other
-  pairs of porosities, $30/76 \% $ and $42/76 \%$, are included as
-  supplementary information.}
+
 \begin{table}
@@
   \addtolength{\tabcolsep}{-2pt}
-    \begin{tabular}{rrrrrrrrr}
-      Class&$\alpha$&$\beta$&A&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
+    \begin{tabular}{rrrrrrrrrr}
+      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
       \hline
       \hline
-      $f_{1}$     &0.24    &---      &---     &222   &86.1    &300    &1150    &89\\
-      $f_{2}$     &0.37    &1.06     &---     &102   &35.9    &220    &1110    &88\\
-      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
+      $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
+      $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
+      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
       \hline
-      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
-      $f_{2}$     &1.08    &1.86     &---     &105   &61.7    &2000    &2000    &89\\
-      $f_{3}$     &1.01    &1.95     &0.20    &102   &62.3    &2050    &1975    &90\\
+      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
+      $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
+      $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
     \end{tabular}
@@
     width and center (ODW and ODC). \notaL{Para el primer rango habría que
-      especificar $\lambda_{min}$ también.}}
+      especificar $\lambda _{min}$ también.} \notaV{Listo}}
 \end{table}
@@
 \notaL{Se me ocurre ODW, omnidirectional spectral width, ODB band, ODC center. Si están de
-  acuerdo, habría que rotular de nuevo las figuras.}
+  acuerdo, habría que rotular de nuevo las figuras.} \notaV{De acuerdo! Figuras modifocadas.}
 of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). \notaL{¿Por
-  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna
-  referencia que defina dicho criterio?} We
-synthesized a structure designated {\em sample $S_1$} corresponding
+  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna referencia que defina dicho criterio?} 
+\notaV{Alguna referencia que defina como tal este criterio, NO. 
+	Sin embargo, hay algunos autores que toman $R>90\%$ como punto 
+	de partida para describir sus sistemas multicapa 
+	\cite{Xu2018,Ahmed2014,Reiner2000}. Depende de los resultados 
+	que hayamos obtenido y qu\'{e} queramos vender}
+We synthesized a structure designated {\em sample $S_1$} corresponding
 to these results. For the region $\mathcal R_2$ the
-resulting structures have similar thicknesses and attain similar reflectance
-spectra,\notaL{es correcto spectra aquí, o nos referimos al promedio?}
+resulting structures have similar thicknesses and attain similar average reflectance,
+\notaL{es correcto spectra aquí, o nos referimos al promedio?} \notaV{Al promedio}
 though the one with the smallest thickness and the maximum $\braket{R}$
@@
         region where the reflectance is greater than  $0.90$,
-        corresponding to the quasi OD band of the
+        corresponding to the quasi ODB of the
         structure. Inset: photograph of the synthesized structure.}
@@
   changed to passive to avoid the fact that Agarwal did the stacking} the
-first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} tuned to
-$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to
+first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} \notaV{S\'{i}, as\'{i} lo propuso} tuned to
+$\lambda_{1}=700$ nm; the following $j-th$ sub-mirrors were tuned to
 wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
-- \lambda_{j}=2+j$ (with its suitable units)\notaL{This is still
-  wrong and/or I don't understand. What are these suitable units? Why
-  the mistery? $j$ numbers
-  periods or sub-mirrors? Do you mean (2+j) nm, such as the sequence
+- \lambda_{j}= \left(2+j \right)$ nm %(with its suitable units)
+\notaL{This is still
+  wrong and/or I don't understand. What are these suitable units? \notaV{units: nm} Why
+  the mistery? \notaV{No cre\'{i} que fuera tan relevante} $j$ numbers
+  periods or sub-mirrors? \notaV{$j-th$ sub-mirrors} Do you mean (2+j) nm, such as the sequence
   $\lambda_1=700$, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
-  $\lambda_{54}=700+2*53+54*55/2-1=2290$?}with 4 periods for
+  $\lambda_{54}=700+2*53+54*55/2-1=2290$?} 
+\notaV{$\lambda_1=700$, $\lambda_2=\lambda_{1}+2+1=703$, $\lambda_3=\lambda_{2}+2+2=704\ldots$
+$\lambda_{54}=\lambda_{53}+2+53= 700+2*53+53*54/2= 2237$.}
+with 4 periods for
 each of the following periods.
@@
 \begin{equation}
-	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
+	 \cos \left(KD \right) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
 \end{equation}
@@
 $\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
-4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para
-  cada subespejo?}
+4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para cada subespejo?}
+\notaV{De acuerdo a lo aprendido en las estructuras chirped, se 
+	requiere que las estructuras posean pocas bicapas en la 
+	regi\'{o} de alta absorci\'{o}n y pueden ir aumentando a 
+	medida que disminuye la absorci\'{o}n. Por eso se me hizo 
+	sensato proponer esa configuraci\'{o}n en la segunda 
+	estrategia de diseño. S\'{i}, si se podr\'{i}a optimizar $p$ 
+	para cada sub espejo; sin embargo, corremos el riesgo de 
+	obtener una estructura similar a la propuesta por 
+	Estrada-Weise \cite{DelRio2018}. Adem\'{a}s, los resultados 
+	aqu\'{i} mostrados ya no ser\'{i}an los adecuados.}
 In both designs, the degree of overlap of consecutive PBGs was
@@
   definir este overlap?}
+\notaV{No entend\'{i} esta observaci\'{o}n.}
 
@@
 
-Finally, Table \ref{tab:table3} shows data from some porous silicon based OD
-mirrors designed to operate in the NIR
-region and the width of the OD bands are compared
-with those of the structures
-analyzed in the present study. The table reveals that the porous silicon based
+Finally, Table \ref{tab:table3} shows data from some porous 
+silicon based OD mirrors designed to operate in the NIR
+region and the width of the OD bands are compared with those of 
+the structures analyzed in the present study. For example, the ODW 
+of the structure $S_1$ is 20 nm wider than that reported by Bruyant, 
+et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore, 
+the ODB of the structure $S_3$ begins at 950 nm like the one 
+synthesized by Estevez, et al. \cite{Estevez2009}; however, the width of S3 extends to 2750 
+nm. In other words, $S_3$ has ODW 3.55 times higher. Moreover, the 
+ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6 
+\% of the ODW of the S2 and S3 structures. Aditionally, the table 
+reveals that the porous silicon based
 structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
@@
   con un ancho mucho mayor, y las otras dos llegan más al azul que las demás muestras previas y
-  con mejores anchos de banda}
+  con mejores anchos de banda} \notaV{Agregue tres oraciones m\'{a}s}
 
@@
 resulting in quasi omnidirectional mirrors with bandwidths of 360nm and 1800nm centered
-at 1160nm and 1925nm, respectively.\notaL{Quité acrónimos de las conclusiones}. We fabricated a
+at 1160nm and 1925nm, respectively.\notaL{Quité acrónimos de las conclusiones} \notaV{Perfecto}. We fabricated a
 stacked structures  with a thickness of 41.5$\mu$m resulting in a quasi omnidirectional mirror
@@
   regiones. ¿Es justo compararlas? Quizás sólo debamos decir que los resultados fueron muy
-  buenos para las tres muestras. Si alguien quisiera diseñar un espejo específico, ¿sabrías qué
+  buenos para las tres muestras. \notaV{De Acuerdo} Si alguien quisiera diseñar un espejo específico, ¿sabrías qué
 estrategia recomendarle para su diseño?}
+\notaV{Si el lector no tiene experiencia acerca de los materiales, 
+	se aconsejar\'{i}a usar estructuras chirped. Por otra parte, al observar el mapeo de los valores de las trazas de sub 
+	espejos, se podr\'{i}a diseñar la estructura adecuada a las 
+	necesidades.}
 Additionally, the analysis techniques developed here can

### 2021-01-25 PaperVictor.tex
Revise Victors version

@@
 omnidirectional spectral width larger than those previously
-reported.\notaL{Es cierto?}\notaL{Quité los acrónimos del resumen}
-\notaV{S\'{i}, la estructura m\'{a}s reciente tiene un ODW de 1321 nm (compuesta por LHM) y la \'{u}ltima estructura de SP tiene un ODW de 1000 nm; las nuestras tienen un ODW de 1800 nm.}
+reported.
 \end{abstract}
@@
 The optimizations were done employing the Minuit module  \cite{minuit}
-of the Perl Data Language (PDL) \cite{PDL1997}. \notaL{cita} \notaV{Listo}
+of the Perl Data Language (PDL) \cite{PDL1997}.
 
@@
 $\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm. \notaL{Any reason
-  for these choices?
-They seem arbitrary.} \notaV{El objetivo de elegir la primer regi\'{o} era comparar la estructura optimizada con el espejo blanco obtenido por Ariza \cite{Ariza2012}.
-La segunda regi\'{o}n la eleg\'{i} porque es uno de los rangos m\'{a}ximos que puedo medir (200-3300) nm.
-En principio puedo optimizar en una regi\'{o}n m\'{a}s amplia, pero solo quedar\'{i}a en el c\'{a}lculo sin su complemento experimental.}
-%The
-%calculations were carried out using the Perl Data Language (PDL)
-%\notaL{cita} and
-%its interface to the MINUIT \cite{minuit} minimization package.
-\notaL{Creo que ya habíamos mencionado esto} \notaV{S\'{i}, oraci\'{o}n repetida}.
+  for these choices? They seem arbitrary.} \notaV{El objetivo de
+  elegir la primer regi\'{o} era comparar la estructura optimizada con
+  el espejo blanco obtenido por Ariza \cite{Ariza2012}. La segunda
+  regi\'{o}n la eleg\'{i} porque es uno de los rangos m\'{a}ximos que
+  puedo medir (200-3300) nm. En principio puedo optimizar en una
+  regi\'{o}n m\'{a}s amplia, pero solo quedar\'{i}a en el c\'{a}lculo
+  sin su complemento experimental.} \notaL{Creo que alguna explicación
+  sencilla merece el lector.}
+
 The
@@
     of the structure and the omnidirectional spectral
-    width and center (ODW and ODC). \notaL{Para el primer rango habría que
-      especificar $\lambda _{min}$ también.} \notaV{Listo}}
+    width and center (ODW and ODC).}
 \end{table}
@@
 $R>0.90$ for all angles,
-\notaL{Se me ocurre ODW, omnidirectional spectral width, ODB band, ODC center. Si están de
-  acuerdo, habría que rotular de nuevo las figuras.} \notaV{De acuerdo! Figuras modifocadas.}
 of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). \notaL{¿Por
-  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna referencia que defina dicho criterio?} 
+  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna
+  referencia que defina dicho criterio?}
 \notaV{Alguna referencia que defina como tal este criterio, NO.
@@
 	\cite{Xu2018,Ahmed2014,Reiner2000}. Depende de los resultados
-	que hayamos obtenido y qu\'{e} queramos vender}
+	que hayamos obtenido y qu\'{e} queramos vender} \notaL{¿Sería
+        correcto citar a Xu, Ahmed y Reiner entonces, para apuntalar
+        nuestra definición?}
 We synthesized a structure designated {\em sample $S_1$} corresponding
@@
 resulting structures have similar thicknesses and attain similar average reflectance,
-\notaL{es correcto spectra aquí, o nos referimos al promedio?} \notaV{Al promedio}
 though the one with the smallest thickness and the maximum $\braket{R}$
@@
   changed to passive to avoid the fact that Agarwal did the stacking} the
-first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} \notaV{S\'{i}, as\'{i} lo propuso} tuned to
+first sub-mirror consisted of 2.5 periods tuned to
 $\lambda_{1}=700$ nm; the following $j-th$ sub-mirrors were tuned to
 wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
-- \lambda_{j}= \left(2+j \right)$ nm %(with its suitable units)
-\notaL{This is still
-  wrong and/or I don't understand. What are these suitable units? \notaV{units: nm} Why
-  the mistery? \notaV{No cre\'{i} que fuera tan relevante} $j$ numbers
-  periods or sub-mirrors? \notaV{$j-th$ sub-mirrors} Do you mean (2+j) nm, such as the sequence
-  $\lambda_1=700$, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
-  $\lambda_{54}=700+2*53+54*55/2-1=2290$?} 
-\notaV{$\lambda_1=700$, $\lambda_2=\lambda_{1}+2+1=703$, $\lambda_3=\lambda_{2}+2+2=704\ldots$
-$\lambda_{54}=\lambda_{53}+2+53= 700+2*53+53*54/2= 2237$.}
+= \lambda_{j}+ \left(2+j \right)$ nm
 with 4 periods for
@@
 \begin{equation}
-	 \cos \left(KD \right) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
+	 \cos KD = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
 \end{equation}
@@
 $\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
-4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para cada subespejo?}
-\notaV{De acuerdo a lo aprendido en las estructuras chirped, se 
-	requiere que las estructuras posean pocas bicapas en la 
-	regi\'{o} de alta absorci\'{o}n y pueden ir aumentando a 
-	medida que disminuye la absorci\'{o}n. Por eso se me hizo 
-	sensato proponer esa configuraci\'{o}n en la segunda 
-	estrategia de diseño. S\'{i}, si se podr\'{i}a optimizar $p$ 
-	para cada sub espejo; sin embargo, corremos el riesgo de 
-	obtener una estructura similar a la propuesta por 
-	Estrada-Weise \cite{DelRio2018}. Adem\'{a}s, los resultados 
-	aqu\'{i} mostrados ya no ser\'{i}an los adecuados.}
-In both designs, the degree of overlap of consecutive PBGs was
+4 and 10. In both designs, the degree of overlap of consecutive PBGs was
 taken as the parameter to be optimized in order to maximize
@@
 \notaV{No entend\'{i} esta observaci\'{o}n.}
+\notaL{En el texto no se aclara como defines el porcentaje de traslape
+  de dos bandas. Valdría la pena definirlo para que el lector entiende
+  qué significan los números en la tabla. Para mí no es obvio. Tienes
+  el ancho de una banda, el ancho de la otra y el ancho de la región
+  en que se traslapan. ¿Cómo combinas dichos números para producir un
+  porcentaje de overlap?}
 
@@
 silicon based OD mirrors designed to operate in the NIR
-region and the width of the OD bands are compared with those of 
-the structures analyzed in the present study. For example, the ODW 
-of the structure $S_1$ is 20 nm wider than that reported by Bruyant, 
+region and their of the ODB's are compared with those of
+the structures analyzed in the present study. The ODW
+of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
 et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
 the ODB of the structure $S_3$ begins at 950 nm like the one
-synthesized by Estevez, et al. \cite{Estevez2009}; however, the width of S3 extends to 2750 
-nm. In other words, $S_3$ has ODW 3.55 times higher. Moreover, the 
+synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
+nm. In other words, $S_3$ has an ODW 3.55 times higher. Moreover, the
 ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
-\% of the ODW of the S2 and S3 structures. Aditionally, the table 
+\% of the ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
 reveals that the porous silicon based
 structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
-largest reported work until now in the NIR region \cite{Wu2021}. \notaL{Creo que podríamos
-  echarla más crema a los tacos, dado que una muestra llega hasta 950, como la de Estevez, pero
-  con un ancho mucho mayor, y las otras dos llegan más al azul que las demás muestras previas y
-  con mejores anchos de banda} \notaV{Agregue tres oraciones m\'{a}s}
+largest reported work until now in the NIR region \cite{Wu2021}.
 
@@
 resulting in quasi omnidirectional mirrors with bandwidths of 360nm and 1800nm centered
-at 1160nm and 1925nm, respectively.\notaL{Quité acrónimos de las conclusiones} \notaV{Perfecto}. We fabricated a
+at 1160nm and 1925nm, respectively. We fabricated a
 stacked structures  with a thickness of 41.5$\mu$m resulting in a quasi omnidirectional mirror
@@
 	espejos, se podr\'{i}a diseñar la estructura adecuada a las
-	necesidades.}
+	necesidades.} \notaL{Falta meterlo entonces a las conclusiones.}
 Additionally, the analysis techniques developed here can

### 2021-01-28 PaperVictor.tex
Atendi 4 observaciones

@@
 \author[4]{D. Ariza-Flores}
-\author[3]{Hector P\'{e}rez-Aguilar}
+\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
 \author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
@@
 sub-mirrors tuned to different wavelengths, chosen so that their
-spectral ranges overlap. For each submirror, the spectral range was
+spectral ranges overlap. For each sub-mirror, the spectral range was
 obtained from the dispersion relation of a corresponding periodic
@@
 \begin{equation}
-\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
+\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
 \end{equation}%
@@
 was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
-$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm. \notaL{Any reason
-  for these choices? They seem arbitrary.} \notaV{El objetivo de
-  elegir la primer regi\'{o} era comparar la estructura optimizada con
-  el espejo blanco obtenido por Ariza \cite{Ariza2012}. La segunda
-  regi\'{o}n la eleg\'{i} porque es uno de los rangos m\'{a}ximos que
-  puedo medir (200-3300) nm. En principio puedo optimizar en una
-  regi\'{o}n m\'{a}s amplia, pero solo quedar\'{i}a en el c\'{a}lculo
-  sin su complemento experimental.} \notaL{Creo que alguna explicación
-  sencilla merece el lector.}
-
+$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm. 
+\notaL{Any reason
+	for these choices? They seem arbitrary.} \notaL{Creo que alguna 
+	explicación  sencilla merece el lector.} 
+\notaV{Agregue:  }
+Approximately $90\%$ of the solar radiation that reaches the 
+earth's surface is contained in the spectral region of 350 to 1400 
+nm ($\mathcal R_1$), while in ($\mathcal R_2$) it can be up 
+to $98\%$ of terrestrial solar radiation \cite{Bird1983}. A direct 
+application of the optimized structures in these regions is solar 
+reflectors.
 The
@@
 \end{table}
-
-The function
-$f_{3}$ yields after optimization the highest $\braket{R}$ in the
-region $\mathcal R_1$ and with the thinnest structure. Furthermore, this
-structure has an
-omnidirectional spectral band (ODB), defined as the region for which
-$R>0.90$ for all angles,
-of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). \notaL{¿Por
-  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna
-  referencia que defina dicho criterio?}
-\notaV{Alguna referencia que defina como tal este criterio, NO.
-	Sin embargo, hay algunos autores que toman $R>90\%$ como punto
-	de partida para describir sus sistemas multicapa
-	\cite{Xu2018,Ahmed2014,Reiner2000}. Depende de los resultados
-	que hayamos obtenido y qu\'{e} queramos vender} \notaL{¿Sería
+\notaL{¿Sería
 	correcto citar a Xu, Ahmed y Reiner entonces, para apuntalar
 	nuestra definición?}
+\notaV{Agregue:   }
+Various photonic structures have been obtained with $R>90\%$ 
+\cite{Xu2018,Ahmed2014,Reiner2000}, so we also report 
+omnidirectional spectra band (ODB) with $R>90\%$ for all angles.
+The function $f_{3}$ yields after optimization the highest 
+$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest 
+structure. Furthermore, this
+structure has an ODB of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). 
 We synthesized a structure designated {\em sample $S_1$} corresponding
@@
     indicate the ODB and the dashed lines
-    indicate the quasi-ODB.
-    gap.}
+    indicate the quasi-ODB.}
 \end{figure}
@@
 first sub-mirror consisted of 2.5 periods tuned to
-$\lambda_{1}=700$ nm; the following $j-th$ sub-mirrors were tuned to
+$\lambda_{1}=700$ nm; the following $j$-th sub-mirrors were tuned to
 wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
@@
 expect a high reflectance, even for a finite system made of only a few periods. This suggests
-the following design strategy. We stack submirrors
+the following design strategy. We stack sub-mirrors
 each made of a few periods of a periodic system such that its photonic band gap
 (PBG) overlaps the PBG of the previous and that of the next
-submirror. The number of periods of each sub-mirror is an
+sub-mirror. The number of periods of each sub-mirror is an
 important parameter. If it is too small, the sub-mirror would be
@@
 resulting structure would be too thick. This is particularly important
-for submirrors tuned to shorter wavelengths, for which there is some
+for sub-mirrors tuned to shorter wavelengths, for which there is some
 absorption. We followed thus two design
@@
 number $p$ of periods. In the second, a different number of periods was
-assigned to each submirror according to the center of its PBG: we chose
-a single period for those submirrors $j$ tuned to
+assigned to each sub-mirror according to the center of its PBG: we chose
+a single period for those sub-mirrors $j$ tuned to
 $\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
@@
 the reflectance $\braket{R}$ averaged within the spectral and
-angular range $400\text{nm}\le
-\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$. \notaL{¿Valdría la pena
+angular range $400\text{ nm}\le
+\lambda\le 3000\text{ nm}$ and for $0^\circ\le\theta\le90^\circ$.
+\notaV{Agregue:   }
+We define the percentage of overlap as the portion of the PBG of the $j$-th mirror that has been covered by the PBG of the $(j + 1)$-th mirror.
+ \notaL{¿Valdría la pena
   definir este overlap?}
@@
   \end{tabular}
-  \caption{Total number $N_m$ of stacked submirrors, thickness $d$,
+  \caption{Total number $N_m$ of stacked sub-mirrors, thickness $d$,
     overlap between consecutive PBG and average reflectance
     $\braket{R}$ for optimized structures designed with a
-    number $p$ of periods per submirror (first block) or a number $p$
-    of periods for those submirrors tuned to wavelengths
-    $\lambda_j\geq 800$nm (second block, see text), for different
+    number $p$ of periods per sub-mirror (first block) or a number $p$
+    of periods for those sub-mirrors tuned to wavelengths
+    $\lambda_j\geq 800$ nm (second block, see text), for different
     values of $p$. The parameters corresponding to the best design
@@
 with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
-resulting in quasi omnidirectional mirrors with bandwidths of 360nm and 1800nm centered
-at 1160nm and 1925nm, respectively. We fabricated a
-stacked structures  with a thickness of 41.5$\mu$m resulting in a quasi omnidirectional mirror
-with a bandwidth of
-1800nm centered at 1850nm. Therefore, the second technique is found
-to be better as it results in thiner structures with a noticeable
-improvement in the average
-reflectance.\notaL{No me es clara la conclusión, pues cada muestra fue diseñada para distintas
+resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm centered
+at 1160 nm and 1925 nm, respectively. We fabricated a
+stacked structures  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
+with a bandwidth of 1800 nm centered at 1850 nm. 
+\notaV{Agregue:    } Thus, the results we have shown are very good for all three structures.
+%Therefore, the second technique is found to be better as it results in thiner structures with a noticeable improvement in the average reflectance.
+\notaL{No me es clara la conclusión, pues cada muestra fue diseñada para distintas
   regiones. ¿Es justo compararlas? Quizás sólo debamos decir que los resultados fueron muy
@@
 	necesidades.} \notaL{Falta meterlo entonces a las conclusiones.}
+\notaV{Agregue:   }
+Furthermore, if someone without experience wants to obtain an 
+optimized photonic structure, we recommend using the chirped type 
+structures. There are cases in which it is suggested to use 
+sub-mirror stacking, for example, when the absorption of the 
+materials is negligible.
 Additionally, the analysis techniques developed here can

### 2021-02-04 PaperVictor.tex
Small corrections.

@@
 \end{abstract}
-
+\notaL{No sé si Vivechna quiera añadir al ICF y mencionar su estancia
+  en los agrads.}
 \section{Introduction}
@@
 Approximately $90\%$ of the solar radiation that reaches the
-earth's surface is contained in the spectral region of 350 to 1400 
-nm ($\mathcal R_1$), while in ($\mathcal R_2$) it can be up 
-to $98\%$ of terrestrial solar radiation \cite{Bird1983}. A direct 
+earth's surface is contained in the spectral region
+$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \notaL{¿qué es
+  terrestrial solar? terrestrial solar radiation} \cite{Bird1983}. A direct
 application of the optimized structures in these regions is solar
-reflectors.
+reflectors. \notaL{¿Pero por qué en un caso dejasta $\lambda_{\min}$
+  fijo y en el otro caso no? Sería bueno que el lector entienda todas
+  las decisiones que sean fáciles de explicar}
 The
@@
 \notaV{Agregue:   }
-Various photonic structures have been obtained with $R>90\%$ 
-\cite{Xu2018,Ahmed2014,Reiner2000}, so we also report 
-omnidirectional spectra band (ODB) with $R>90\%$ for all angles.
+Various works use $R>90\%$ as a criterium for defining
+omnidirectional band, and
+
 The function $f_{3}$ yields after optimization the highest
@@
 structure. Furthermore, this
-structure has an ODB of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). 
+structure has an omnidirectional band (ODB) of width (ODW) 250 nm
+centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
+photonic structures have been reported with
+omnidirectional bands (ODB's) \cite{Xu2018,Ahmed2014,Reiner2000} defined
+through the criterium $R>90\%$ which we adopt here.
 We synthesized a structure designated {\em sample $S_1$} corresponding
@@
 \notaV{Agregue:   }
-We define the percentage of overlap as the portion of the PBG of the $j$-th mirror that has been covered by the PBG of the $(j + 1)$-th mirror.
- \notaL{¿Valdría la pena
-  definir este overlap?}
-\notaV{No entend\'{i} esta observaci\'{o}n.}
-\notaL{En el texto no se aclara como defines el porcentaje de traslape
-  de dos bandas. Valdría la pena definirlo para que el lector entiende
-  qué significan los números en la tabla. Para mí no es obvio. Tienes
-  el ancho de una banda, el ancho de la otra y el ancho de la región
-  en que se traslapan. ¿Cómo combinas dichos números para producir un
-  porcentaje de overlap?}
+We define the percentage of overlap in terms of the portion of the PBG of the
+$j$-th mirror that lies within the PBG of the $(j + 1)$-th
+mirror.
 
@@
 at 1160 nm and 1925 nm, respectively. We fabricated a
-stacked structures  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
+stacked structure  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
 with a bandwidth of 1800 nm centered at 1850 nm.
-\notaV{Agregue:    } Thus, the results we have shown are very good for all three structures.
-%Therefore, the second technique is found to be better as it results in thiner structures with a noticeable improvement in the average reflectance.
-\notaL{No me es clara la conclusión, pues cada muestra fue diseñada para distintas
-  regiones. ¿Es justo compararlas? Quizás sólo debamos decir que los resultados fueron muy
-  buenos para las tres muestras. \notaV{De Acuerdo} Si alguien quisiera diseñar un espejo específico, ¿sabrías qué
-estrategia recomendarle para su diseño?}
-\notaV{Si el lector no tiene experiencia acerca de los materiales,
-	se aconsejar\'{i}a usar estructuras chirped. Por otra parte, al observar el mapeo de los valores de las trazas de sub
-	espejos, se podr\'{i}a diseñar la estructura adecuada a las
-	necesidades.} \notaL{Falta meterlo entonces a las conclusiones.}
-\notaV{Agregue:   }
+\notaV{Agregue:    } Thus, our techniques allowed us to obtain very
+good relatively thin quasi omnidirectional mirrors with wide bands
+over different wavelength ranges.
+\notaL{Me sospecho que es un poco improvisada esta respuesta, pues el
+  resultado depende de la región espectral, contrastes, etc. Entiendo
+  que estás contestando mi pregunta previa, pero desmerece las
+  conclusiones. El lector sin experiencia se quedará en las mismas,
+  además de ofendido de que te refieras en el texto a ellos directamente:
 Furthermore, if someone without experience wants to obtain an
@@
 sub-mirror stacking, for example, when the absorption of the
-materials is negligible.
-Additionally, the analysis techniques developed here can
-be used to optimize the reflectance for other refractive index contrasts
-in PS multilayers or in different systems with other types of
+materials is negligible.}
+Our analysis techniques can
+be used for the optimization of the reflectance multilayered PS systems with
+different refractive index contrasts or for systems with other types of
 materials. Such proposed structures could be used as mirrors for solar

### 2021-02-04 PaperVictor.tex
Revise Victor's version

@@
 \usepackage{bm}
-\usepackage{showkeys}
+%\usepackage{showkeys}
 \usepackage{ragged2e}
@@
 region. We design, fabricate and characterize
-some of the optimized omnidirectional structures with less
-than 100 pairs of layers. We obtained a structure that has the an
-omnidirectional spectral width larger than those previously
+some of the optimized omnidirectional mirrors with less
+than 100 pairs of layers. We obtained structures with a wider
+omnidirectional spectral region than those previously
 reported.
@@
 Photons entering a PC interact with its periodically varying dielectric constant and
-are consequently organized into photonic bands. In analogy to electrons in a
-crystal, their propagation is forbidden if their energy lies
+their energies are consequently organized into photonic bands. In
+analogy to electronic bands withiny a
+crystal, propagation is forbidden if the energy lies
 within certain regions known as photonic band gaps (PBG's). Thus, the
@@
 On the other hand, different fabrication techniques have been used to
-obtain omnidirectional (OD) mirrors that operate on the visible and/or
+obtain omnidirectional mirrors (ODM) that operate on the visible and/or
 near infrared (Vis-NIR) range of the electromagnetic spectrum. For
@@
  TiO$_{2}$/SiO$_{2}$  layers with
-an OD band of about 70 nm in the NIR range, employing a sol-gel deposition
+an omnidirectional band (ODB) of about 70 nm in the NIR range, employing a sol-gel deposition
 method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
@@
 GaAs/Al$_{2}$O$_{3}$ by selective oxidation of the AlAs
-layers, to obtain an OD with a band from 710 to 950 nm.
+layers, to obtain an ODB from 710 to 950 nm.
 On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
 coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
-polyamide-imide polymer, deposited by thermal evaporation and spin-casting
+polyamide-imide deposited by thermal evaporation and spin-casting
 respectively, to obtain a 150 nm wide omnidirectional band centered at
 1750 nm. Furthermore, Jena et al. \cite{Jena2019},
-used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
-_{2}$ layers) and radio frequen cy magnetron sputtering (for SiO$_{2}$
-layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
+used sequential asymmetric bipolar pulsed DC magnetron sputtering for TiO$%
+_{2}$ layers and radio frequency magnetron sputtering for SiO$_{2}$
+layers to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an ODB from
 592 to 668 nm. However, these techniques are expensive and they
-require sophisticated equipment and long fabrication times. Use of PS
+require sophisticated equipment and long fabrication times. Use of
+porous silicon (PS)
 is an attractive alternative, since it can be easily manufactured by
@@
 time during the electrochemical reaction, it is possible to obtain
-multilayered structures allowing for the fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
+multilayered structures allowing for the fabrication ODM's \cite{Xifre2015,Pavesi2000}.
 Although optical filters \cite{Estevez2009,Ariza2014} are the most common
@@
 increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
-PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
+PS based dielectric optical filters, quasi-ODM's and ODM's have been extensively studied in different
 regions of the electromagnetic spectrum, such as the ultraviolet (UV)
-\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} region.
+\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} regions.
 However, to obtain the desirable high index of refraction
@@
 layers were obtained through the Bruggeman's effective medium theory, which
-has been reported to adequately reproduce the PS optical parameters
+has been reported to adequately reproduce the  optical parameters of PS
 \cite{Giusseppe2011,Pap2006,Estrada2018}.
@@
 with corresponding porosities of 51\% and 76\%, respectively.
-These porosities were obtained through previously obtained calibration
+These porosities were determined through previously obtained calibration
 curves using a gravimetric technique \cite{Pap2006}. The
@@
 values of $\theta _{i}$ were constrained by the angular range of the
-equipment accessory URA.
+URA.
 
@@
 \begin{equation}
-\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
+\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
 \end{equation}%
+\notaL{Quité el -1 en el numerador pues antes pusimos que j empezaba
+  en 0}
 where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
 maximum {\em design} wavelengths respectively, $N_p$ is the number of
-periods  in the structure and $f(\xi)$ is a smooth function that
+periods  in the structure, and $f(\xi)$ is a smooth function that
 goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
@@
 The
-optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
+optimized parameters corresponding to the choice $p_l=0.51$ and
+$p_h=0.76$ for the low and high porosities
 are shown in Table \ref{tab:tableA}.
@@
 \end{table}
-\notaL{¿Sería
-	correcto citar a Xu, Ahmed y Reiner entonces, para apuntalar
-	nuestra definición?}
-\notaV{Agregue:   }
-Various works use $R>90\%$ as a criterium for defining
-omnidirectional band, and
 
@@
 structure. Furthermore, this
-structure has an omnidirectional band (ODB) of width (ODW) 250 nm
+structure has an omnidirectional width (ODW) of 250 nm
 centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
 photonic structures have been reported with
-omnidirectional bands (ODB's) \cite{Xu2018,Ahmed2014,Reiner2000} defined
-through the criterium $R>90\%$ which we adopt here.
+ODB's \cite{Xu2018,Ahmed2014,Reiner2000} defined as those spectral regions for
+which $R>90\%$ for all angles. Here we we adopt the same criterium.
 We synthesized a structure designated {\em sample $S_1$} corresponding
@@
   \end{center}
-  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
+  \caption{Profiles of the functions $f_n(\xi_j)$ \notaL{¿No sería
+      mejor rotular el eje horizontal de (a) y (c) como $\xi$ y que
+      vaya de 0 a 1? Si no, recuerda que tomamos $j$ va de 0 a $N_p-1$} optimized for
     the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
@@
 For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic
-structure in which 54 sub-mirrors were stacked as follows:\notaL{I
-  changed to passive to avoid the fact that Agarwal did the stacking} the
+structure in which 54 sub-mirrors were stacked as follows: the
 first sub-mirror consisted of 2.5 periods tuned to
@@
 \lambda\le 3000\text{ nm}$ and for $0^\circ\le\theta\le90^\circ$.
-\notaV{Agregue:   }
 We define the percentage of overlap in terms of the portion of the PBG of the
@@
 
-Fig. \ref{Fig3}(a) reveals a quasi-OD
-mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
+Fig. \ref{Fig3}(a) reveals a quasi-ODM
+in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
 $60^\circ$. It is also observed that at incidence angles $\theta
@@
 Finally, Table \ref{tab:table3} shows data from some porous
-silicon based OD mirrors designed to operate in the NIR
+silicon based ODM designed to operate in the NIR
 region and their of the ODB's are compared with those of
@@
 with a bandwidth of 1800 nm centered at 1850 nm.
-\notaV{Agregue:    } Thus, our techniques allowed us to obtain very
+Thus, our techniques allowed us to obtain very
 good relatively thin quasi omnidirectional mirrors with wide bands
 over different wavelength ranges.
-\notaL{Me sospecho que es un poco improvisada esta respuesta, pues el
+\notaL{Me sospecho que lo que sigue era un poco improvisada esta respuesta, pues el
   resultado depende de la región espectral, contrastes, etc. Entiendo
-  que estás contestando mi pregunta previa, pero desmerece las
+  que estás contestando literalmente mi pregunta previa, pero desmerece las
   conclusiones. El lector sin experiencia se quedará en las mismas,
-  además de ofendido de que te refieras en el texto a ellos directamente:
+  además de ofendido de que te refieras en el texto a ellos
+  directamente. Mejor quitémoslo:
 Furthermore, if someone without experience wants to obtain an
@@
 Michoacana de San Nicol\'{a}s de Hidalgo.
-%\end{acknowledgments}
+\notaL{Quizás Vivechna quiera mencionar al ICF. Quizás Victor también,
+  dado que puso este artículo en su reporte sobre su estancia en el icf.}
 

### 2021-02-18 PaperVictor.tex
Version aprovada por Dra. Vivechana

@@
 % !TeX spellcheck = en_US
-\documentclass{article}
-\usepackage{amsmath}
+\documentclass[a4paper,fleqn]{cas-sc}
+\usepackage[numbers]{natbib}
+
+%%%Author macros
+\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
+\tsc{WGM}
+\tsc{QE}
+\tsc{EP}
+\tsc{PMS}
+\tsc{BEC}
+\tsc{DE}
+%%%
 \usepackage{braket}
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{dcolumn}
 \usepackage{bm}
-%\usepackage{showkeys}
-\usepackage{ragged2e}
-\usepackage{cite}
-\newif{\ifmover}
-\newif{\ifquitar}
-\usepackage{authblk}
-\renewcommand{\Affilfont}{\small}
-\usepackage{xcolor}
-\newcommand{\notaL}[1]{{\color{orange}L: #1}}
-\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
-\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
-\definecolor{Addtext}{RGB}{0,0,255}
+
 \begin{document}
+	\let\WriteBookmarks\relax
+	\def\floatpagepagefraction{1}
+	\def\textpagefraction{.001}
+	\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
+	\shortauthors{V. Castillo-Gallardo et~al.}
 
-%\title{Thickness optimization in wide range quasi omnidirectional multilayer
-% structures}
-\title{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
-\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
-			victor1\_1@hotmail.com}}}
-\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
-\author[4]{D. Ariza-Flores}
-\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
-\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
-			mochan@fis.unam.mx}}}
-\author[1]{Vivechana Agarwal\thanks{email: {\tt
-			vagarwal@uaem.mx}}}
-\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
+	\title [mode = title]{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
+
+	\author[1,2,3]{V. Castillo-Gallardo}
+	\cormark[1]
+	\ead{ing.victorcg@gmail.com}
+	\credit{Conceptualization, Software $\&$ Investigation, synthesis $\&$ characterization, Writing}
+	\address[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
 		Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
@@
 		M\'{e}xico.}
-\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad
+
+	\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
+	\ead{fmatpuente@gmail.com}
+	\credit{Software $\&$ Investigation}
+	\address[2]{Instituto de Ciencias F\'{i}sicas, Universidad
 		Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
-Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
-\affil[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
+		Col. Chamilpa, 62210 Cuernavaca, Morelos, M\'{e}xico.}
+	\address[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
 		Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
 		Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
-\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
+
+	\author[4]{D. Ariza-Flores}
+	\ead{david1cool@gmail.com}
+	\credit{Investigation, Writing - review $\&$ editing}
+	\address[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
 		Potos\'{i}, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
 		S.L.P., 78210, M\'{e}xico.}
-%\date{{\small {\today}}}
-\maketitle
+
+	\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
+	\ead{hiperezag@yahoo.com}
+	\credit{Investigation and Supervision}
+
+	\author[2]{W. Luis Moch\'{a}n}
+	\ead{mochan@fis.unam.mx}
+	\credit{Conceptualization, Funding acquisition, Investigation, Supervision, Writing - review $\&$ editing}
+
+	\author[1]{V Agarwal}
+	\cormark[2]
+	\fnmark[1]
+	\ead{vagarwal@uaem.mx}
+	\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}
+
+	\cortext[cor1]{Corresponding author}
+	\cortext[cor2]{Principal corresponding author}
+	\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM}
 
@@
 	\end{abstract}
-\notaL{No sé si Vivechna quiera añadir al ICF y mencionar su estancia
-  en los agrads.}
+
+	\begin{graphicalabstract}
+		\includegraphics[width=\textwidth]{GraphicalAbstract.pdf}
+	\end{graphicalabstract}
+
+	\begin{highlights}
+		\item We design, optimize, fabricate and characterize wideband quasi-omnidirectional (q-OD) structures using different approaches.
+		\item Reflectance averaged over wide spectral range is optimized with simple parametrized functions (chirped) and by stacking Bragg submirrors.
+		\item Chirped structure with q-OD bandwidth of 1800 nm in the NIR have been demonstrated.
+		\item Stacking Bragg submirrors resulted in similar q-OD band with two third of total physical thickness.
+		\item Agreement between the theoretical and experimental results is obtained for porous silicon multilayers .
+		\item Proposed design techniques can be useful for obtaining OD dielectric mirrors with different materials in large spectral regions.
+	\end{highlights}
+
+	\begin{keywords}
+		Optimized reflectance \sep Omnidirectional structures \sep Chirped structures \sep Stacked Bragg mirror structures
+	\end{keywords}
+
+	\maketitle
+
 	\section{Introduction}
-
 	Photonic crystal (PC)-based structures have been extensively investigated due
@@
 	\end{equation}%
-\notaL{Quité el -1 en el numerador pues antes pusimos que j empezaba
-  en 0}
 	where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
@@
 	$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
-\notaL{Any reason
-	for these choices? They seem arbitrary.} \notaL{Creo que alguna
-	explicación  sencilla merece el lector.}
-\notaV{Agregue:  }
+	In the first case, we decided to optimize $\lambda_{min}$ to 
+	obtain the best design in the high absorption zone of the PS.
 	Approximately $90\%$ of the solar radiation that reaches the
 	earth's surface is contained in the spectral region
-$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \notaL{¿qué es
-  terrestrial solar? terrestrial solar radiation} \cite{Bird1983}. A direct
+	$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \cite{Bird1983}. 
+	A direct
 	application of the optimized structures in these regions is solar
-reflectors. \notaL{¿Pero por qué en un caso dejasta $\lambda_{\min}$
-  fijo y en el otro caso no? Sería bueno que el lector entienda todas
-  las decisiones que sean fáciles de explicar}
-The
+	reflectors. The
 	optimized parameters corresponding to the choice $p_l=0.51$ and
@@
 		\end{center}
-  \caption{Profiles of the functions $f_n(\xi_j)$ \notaL{¿No sería
-      mejor rotular el eje horizontal de (a) y (c) como $\xi$ y que
-      vaya de 0 a 1? Si no, recuerda que tomamos $j$ va de 0 a $N_p-1$} optimized for
+		\caption{Profiles of the functions $f_n(\xi_j)$ optimized for
 			the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
@@
 
-We have designed, fabricated and characterized highly reflective quasi
+	We have designed, optimized, fabricated and characterized highly reflective quasi
 	omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
-spectral range, optimized through two techniques: chirping and
-stacking of Bragg-type sub-structures. Numerical calculations were
+	spectral range. Two techniques, chirping (a continuous change in thicknesses) and
+	stacking of Bragg-type sub-structures, have been used to enhance the reflectance with minimum thickness for a given pair of refractive indices. Numerical calculations were
 	carried out employing the transfer matrix method and we optimized the
-design parameters to maximize the reflectance averaged over different spectral ranges and for
-all angles. We manufactured some of the optimized structures with
+	design parameters to obtain maximal reflectance averaged over different spectral ranges for
+	all angles. We fabricated some of the optimized structures with
 	porous silicon
 	dielectric multilayers and compared their measured  optical properties
-to the results of calculations. We fabricated two chirped structures
+	with the calculations. Two chirped structures 
 	with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
-resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm centered
-at 1160 nm and 1925 nm, respectively. We fabricated a
+	resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
+	at 1160 nm and 1925 nm respectively have been shown. In addition, we fabricated a
 	stacked structure  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
 	with a bandwidth of 1800 nm centered at 1850 nm.
-Thus, our techniques allowed us to obtain very
-good relatively thin quasi omnidirectional mirrors with wide bands
+	Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
 	over different wavelength ranges. 
-\notaL{Me sospecho que lo que sigue era un poco improvisada esta respuesta, pues el
-  resultado depende de la región espectral, contrastes, etc. Entiendo
-  que estás contestando literalmente mi pregunta previa, pero desmerece las
-  conclusiones. El lector sin experiencia se quedará en las mismas,
-  además de ofendido de que te refieras en el texto a ellos
-  directamente. Mejor quitémoslo:
-Furthermore, if someone without experience wants to obtain an
-optimized photonic structure, we recommend using the chirped type
-structures. There are cases in which it is suggested to use
-sub-mirror stacking, for example, when the absorption of the
-materials is negligible.}
 	Our analysis techniques can
@@
 	\section*{Acknowledgments}
-This work was partially supported by Consejo Nacional de Ciencia y
-Tecnolog\'{i}a through grant No. 256243, C\'{a}tedras
-Conacyt program 1577, and by DGAPA-PAPIIT UNAM under grant IN111119.
-HPA also express his gratitude to the Coordinaci\'{o}n
+
+	This project is supported by Consejo Nacional de Ciencia y
+	Tecnolog\'{i}a through grant No.A-S1-30393(VA), 256243 (DA), C\'{a}tedras
+	Conacyt program 1577 (DA), and by DGAPA-PAPIIT UNAM under grant IN111119 (LM).
+	VA acknowledges PRODEP (Sabbatical grant), and
+	is grateful to ICF where she spent the sabbatical year.
+	HPA also expresses his gratitude to the Coordinaci\'{o}n
 	de la Investigaci\'{o}n Cient\'{i}fica de la Universidad
-Michoacana de San Nicol\'{a}s de Hidalgo.
-\notaL{Quizás Vivechna quiera mencionar al ICF. Quizás Victor también,
-  dado que puso este artículo en su reporte sobre su estancia en el icf.}
+	Michoacana de San Nicol\'{a}s de Hidalgo. VCG is grateful to CIICAp 
+	and ICF where he did this work.
+
+	\printcredits
 
@@
 	\bibliography{Bibliografia}
+
 \end{document}

### 2021-02-18 SITemplete.tex
Sugerido por Dra. Vivechana

%% 
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}

%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}

\begin{document}
	\let\WriteBookmarks\relax
	\def\floatpagepagefraction{1}
	\def\textpagefraction{.001}
	\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
	\shortauthors{V. Castillo-Gallardo et~al.}

	\title [mode = title]{Suplementary information: Optimization of wide-band quasi-omnidirectional 1-D photonic structures}                      	
	\author[1,2,3]{V. Castillo-Gallardo}
	\cormark[1]
	\ead{ing.victorcg@gmail.com}
	\credit{Conceptualization, Software $\&$ Investigation, synthesis $\&$ characterization, Writing}
	\address[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
		Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
		Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
		M\'{e}xico.}

	\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
	\ead{fmatpuente@gmail.com}
	\credit{Software $\&$ Investigation}
	\address[2]{Instituto de Ciencias F\'{i}sicas, Universidad
		Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
		Col. Chamilpa, 62210 Cuernavaca, Morelos, M\'{e}xico.}
	\address[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
		Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
		Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}

	\author[4]{D. Ariza-Flores}
	\ead{david1cool@gmail.com}
	\credit{Investigation, Writing - review $\&$ editing}
	\address[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
		Potos\'{i}, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
		S.L.P., 78210, M\'{e}xico.}

	\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
	\ead{hiperezag@yahoo.com}
	\credit{Investigation and Supervision}

	\author[2]{W. Luis Moch\'{a}n}
	\cormark[2]
	\ead{mochan@fis.unam.mx}
	\credit{Conceptualization, Funding acquisition, Software $\&$ Investigation, Methodology, Supervision, Writing - review $\&$ editing}

	\author[1]{V Agarwal}
	\cormark[3]
	\fnmark[1]
	\ead{vagarwal@uaem.mx}
	\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}

	\cortext[cor1]{Corresponding author}
	\cortext[cor2]{Corresponding author}
	\cortext[cor3]{Principal corresponding author}
	\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM}

	\begin{abstract}
		Porous silicon is a very versatile material for developing optical
		devices based on multilayered structures, since high and low porosity layers
		can be synthesized by a simple electrochemical technique. In the present work, we design
		mirrors using \textit{chirped}-type structures and by stacking
		appropriately tuned sub-mirrors, and we optimize the design parameters
		to maximize the
		optical reflectance $\braket{R}$ averaged within a wide
		spectral range  covering the visible and near infrared regions, and
		within a wide angular range using low refractive index contrast. The chirped structures are found to be
		more suitable for the visible range,
		while stacked sub-mirrors are found to be better for the NIR
		region. We design, fabricate and characterize
		some of the optimized omnidirectional mirrors with less
		than 100 pairs of layers. We obtained structures with a wider
		omnidirectional spectral region (almost 1.4 times) and low refractive index contrast ratio than those previously
		reported.
	\end{abstract}

	\begin{keywords}
		Optimized reflectance \sep Omnidirectional structures \sep 
		Chirped structures \sep Stacked Bragg mirror structures
	\end{keywords}
\maketitle

\section{Chirped structure}
As expected, with an increase in the porosity contrast of the periods, the thickness 
of the structure decreases and the average reflectance increases. For 
example, one could have structures with a thickness of approx. 10 $\mu$m with the 
average reflectance greater than 90$\%$ for a wide spectral range, i.e., 350-1400nm, 
as shown in first block of table \ref{tab:tableA}. This block represents structures 
with porosities of $p_l=0.30$ and $p_h=0.76$. The second block manifiest the 
optimized parameters for structures with porosities of $p_l=0.42$ and $p_h=0.76$.

The mapping of the calculated reflectance of the structures designed with the 
optimized parameters is shown in Fig. \ref{Fig2}. Here it is observed that all of 
them have a ODB in the NIR region of the electromagnetic spectrum, i. e.,  
structures designed from functions $f_{1}$ and $f_{3}$ with a porosity contrast of 
$30/76\%$ have the highest ODB localized from 970 to 1370 nm, these are shown in 
panels (a) and (c).

\begin{table}[!ht]
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.55    &---      &---     &400&30   &9.2    
      &380    &1170    &92\\
      $f_{2}$     &0.22    &4.30     &---     &430&66   &17.8
      &280    &1190    &93\\
      $f_{3}$     & 1.15   &0.56   & 0.09    &400&30   & 10.5
      & 400& 1150& 91\\
      \hline
      $f_{1}$     & 0.35    & ---  & ---     &400&101    & 35.7
      &350& 1195& 91\\
      $f_{2}$     &0.45    &1.23     &0.5  &410  &105   &9.8     &280    &1170    &89\\
      $f_{3}$     &1.01    &0.50     &0.10  &350  &50   &16.4    &350    &1195    &90\\
    \end{tabular}
    %\caption{ Design parameters obtained after the optimization of functions for maximum average reflectance and minimum thickness}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral range $350-1400$ nm and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$. Structures have porosities of $p_l=0.30$ and $p_h=0.76$ (first block), and $p_l=0.42$ and $p_l=0.76$ (second block). We include the thickness $d$ of the structure, the omnidirectional spectral width (ODW) and the central wavelength (ODC).}
\end{table}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=\textwidth]
		{FigureS1.pdf}
	\end{center}
	\caption{Calculated reflectance of the structures designed with the optimized parameters of $f_{1}$ (left), $f_{2}$ (center) and $f_{3}$ (right) and with the porosity contrasts of $30/76\%$ (upper panels) and $42/76\%$ (lower panels). The dotted lines limit the area of the ODB.}
	\label{Fig2}
\end{figure}

\newpage

\section{Stacked sub-mirrors structure}

Additionally, the T$r|\text{M}|$ and R$(\lambda,\theta)$ were calculated for light with TE 
polarization and 45${{}^\circ}$ of incidence. In Fig. 3d it is shown that by using 
mirrors that have 6 periods and designed to reflect at wavelengths greater than 1000 
nm, they also reflect in a certain region of the visible spectrum. Then, to 
reinforce the reflection of the electromagnetic waves in the visible, it is enough 
to place a smaller number of periods. This is another reason for the increasing 
number of periods in the 400 to 800 nm region. 
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=\textwidth]
		{FigureS2.pdf}
	\end{center}
	\caption{Calculated transfer matrix trace and reflectance of individual mirrors using ((a) and (b)) one period  and ((c) and (d)) six periods, respectively. Each mirror was tuned to a wavelength between 400 and 3000 nm. The calculations were made in the visible and NIR region and at 45${{}^\circ}$ of incidence.}
	\label{Fig3}
\end{figure}
%\newpage

It is common to imagine that the stacking of the sub-mirrors in such a way that
the ODB of the second mirror begins at the edge of the ODB of the first mirror, the 
third ODB that begins at the edge of the ODB of the second mirror, and so on until 
the desired interval is completed. With this configuration, the reflectance 
decreases at each intersection of the two ODBs. For example, in Figs. \ref{Fig4}(a) 
and \ref{Fig4}(b) show the calculated R$(\lambda, \theta)$ for the structures formed 
by sub-mirrors that have one and six periods, respectively, using non-polarized 
light.  The R$_{Ave}(\lambda, \theta)$ was maximized through the percentage of 
overlap of the ODBs of two consecutive sub-mirrors.  
The 
calculated R$(\lambda, \theta)$ for the structures designed with 4 periods for each 
sub-mirror and using the pattern described in the main article are shown in Figs. 
\ref{Fig4}(c) and \ref{Fig4}(d) of this document, respectively. Here the overlap of 
the two consecutive ODBs was optimized, being $72\%$ for the first case and $78\%$ 
for the last. The calculations reveal the quasi-ODB of the structures.

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=\textwidth]
		{FigureS3.pdf}
	\end{center}
	\caption{Reflectance calculated for structures designed through the stacking of 
		sub-mirrors analyzing the overlap of the ODB and the number of periods in 
		each case. 
		Case I: there is no overlap of the ODBs and each 
		sub-mirror has (a) one period and (b) six periods. Case II: optimized 
		overlap of consecutive ODBs and (c) each submirror has 4 periods with 
		$72\%$ overlap, and (d) proposed arrangement in the main article with 6 
		periods for $\lambda>800$ nm and $78\%$ overlap. The quasi-OD region is indicated by the dotted lines.
	}
	\label{Fig4}
\end{figure}

\end{document}

### 2021-02-19 PaperVictor.tex
Minor changes, including removal of useless spaces

@@
 \usepackage[numbers]{natbib}
-
 %%%Author macros
@@
 
-	\author[1,2,3]{V. Castillo-Gallardo}
+\author[1,2,3]{V. Castillo-Gallardo}[orcid=0000-0002-8157-3534]
 \cormark[1]
 \ead{ing.victorcg@gmail.com}
-	\credit{Conceptualization, Software $\&$ Investigation, synthesis $\&$ characterization, Writing}
+\credit{Conceptualization, Software \& Investigation, synthesis \& characterization, Writing}
 \address[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
@@
 
-	\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
+\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}[orcid=0000-0003-3719-8535]
 \ead{fmatpuente@gmail.com}
-	\credit{Software $\&$ Investigation}
+\credit{Conceptualization, Software $\&$ Investigation}
 \address[2]{Instituto de Ciencias F\'{i}sicas, Universidad
@@
   Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
-		Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
+  Francisco J. M\'ugica S/N 58030, Morelia, Mich., M\'{e}xico.}
 
@@
 
-	\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
+\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}[orcid=0000-0002-8572-1485]
 \ead{hiperezag@yahoo.com}
@@
 
-	\author[2]{W. Luis Moch\'{a}n}
+\author[2]{W. Luis Moch\'{a}n}[orcid=0000-0003-0418-5375]
 \ead{mochan@fis.unam.mx}
@@
 
-	\author[1]{V Agarwal}
-	\cormark[2]
+\author[1]{V Agarwal}[orcid=0000-0003-2168-853X]
 \fnmark[1]
@@
 \cortext[cor1]{Corresponding author}
-	\cortext[cor2]{Principal corresponding author}
 \fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM}
@@
 \begin{highlights}
-		\item We design, optimize, fabricate and characterize wideband quasi-omnidirectional (q-OD) structures using different approaches.
-		\item Reflectance averaged over wide spectral range is optimized with simple parametrized functions (chirped) and by stacking Bragg submirrors.
-		\item Chirped structure with q-OD bandwidth of 1800 nm in the NIR have been demonstrated.
-		\item Stacking Bragg submirrors resulted in similar q-OD band with two third of total physical thickness.
-		\item Agreement between the theoretical and experimental results is obtained for porous silicon multilayers .
-		\item Proposed design techniques can be useful for obtaining OD dielectric mirrors with different materials in large spectral regions.
+\item We design, optimize, fabricate and characterize
+  wideband quasi-omnidirectional (q-OD) structures
+  using different approaches.
+\item Reflectance averaged over wide spectral range is
+  optimized with simple parametrized functions
+  (chirped) and by stacking Bragg submirrors.
+\item Chirped structure with q-OD bandwidth of 1800 nm
+  in the NIR have been demonstrated.
+\item Stacking Bragg submirrors resulted in similar
+  q-OD band with two third of total physical
+  thickness.
+\item Agreement between the theoretical and
+  experimental results is obtained for porous silicon
+  multilayers .
+\item Proposed design techniques can be useful for
+  obtaining OD dielectric mirrors with different
+  materials in large spectral regions.
 \end{highlights}
@@
 \begin{keywords}
-		Optimized reflectance \sep Omnidirectional structures \sep Chirped structures \sep Stacked Bragg mirror structures
+  Optimized reflectance \sep Omnidirectional structures \sep
+  Chirped structures \sep Stacked Bragg mirror structures
 \end{keywords}
@@
 \section{Introduction}
+
 Photonic crystal (PC)-based structures have been extensively investigated due

### 2021-02-19 PaperVictor.tex
Cambios hechos por Dra. Vivechana

@@
 
-\author[4]{D. Ariza-Flores}
+\author[4]{D. Ariza-Flores}[orcid=0000-0002-1775-6598]
 \ead{david1cool@gmail.com}
@@
 \begin{abstract}
-Porous silicon is a very versatile material for developing optical
-devices based on multilayered structures, since high and low porosity layers
-can be synthesized by a simple electrochemical technique. In the present work, we design
-mirrors using \textit{chirped}-type structures and by stacking
-appropriately tuned sub-mirrors, and we optimize the design parameters
-to maximize the
-optical reflectance $\braket{R}$ averaged within a wide
-spectral range  covering the visible and near infrared regions, and
-within a wide angular range. The chirped structures are found to be
-more suitable for the visible range,
-while stacked sub-mirrors are found to be better for the NIR
-region. We design, fabricate and characterize
-some of the optimized omnidirectional mirrors with less
-than 100 pairs of layers. We obtained structures with a wider
-omnidirectional spectral region than those previously
-reported.
+We have designed, optimized, fabricated and characterized highly 
+reflective quasi-omnidirectional (angular range of $0-60^\circ$) 
+multilayered structures with a wide spectral range. Two techniques, 
+chirping (a continuous change in thicknesses) and stacking of 
+Bragg-type sub-structures, have been used to enhance the 
+reflectance with minimum thickness for a given pair of refractive 
+indices. Numerical calculations were carried out employing the 
+transfer matrix method and we optimized the design parameters to 
+obtain maximal reflectance averaged over different spectral ranges 
+for all angles. We fabricated some of the optimized structures with 
+porous silicon dielectric multilayers with low refractive contrast 
+and compared their measured  optical properties with the 
+calculations. Two chirped structures with thicknesses 21.6 $\mu$m 
+and 60.4 $\mu$m, resulting in quasi omnidirectional mirrors with 
+bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm 
+respectively have been shown. In addition, we fabricated a stacked 
+sub-Bragg mirror structure  with a quasi omnidirectional bandwidth 
+of 1800 nm (centered at 1850 nm) and a thickness of 41.5 $\mu$m, 
+which is almost two third (in thickness) of the chirped structure. 
+Thus, our techniques allowed us to obtain relatively thin 
+quasi-omnidirectional mirrors with wide bands over different 
+wavelength ranges. Our analysis techniques can be used for the 
+optimization of the reflectance not only in multilayered PS 
+systems  with different refractive index contrasts but also for 
+systems with other types of materials with low refractive index 
+contrast. The present study could also be useful for obtaining 
+omnidirectional dielectric mirrors in large spectral regions using 
+different materials,  flat focusing reflectors, thermal regulators, 
+or, if defects are included, as filters or remote 
+chemical/biosensors with a wide angular independent response.
 \end{abstract}
@@
 
-%\section{Numerical simulation} \label{s:theory}
 \section{Theory} \label{s:theory}
@@
 multilayer systems, as
-proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
+proposed by Puente-D\'{i}az, et al. \cite{Puente2020}, summarized in the
 supplementary information. The
@@
 compare the results with experimental spectra taken from
-the corresponding samples at several angles of
+the corresponding samples at diferent angles of
 incidence. Sec. \ref{ss:chirped} is devoted to chirped-type Bragg
@@
 $p_h=0.76$ for the low and high porosities
-are shown in Table \ref{tab:tableA}.
+are shown in Table \ref{tab:tableA}. In the supplementary 
+information, we include the parameters used to calculate the 
+reflectance of structures corresponding to the porosity $p_l=0.30$ 
+and $p_h=0.76$. We also add the theoretical results obtained for 
+$p_l=0.42$ and $p_h=0.76$.
 
@@
 largest reported work until now in the NIR region \cite{Wu2021}. 
+As compared to the previous studies \cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work 
+opens the possibility of generating dielectric multilayered 
+structure with large omnidirectional band with 
+the materials with relatively low refractive index contrast.
 
@@
 design parameters to obtain maximal reflectance averaged over different spectral ranges for
-all angles. We fabricated some of the optimized structures with
+all angles. 
+We fabricated some of the optimized structures with
 porous silicon
-dielectric multilayers and compared their measured  optical properties
+dielectric multilayers with low refractive contrast and compared their measured  optical properties
 with the calculations. Two chirped structures
@@
 resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
-at 1160 nm and 1925 nm respectively have been shown. In addition, we fabricated a
-stacked structure  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
-with a bandwidth of 1800 nm centered at 1850 nm.
+at 1160 nm and 1925 nm respectively have been shown. In addition, 
+we fabricated a stacked sub-Bragg mirror structure  with a quasi 
+omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a 
+thickness of 41.5 $\mu$m, which is almost two third (in thickness) 
+of the chirped structure.
 Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
@@
 Our analysis techniques can
-be used for the optimization of the reflectance multilayered PS systems with
-different refractive index contrasts or for systems with other types of
-materials. Such proposed structures could be used as mirrors for solar
-concentrators, flat focusing reflectors, thermal regulators, or, if
-defects are included, as filters or remote chemical/biosensors with a
-wide angular independent response.
+be used for the optimization of the reflectance not only in multilayered PS systems with
+different refractive index contrasts but also for systems with other types of
+materials with low refractive index contrast.
+The present study could also be useful for obtaining omnidirectional dielectric mirrors in large spectral regions using different materials,  flat focusing reflectors, thermal regulators, or, if
+defects are included, as filters or remote chemical/biosensors with 
+a wide angular independent response.
 

### 2021-04-25 PaperVictor.tex
Ŕemove spaces inadvertently by Vivechna
Minor punctuation correction
Relabel figures
Relabel tables

@@
 
-\author[1]{V Agarwal}[orcid=0000-0003-2168-853X]
+\author[1]{V. Agarwal}[orcid=0000-0003-2168-853X]
 \fnmark[1]
@@
         \centering
-        \label{tab:tableA}
         \addtolength{\tabcolsep}{-2pt}
@@
                 width and center (ODW and ODC).}
+        \label{tab:tableA}
 \end{table}
@@
 \begin{figure}
-        \label{Fig1}
         \begin{center}
@@
                 indicate the quasi-ODB.}
+        \label{Fig1}
 \end{figure}
@@
 \begin{figure}
-  \label{Fig2}
   \begin{center}
@@
     structure. Inset: photograph of the synthesized structure.}
+  \label{Fig2}
 \end{figure}
@@
         \centering
-        \label{tab:table2}
         \begin{tabular}{rrrrr}
@@
                 are typeset in bold.}
+        \label{tab:table2}
 \end{table}
 
-According to table \ref{tab:table2}, the structure that has the highest
+According to Table \ref{tab:table2}, the structure that has the highest
 reflectance is in the second block, with an optimal overlap between
@@
         \centering
-        \label{tab:table3}
         \begin{tabular}{rrrrr}
@@
                 block. We show the attained omnidirectional bands (ODB) and their widths (ODW).}
+        \label{tab:table3}
 \end{table}

### 2021-04-27 PaperVictor.tex
Agregue rangos angulares en T3

@@
 
-\begin{graphicalabstract}
-  \includegraphics[width=\textwidth]{GraphicalAbstract.pdf}
-\end{graphicalabstract}
+%\begin{graphicalabstract}
+%  \includegraphics[width=\textwidth]{GraphicalAbstract.pdf}
+%\end{graphicalabstract}
 
-\begin{highlights}
-\item We design, optimize, fabricate and characterize
-  wideband quasi-omnidirectional (q-OD) structures
-  using different approaches.
-\item Reflectance averaged over wide spectral range is
-  optimized with simple parametrized functions
-  (chirped) and by stacking Bragg submirrors.
-\item Chirped structure with q-OD bandwidth of 1800 nm
-  in the NIR have been demonstrated.
-\item Stacking Bragg submirrors resulted in similar
-  q-OD band with two third of total physical
-  thickness.
-\item Agreement between the theoretical and
-  experimental results is obtained for porous silicon
-  multilayers .
-\item Proposed design techniques can be useful for
-  obtaining OD dielectric mirrors with different
-  materials in large spectral regions.
-\end{highlights}
+%\begin{highlights}
+%\item We design, optimize, fabricate and characterize
+%  wideband quasi-omnidirectional (q-OD) structures
+%  using different approaches.
+%\item Reflectance averaged over wide spectral range is
+%  optimized with simple parametrized functions
+%  (chirped) and by stacking Bragg submirrors.
+%\item Chirped structure with q-OD bandwidth of 1800 nm
+%  in the NIR have been demonstrated.
+%\item Stacking Bragg submirrors resulted in similar
+%  q-OD band with two third of total physical
+%  thickness.
+%\item Agreement between the theoretical and
+%  experimental results is obtained for porous silicon
+%  multilayers .
+%\item Proposed design techniques can be useful for
+%  obtaining OD dielectric mirrors with different
+%  materials in large spectral regions.
+%\end{highlights}
 
@@
         \centering
-        \begin{tabular}{rrrrr}
-                Reference&Year&Sample&ODB (nm)&ODW (nm)\\
+        \begin{tabular}{rrrrrr}
+                Reference&Year&Sample&ODB (nm)&AR ($^\circ$)&ODW (nm)\\
                 \hline
                 \hline
-                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&340\\
-                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-    &1297-1615&318\\
-                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456 &506\\
-                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&1000\\
-                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&1321\\
+                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
+                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
+                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
+                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
+                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
                 \hline
-                &    &$S_1$&980-1340&360 \\
-                This work                               &2021&$S_2$&980-2780&1800\\
-                &    &$S_3$&950-2750&1800\\
+                &    &$S_1$&980-1340&10-60&360 \\
+                This work                               &2021&$S_2$&980-2780&10-60&1800\\
+                &    &$S_3$&950-2750&10-60&1800\\
         \end{tabular}
@@
                 previously published works (first block) and for the different samples studied here (second
-                block. We show the attained omnidirectional bands (ODB) and their widths (ODW).}
+                block). We show the attained omnidirectional bands (ODB) in the angular range (AR) and their widths (ODW).}
         \label{tab:table3}

### 2021-04-28 reply.tex
Respuesta al referee

% Created 2021-04-24 Sat 19:24
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{bm}\usepackage[left=1in,right=1in]{geometry}
\date{}
\title{}
\hypersetup{
 pdfauthor={Luis Mochan},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)},
 pdflang={English}}
\begin{document}

\noindent{Dear Maurizio Ferrari\\Handling Editor\\Optical Materials}

Please find enclosed a revised version of our manuscript OM-D-21-00419
entitled \emph{Optimization of wide-band quasi-omnidirectional 1-D photonic
structures}. In the following we discuss the reviewer's remarks.
\section{Reviewer \#2:}
\label{sec:org02237c2}
\begin{itemize}
\item \emph\{First of all, I would like to commend this work. The article
overall is very interesting, it contains a good amount of valuable
information, a detailed description of the methods used, and
convincing results from both calculations and experiments. The
body of the paper is for the most part clear and complete, and I
would recommend it for publication,\}
\begin{itemize}
\item We are grateful for the reviewers opinion.
\end{itemize}
\item \emph{as soon as some minor corrections are performed.}
\item \emph\{In particular, there seems to be an issue with the labeling
of figures and tables: the numbering in the text does not match
the notations in the figure and table captions.\}
\begin{itemize}
\item We are sorry for this confusion which was due to misplaced
\texttt{\textbackslash{}label} statements in the tex source. We have made the
corresponding corrections.
\end{itemize}
\item \emph\{Also, in the final paragraph of the results section you
compare the qODB with the ODB of devices proposed by other papers
(table 3). While it has been stated before that your results are
specifically referring to a quasi-omnidirectional PBG, I suggest
pointing out explicitly one more time whether you are comparing a
quasi-omindirectional PBG of this paper to the actual
omnidirectional PBGs from literature, or you are considering just
the 0-60° qODW for all of the cited works. This is also due to the
fact that the papers in question present different angular ranges
in their evaluation of the omnidirectional bandgap, and therefore
the comparison should take that into account for the sake of
transparency.\}
\begin{itemize}
\item We agree with the reviewer. In the discussion of Table 3 we
now remind the reader that our band is not \emph{omnidirectional} but
\emph{quasi-omnidirectional} and we included the angular range
reported in the corresponding references.
\end{itemize}
\end{itemize}
\section{In summary}
\label{sec:orge75e81e}
\begin{itemize}
\item We have addressed all of the remarks and suggestions received from
the reviewer.
\item Our manuscript presents different approaches to the design of
optimized wide-band omnidirectional mirrors, we fabricated and
characterized the corresponding structures and obtained mirrors
that compare favorably to others described in the literature.
\item The reviewer commended this work and recommended its publication,
save for the issues which have been addressed in this revision.
\item Thus we believe that the current version is appropriate for
publication in Optical Materials.
\end{itemize}

\noindent Yours truly,

\noindent Victor Castillo-Galalrdo
\end{document}

### 2021-04-28 reply.tex
Remove typographic errors in reply

@@
 \begin{itemize}
-\item \emph\{First of all, I would like to commend this work. The article
+\item \emph{First of all, I would like to commend this work. The article
 overall is very interesting, it contains a good amount of valuable
@@
 body of the paper is for the most part clear and complete, and I
-would recommend it for publication,\}
+would recommend it for publication,}
 \begin{itemize}

### 2021-04-28 PaperVictor.tex
Describe the changes to table 3 in the text and highlight changes

@@
 \usepackage{bm}
-
+\usepackage{xcolor}
+\newcommand{\hl}[1]{{\color{blue}#1}}
 \begin{document}
@@
 Finally, Table \ref{tab:table3} shows data from some porous
-silicon based ODM designed to operate in the NIR
-region and their of the ODB's are compared with those of
-the structures analyzed in the present study. The ODW
+silicon based ODM \hl{and quasi-ODM designed to operate in the NIR
+region and their (quasi) ODB's are compared with those of
+the structures analyzed in the present study. The quasi-ODW}
 of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
 et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
-the ODB of the structure $S_3$ begins at 950 nm like the one
+\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
 synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
-nm. In other words, $S_3$ has an ODW 3.55 times higher. Moreover, the
+nm. In other words, $S_3$ has \hl{a quasi-ODW 3.55 times larger}. Moreover, the
 ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
-\% of the ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
+\% of the \hl{quasi-ODW of our $S_2$ and $S_3$ structures}. Aditionally, the table
 reveals that the porous silicon based
@@
 largest reported work until now in the NIR region \cite{Wu2021}.
-As compared to the previous studies \cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
+As compared to the previous studies
+\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
 opens the possibility of generating dielectric multilayered
-structure with large omnidirectional band with
-the materials with relatively low refractive index contrast.
+\hl{structures with large quasi-omnidirectional bands with pairs of
+materials that have a relatively low refractive index contrast. To be
+fair, we have to point out that the (quasi) omnidirectional band widths of the
+structures compared above correspond to different angular ranges,
+which are defined by instrumental constrictions.}
 
@@
         \begin{tabular}{rrrrrr}
-                Reference&Year&Sample&ODB (nm)&AR ($^\circ$)&ODW (nm)\\
+                Reference&Year&Sample&\emph{q}-ODB (nm)&\hl{AR (degrees)}&\emph{q}-ODW (nm)\\
                 \hline
                 \hline
-                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
-                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
-                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
-                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
-                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
+                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&\hl{0-80}&340\\
+                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&\hl{0-89}&318\\
+                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&\hl{8-68}&506\\
+                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&\hl{8-65}&1000\\
+                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&\hl{0-80}&1321\\
                 \hline
-                &    &$S_1$&980-1340&10-60&360 \\
-                This work                               &2021&$S_2$&980-2780&10-60&1800\\
-                &    &$S_3$&950-2750&10-60&1800\\
+                &    &$S_1$&980-1340&\hl{10-60}&360 \\
+                This work&2021&$S_2$&980-2780&\hl{10-60}&1800\\
+                &    &$S_3$&950-2750&\hl{10-60}&1800\\
         \end{tabular}
@@
                 previously published works (first block) and for the different samples studied here (second
-                block). We show the attained omnidirectional bands (ODB) in the angular range (AR) and their widths (ODW).}
+                block). We show the attained (quasi) omnidirectional
+                bands (\emph{q}-ODB), the measured angular range (AR) and their widths (\emph{q}-ODW).}
         \label{tab:table3}
@@
 spectral range. Two techniques, chirping (a continuous change in thicknesses) and
-stacking of Bragg-type sub-structures, have been used to enhance the reflectance with minimum thickness for a given pair of refractive indices. Numerical calculations were
+stacking of Bragg-type sub-structures, have been used to enhance the
+reflectance with minimum thickness for a given pair of refractive
+indices. Numerical calculations were
 carried out employing the transfer matrix method and we optimized the
@@
 different refractive index contrasts but also for systems with other types of
-materials with low refractive index contrast.
-The present study could also be useful for obtaining omnidirectional dielectric mirrors in large spectral regions using different materials,  flat focusing reflectors, thermal regulators, or, if
+materials with low refractive index contrast. The present study could
+also be useful for obtaining omnidirectional dielectric mirrors in
+large spectral regions using different materials,  flat focusing
+reflectors, thermal regulators, or, if
 defects are included, as filters or remote chemical/biosensors with

### 2021-04-28 reply.tex
Finish reply

@@
-% Created 2021-04-24 Sat 19:24
+% Created 2021-04-27 Tue 20:23
 % Intended LaTeX compiler: pdflatex
@@
 \section{Reviewer \#2:}
-\label{sec:org02237c2}
+\label{sec:orgc9f91cf}
 \begin{itemize}
@@
 \item \emph{as soon as some minor corrections are performed.}
-\item \emph\{In particular, there seems to be an issue with the labeling
+\item \emph{In particular, there seems to be an issue with the labeling
     of figures and tables: the numbering in the text does not match
-the notations in the figure and table captions.\}
+    the notations in the figure and table captions.}
 \begin{itemize}
@@
 \end{itemize}
-\item \emph\{Also, in the final paragraph of the results section you
+\item \emph{Also, in the final paragraph of the results section you
     compare the qODB with the ODB of devices proposed by other papers
@@
     the comparison should take that into account for the sake of
-transparency.\}
+    transparency.}
 \begin{itemize}
@@
 \section{In summary}
-\label{sec:orge75e81e}
+\label{sec:org62171b7}
 \begin{itemize}
@@
 the reviewer.
+\item We have highlighted in color the revisions to our manuscript.
 \item Our manuscript presents different approaches to the design of

### 2021-04-29 PaperVictor.tex
Agregue - a todas las palabras quasi-omnidirectional

--- 2021-04-27 PaperVictor.tex
@@
 calculations. Two chirped structures with thicknesses 21.6 $\mu$m
-and 60.4 $\mu$m, resulting in quasi omnidirectional mirrors with
+and 60.4 $\mu$m, resulting in quasi-omnidirectional mirrors with
 bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
 respectively have been shown. In addition, we fabricated a stacked
-sub-Bragg mirror structure  with a quasi omnidirectional bandwidth
+sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
 of 1800 nm (centered at 1850 nm) and a thickness of 41.5 $\mu$m,
@@
 their energies are consequently organized into photonic bands. In
-analogy to electronic bands withiny a
+analogy to electronic bands within a
 crystal, propagation is forbidden if the energy lies
@@
     region where the reflectance is greater than  $0.90$,
-    corresponding to the quasi ODB of the
+    corresponding to the quasi-ODB of the
     structure. Inset: photograph of the synthesized structure.}
@@
 calculated and measured reflectance for the structure $S_3$ at several angles of
-incidence. Although, the quasi omnidirectional wavelength range of
+incidence. Although, the quasi-omnidirectional wavelength range of
 the synthesized structure, from 950 to 2750 nm, is slightly smaller than the calculated
@@
 Finally, Table \ref{tab:table3} shows data from some porous
-silicon based ODM designed to operate in the NIR
-region and their of the ODB's are compared with those of
-the structures analyzed in the present study. The ODW
+silicon based ODM and quasi-ODM designed to operate in the NIR
+region and their (quasi) ODB's are compared with those of
+the structures analyzed in the present study. The quasi-ODW
 of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
 et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
-the ODB of the structure $S_3$ begins at 950 nm like the one
+the quasi-ODB of the structure $S_3$ begins at 950 nm like the one
 synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
-nm. In other words, $S_3$ has an ODW 3.55 times higher. Moreover, the
+nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
 ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
-\% of the ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
+\% of the quasi-ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
 reveals that the porous silicon based
@@
 largest reported work until now in the NIR region \cite{Wu2021}.
-As compared to the previous studies \cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
+As compared to the previous studies
+\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
 opens the possibility of generating dielectric multilayered
-structure with large omnidirectional band with
-the materials with relatively low refractive index contrast.
+structures with large quasi-omnidirectional bands with pairs of
+materials that have a relatively low refractive index contrast. To be
+fair, we have to point out that the (quasi-) omnidirectional band widths of the
+structures compared above correspond to different angular ranges,
+which are defined by instrumental constrictions.
 
@@
         \begin{tabular}{rrrrrr}
-                Reference&Year&Sample&ODB (nm)&AR ($^\circ$)&ODW (nm)\\
+                Reference&Year&Sample&\emph{q}-ODB (nm)&AR (degrees)&\emph{q}-ODW (nm)\\
                 \hline
@@
                 &    &$S_1$&980-1340&10-60&360 \\
-                This work                               &2021&$S_2$&980-2780&10-60&1800\\
+                This work&2021&$S_2$&980-2780&10-60&1800\\
                 &    &$S_3$&950-2750&10-60&1800\\
@@
                 previously published works (first block) and for the different samples studied here (second
-                block). We show the attained omnidirectional bands (ODB) in the angular range (AR) and their widths (ODW).}
+                block). We show the attained (quasi-) omnidirectional
+                bands (\emph{q}-ODB), the measured angular range (AR) and their widths (\emph{q}-ODW).}
         \label{tab:table3}
@@
 
-We have designed, optimized, fabricated and characterized highly reflective quasi
-omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
+We have designed, optimized, fabricated and characterized highly reflective quasi-omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
 spectral range. Two techniques, chirping (a continuous change in thicknesses) and
-stacking of Bragg-type sub-structures, have been used to enhance the reflectance with minimum thickness for a given pair of refractive indices. Numerical calculations were
+stacking of Bragg-type sub-structures, have been used to enhance the
+reflectance with minimum thickness for a given pair of refractive
+indices. Numerical calculations were
 carried out employing the transfer matrix method and we optimized the
@@
 with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
-resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
+resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
 at 1160 nm and 1925 nm respectively have been shown. In addition,
-we fabricated a stacked sub-Bragg mirror structure  with a quasi
-omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a
+we fabricated a stacked sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a
 thickness of 41.5 $\mu$m, which is almost two third (in thickness)

### 2021-05-01 PaperVictor.tex
Add \hl's removed by VIctor

@@
 Finally, Table \ref{tab:table3} shows data from some porous
-silicon based ODM and quasi-ODM designed to operate in the NIR
+silicon based ODM \hl{and quasi-ODM designed to operate in the NIR
 region and their (quasi) ODB's are compared with those of
-the structures analyzed in the present study. The quasi-ODW
+the structures analyzed in the present study. The quasi-ODW}
 of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
 et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
-the quasi-ODB of the structure $S_3$ begins at 950 nm like the one
+\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
 synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
@@
 ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
-\% of the quasi-ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
+\% of the \hl{quasi-ODW of our $S_2$ and $S_3$ structures}. Aditionally, the table
 reveals that the porous silicon based
@@
 opens the possibility of generating dielectric multilayered
-structures with large quasi-omnidirectional bands with pairs of
+\hl{structures with large quasi-omnidirectional bands with pairs of
 materials that have a relatively low refractive index contrast. To be
@@
 structures compared above correspond to different angular ranges,
-which are defined by instrumental constrictions.
+which are defined by instrumental constrictions.}
 
@@
         \begin{tabular}{rrrrrr}
-                Reference&Year&Sample&\emph{q}-ODB (nm)&AR (degrees)&\emph{q}-ODW (nm)\\
+                Reference&Year&Sample&\emph{q}-ODB (nm)&\hl{AR (degrees)}&\emph{q}-ODW (nm)\\
                 \hline
                 \hline
-                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
-                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
-                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
-                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
-                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
+                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&\hl{0-80}&340\\
+                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&\hl{0-89}&318\\
+                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&\hl{8-68}&506\\
+                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&\hl{8-65}&1000\\
+                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&\hl{0-80}&1321\\
                 \hline
-                &    &$S_1$&980-1340&10-60&360 \\
-                This work&2021&$S_2$&980-2780&10-60&1800\\
-                &    &$S_3$&950-2750&10-60&1800\\
+                &    &$S_1$&980-1340&\hl{10-60}&360 \\
+                This work&2021&$S_2$&980-2780&\hl{10-60}&1800\\
+                &    &$S_3$&950-2750&\hl{10-60}&1800\\
         \end{tabular}
@@
 
-We have designed, optimized, fabricated and characterized highly reflective quasi-omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
+We have designed, optimized, fabricated and characterized highly
+reflective quasi-omnidirectional (angular range of $0-60^\circ$)
+multilayered structures with a wide
 spectral range. Two techniques, chirping (a continuous change in thicknesses) and
@@
 at 1160 nm and 1925 nm respectively have been shown. In addition,
-we fabricated a stacked sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a
-thickness of 41.5 $\mu$m, which is almost two third (in thickness)
-of the chirped structure.
-Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
+we fabricated a stacked sub-Bragg mirror structure  with a
+quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
+thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
+Thus, our techniques allowed us to obtain relatively thin
+quasi-omnidirectional mirrors with wide bands
 over different wavelength ranges.

### 2021-05-01 PaperVictor.tex
Revise manuscript.

@@
 sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
-of 1800 nm (centered at 1850 nm) and a thickness of 41.5 $\mu$m,
+of 1800 nm centered at 1850 nm and a thickness of 41.5 $\mu$m,
 which is almost two third (in thickness) of the chirped structure.
@@
 increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
-PS based dielectric optical filters, quasi-ODM's and ODM's have been extensively studied in different
+PS based dielectric optical filters, {\em quasi}-ODM's and ODM's have
+been extensively studied in different
 regions of the electromagnetic spectrum, such as the ultraviolet (UV)
@@
 periods  in the structure, and $f(\xi)$ is a smooth function that
-goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
+goes from 0 to 1 as its argument \hl{$\xi=j/(N_p-1)$} goes from the surface ($\xi=0$) to the
 substrate ($\xi=1)$. We only consider increasing functions $f$ due to
@@
 $\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
-In the first case, we decided to optimize $\lambda_{min}$ to
+In the first case, we decided to optimize $\lambda_{\min}$ to
 obtain the best design in the high absorption zone of the PS.
@@
 Finally, Table \ref{tab:table3} shows data from some porous
-silicon based ODM \hl{and quasi-ODM designed to operate in the NIR
-region and their (quasi) ODB's are compared with those of
+silicon based ODM's \hl{and quasi-ODM's designed to operate in the NIR
+region and their (quasi-) ODB's are compared with those of
 the structures analyzed in the present study. The quasi-ODW}
@@
 ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
-\% of the \hl{quasi-ODW of our $S_2$ and $S_3$ structures}. Aditionally, the table
+\% of the \hl{quasi-ODW's of our $S_2$ and $S_3$ structures}. Aditionally, the table
 reveals that the porous silicon based
@@
 materials that have a relatively low refractive index contrast. To be
-fair, we have to point out that the (quasi-) omnidirectional band widths of the
-structures compared above correspond to different angular ranges,
+fair, we have to remark that, as shown in Table \ref{tab:table3}, the
+(quasi-) omnidirectional band widths of the structures compared above
+correspond to different angular ranges,
 which are defined by instrumental constrictions.}
@@
 indices. Numerical calculations were
-carried out employing the transfer matrix method and we optimized the
+carried out employing a stabilized transfer matrix method and we optimized the
 design parameters to obtain maximal reflectance averaged over different spectral ranges for

### 2021-05-01 PaperVictor.tex
Corrections of David

@@
 \documentclass[a4paper,fleqn]{cas-sc}
-\usepackage[numbers]{natbib}
+\usepackage[numbers,sort&compress]{natbib}
 %%%Author macros
@@
 %%%
+%\usepackage{cite}
 \usepackage{braket}
@@
 \begin{document}
+\bibliographystyle{unsrt}
 \let\WriteBookmarks\relax
@@
 \begin{abstract}
-We have designed, optimized, fabricated and characterized highly
-reflective quasi-omnidirectional (angular range of $0-60^\circ$)
-multilayered structures with a wide spectral range. Two techniques,
-chirping (a continuous change in thicknesses) and stacking of
-Bragg-type sub-structures, have been used to enhance the
-reflectance with minimum thickness for a given pair of refractive
-indices. Numerical calculations were carried out employing the
-transfer matrix method and we optimized the design parameters to
-obtain maximal reflectance averaged over different spectral ranges
-for all angles. We fabricated some of the optimized structures with
-porous silicon dielectric multilayers with low refractive contrast
-and compared their measured  optical properties with the
-calculations. Two chirped structures with thicknesses 21.6 $\mu$m
-and 60.4 $\mu$m, resulting in quasi-omnidirectional mirrors with
-bandwidths of 360 nm and 1800 nm, centered at 1160 nm and 1925 nm
-respectively have been shown. In addition, we fabricated a stacked
-sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth
-of 1800 nm centered at 1850 nm and a thickness of 41.5 $\mu$m,
-which is almost two third (in thickness) of the chirped structure.
-Thus, our techniques allowed us to obtain relatively thin
+We design, optimize, fabricate, and characterize highly
+reflective quasi-omnidirectional multilayered structures with a wide
+angular and spectral range. We consider chirped structures with layers
+of gradually varying thicknesses and structures made by stacking
+Bragg-type sub-structures, and we maximized their numerically calculated
+reflectance averaged over different spectral ranges keeping a minimum
+thickness for given pairs of refractive indices. We fabricated some of
+these structures with porous silicon with a low refractive contrast
+between adjacent layers,
+and compared their measured  optical properties to the theoretical
+results and to previous works. We obtained relatively thin
 quasi-omnidirectional mirrors with wide bands over different
-wavelength ranges. Our analysis techniques can be used for the
-optimization of the reflectance not only in multilayered PS
-systems  with different refractive index contrasts but also for
-systems with other types of materials with low refractive index
-contrast. The present study could also be useful for obtaining
-omnidirectional dielectric mirrors in large spectral regions using
-different materials,  flat focusing reflectors, thermal regulators,
-or, if defects are included, as filters or remote
-chemical/biosensors with a wide angular independent response.
+wavelength ranges that compare favorably to others reported in the
+literature.
+
 \end{abstract}
@@
 of periodically alternating
-layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
-corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
+layers of high $n_h$ and low $n_l$ refractive indices, with
+corresponding thicknesses $d_h$ and $d_l$ chosen so that their optical
 thicknesses corresponds to a quarter of a wavelength
-$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
+$n_hd_h=n_ld_l=\lambda_{0}/4$ at a nominal
 wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
-which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
+which might have a large PBG including an omnidirectional gap if the contrast $n_h/n_l$
 and the number of periods are large enough. Mirrors with high
@@
 chirped multilayer structures has
-increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
+increased due to their possible application as flat focusing mirrors
+\cite{Wu2021,Kozar2017,Cheng2018}.
 PS based dielectric optical filters, {\em quasi}-ODM's and ODM's have
@@
     (panel a)  and $S_2$ (panel b). The gray band indicates the
-    region where the reflectance is greater than  $0.90$,
+    region where the reflectance is greater than  $90\%$,
     corresponding to the quasi-ODB of the
@@
 consecutive PBGs of $78\%$, a thickness of
-41.5 $\mu$m, and an average reflectance $\braket{0.954}$. It is made up
+41.5 $\mu$m, and an average reflectance $\braket{R}=95.4\%$. It is made up
 of 18 sub-mirrors tuned to the wavelengths
@@
                 $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
-                the region in which the reflectance is greater than $R>0.90$.  Inset shows a
+                the region in which the reflectance is greater than $R>90\%$.  Inset shows a
                 photograph with a top view of the synthesized structure.}
@@
 
-We have designed, optimized, fabricated and characterized highly
-reflective quasi-omnidirectional (angular range of $0-60^\circ$)
-multilayered structures with a wide
-spectral range. Two techniques, chirping (a continuous change in thicknesses) and
-stacking of Bragg-type sub-structures, have been used to enhance the
+We developed a formalism to design and optimize highly
+reflective quasi-omnidirectional multilayered mirrors with a wide
+spectral range. We considered two kinds of systems, chirped structures with a gradual
+change in layer thicknesses and
+stacked Bragg mirrors tuned so that their bandwidths overlap, and
+optimized their
 reflectance with minimum thickness for a given pair of refractive
@@
 resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
-at 1160 nm and 1925 nm respectively have been shown. In addition,
-we fabricated a stacked sub-Bragg mirror structure  with a
+at 1160 nm and 1925 nm respectively were shown. In addition,
+we fabricated a stacked structure  with a
 quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
@@
 quasi-omnidirectional mirrors with wide bands
-over different wavelength ranges.
-Our analysis techniques can
-be used for the optimization of the reflectance not only in multilayered PS systems with
-different refractive index contrasts but also for systems with other types of
+over different wavelength ranges that compare favorably to those in
+the literature.
+We believe that our analysis techniques can
+be used for the optimization of the reflectance not only in
+multilayered porous silicon systems but also for systems with other types of
 materials with low refractive index contrast. The present study could
@@
 
-\bibliographystyle{unsrt}
 \bibliography{Bibliografia}

### 2021-05-01 PaperVictor.tex
Highlight new changes

@@
 %%%
-%\usepackage{cite}
 \usepackage{braket}
@@
 \begin{document}
-\bibliographystyle{unsrt}
 \let\WriteBookmarks\relax
@@
 \begin{abstract}
-We design, optimize, fabricate, and characterize highly
+\hl{We design, optimize, fabricate, and characterize highly
 reflective quasi-omnidirectional multilayered structures with a wide
@@
 wavelength ranges that compare favorably to others reported in the
-literature.
+literature.}
 
@@
 
-We developed a formalism to design and optimize highly
+\hl{We developed a formalism to design and optimize highly
 reflective quasi-omnidirectional multilayered mirrors with a wide
@@
 stacked Bragg mirrors tuned so that their bandwidths overlap, and
-optimized their
+optimized their}
 reflectance with minimum thickness for a given pair of refractive
@@
 resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
-at 1160 nm and 1925 nm respectively were shown. In addition,
-we fabricated a stacked structure  with a
+\hl{at 1160 nm and 1925 nm respectively were shown. In addition,
+we fabricated a stacked structure} with a
 quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
@@
 quasi-omnidirectional mirrors with wide bands
-over different wavelength ranges that compare favorably to those in
+over different wavelength ranges \hl{that compare favorably to those in
 the literature.
@@
 
+\bibliographystyle{unsrt}
 \bibliography{Bibliografia}

### 2021-05-01 PaperVictor.tex
Correct a latex mistake

@@
 be used for the optimization of the reflectance not only in
-multilayered porous silicon systems but also for systems with other types of
+multilayered porous silicon} systems but also for systems with other types of
 materials with low refractive index contrast. The present study could

### 2021-05-02 SupplementaryInformation.tex
Rename supplementary information and apply David's suggestions

--- 2020-09-19 SuplementaryInformation.tex
@@
 	% structures}
-	\title{Suplementary information: Thickness optimization in wide range quasi
-		omnidirectional 1-D photonic structures}
+	\title{Suplementary information: Optimization of wide-band
+          quasi-omnidirectional 1-D photonic structures}
 	\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
@@
 If you consider that the system only varies on the $z$ axis (as show in Fig.
-\ref{Fig1}(a)) , the transfer matrix is $M\left(z_{2},z_{1}\right) ${}{}a
+\ref{Fig1}(a)) , the transfer matrix is $M\left(z_{2},z_{1}\right) $
+is a
 2x2 matrix that relates the components of the electric field E$_{\parallel }$
@@
 
-Many equivalent formulations have been proposed to obtain $M$ . For example, if you 
+Many equivalent formulations have been proposed to obtain $M$. For example, if you
 have a complete multilayer system and it periodically replicates to form an artificial photonic crystal, then Bloch's theorem can be used to describe the normal
@@
 thickness of the multilayered system, and $\pm K$ represents a 1D Bloch's
-vector corresponding to a wave that propagates along $z$-direction. Thus, $\Lambda _{\pm }=e^{\pm iKD}$ are
+vector corresponding to a wave that propagates along $z$-direction. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
 the eigenvalues of transfer matrix $M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
 }^{\pm }$ are the corresponding eigenvectors. Notice that exactly $\det M=1$
-is used, so that the product of eigenvalues ought to be $\Lambda _{+}\Lambda
-_{-}=1$, and the dispersion relation of the Bloch modes may be obtained in
+is used, so that the product of eigenvalues ought to be $\Lambda_{+}\Lambda_{-}=1$, and the dispersion relation of the Bloch modes may be obtained in
 principle from
@@
 waves should decay as they propagate. Thus, the eigenvalue of ascending mode
-$\Lambda _{+}=e^{iKD}$ is identified as the one that obeys $|\Lambda +|<1$, $%
+$\Lambda_{+}=e^{iKD}$ is identified as the one that obeys $|\Lambda_+|<1$, $%
 \text{Im}K>0$, adding a negligible amount of dissipation if necessary to
-avoid cases $|\Lambda +|=1$.
+avoid cases $|\Lambda_+|=1$.
 
-From the eigenvalues $\Lambda _{\pm }$ of the transfer matrix, we may obtain
+From the eigenvalues $\Lambda_{\pm }$ of the transfer matrix, we may obtain
 the corresponding eigenvectors $E_{\Vert }^{\pm }$ and $H_{\Vert }^{\pm }$
@@
 \begin{equation}
-Z^{\pm }=-\frac{M_{12}}{M_{11}-\Lambda _{\pm }},  \label{Z+-}
+Z^{\pm }=-\frac{M_{12}}{M_{11}-\Lambda_{\pm }},  \label{Z+-}
 \end{equation}%
@@
 where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
-in Eq. (\ref{tBloch}) has been chosen for the case of TE polarization, while
+in Eq. (\ref{tBloch}) have been chosen for the case of TE polarization, while
 the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
@@
 optimized parameters is shown in Fig. \ref{Fig2}. Here it is observed that all of
-them have a PBG in the NIR region of the electromagnetic spectrum, i. e.,  
+them have a PBG in the near infrared (NIR) region of the electromagnetic spectrum, i. e.,
 structures designed from functions $f_{1}$ and $f_{3}$ with a porosity contrast of
@@
 and \ref{Fig3}(d)). Each mirror was designed to reflect a wavelength in the range of
-400-3000 nm and the illumination range was the same. Additionally, the T$r|\text{M}|$ and R$(\lambda,\theta)$ were calculated for light with TE 
-polarization and 45${{}^\circ}$ of incidence. In Fig. 3d it is shown that by using 
+400-3000 nm and the illumination range was the same. Additionally, the
+$\text{Tr}|M|$ and $R(\lambda,\theta)$ were calculated for light with
+  TE
+polarization and $45^\circ$ of incidence. In Fig. \ref{Fig3}(d) it is shown that by using
 mirrors that have 6 periods and designed to reflect at wavelengths greater than 1000
@@
 the desired interval is completed. With this configuration, the reflectance
-decreases at each intersection of the two PBGs. For example, in Figs. \ref{Fig4}(a) 
-and \ref{Fig4}(b) show the calculated R$(\lambda, \theta)$ for the structures formed 
+decreases at each intersection of the two PBGs. For example, Figs. \ref{Fig4}(a)
+and \ref{Fig4}(b) show the calculated $R(\lambda, \theta)$ for the structures formed
 by sub-mirrors that have one and six periods, respectively, using non-polarized
 light. In these cases, the calculations do not show a PBG, or quasi-PBG. For this
-reason, the R$_{Ave}(\lambda, \theta)$ was maximized through the percentage of 
-overlap of the PBGs of two consecutive sub-mirrors. In Fig. 3 (b) of the main 
+reason, the $R_{Ave}(\lambda, \theta)$ was maximized through the percentage of
+overlap of the PBGs of two consecutive sub-mirrors. In Fig. \ref{Fig3}(b) of the main
 article the results obtained at the end of the optimization process are shown. The
-calculated R$(\lambda, \theta)$ for the structures designed with 4 periods for each 
+calculated $R(\lambda, \theta)$ for the structures designed with 4 periods for each
 sub-mirror and using the pattern described in the main article are shown in Figs.
@@
 		$72\%$ overlap, and (d) proposed arrangement in the main article with 6
-		periods for $\lambda>800$ nm and $78\%$ overlap. The quasi-OD region is bounded by the dotted lines.
+		periods for $\lambda>800$ nm and $78\%$ overlap. The
+                quasi-OD region is bounded by the dashed lines.
 	}

### 2021-05-02 SupplementaryInformation.tex
Start modifying supplementary information

@@
 
-If you consider that the system only varies on the $z$ axis (as show in Fig.
-\ref{Fig1}(a)) , the transfer matrix is $M\left(z_{2},z_{1}\right) $
+Consider a system that varies along  the $z$ axis only, as show in Fig.
+\ref{Fig1}(a). Its transfer matrix $\bm{M}(z_{2},z_{1})$
 is a
-2x2 matrix that relates the components of the electric field E$_{\parallel }$
-and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
+2x2 matrix that relates the components  $E_{\parallel }$ and
+$H_{\parallel }$ of the electric and magnetic fields parallel to the $xy$ plane and
 normal to the axis of the structure, evaluated at any two points $z_{2}$
-and $z_{1}$
+and $z_{1}$,
 \begin{equation*}
@@
 \end{array}%
-\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
+\right) _{z_{2}}=\bm M( z_{2},z_{1}) \left(
 \begin{array}{c}
@@
 
-Many equivalent formulations have been proposed to obtain $M$. For example, if you
-have a complete multilayer system and it periodically replicates to form an artificial photonic crystal, then Bloch's theorem can be used to describe the normal
-modes of this crystal. According to Bloch's theorem, the modes of a periodic system
-may be written as a superposition of Bloch waves, each of which acquires a
-\emph{phase factor} as it propagates from one period to the next. Therefore, each
-Bloch wave would obey
+Many equivalent formulations have been proposed to obtain $\bm M$. For
+a periodically
+replicated multilayered system, the transfer matrix may be constructed
+from the normal modes of the corresponding photonic crystal. These
+modes are described by Bloch's
+theorem, which reads in this case,
 \begin{equation}
@@
 \end{pmatrix}%
-_{z_{N}}=M%
+_{z_{N}}=\bm M%
 \begin{pmatrix}
@@
 where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
-thickness of the multilayered system, and $\pm K$ represents a 1D Bloch's
-vector corresponding to a wave that propagates along $z$-direction. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
-the eigenvalues of transfer matrix $M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
-}^{\pm }$ are the corresponding eigenvectors. Notice that exactly $\det M=1$
-is used, so that the product of eigenvalues ought to be $\Lambda_{+}\Lambda_{-}=1$, and the dispersion relation of the Bloch modes may be obtained in
-principle from
+thickness of the multilayered system, and $\pm K$ is the 1D Bloch's
+vector describing the propagation along $z$. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
+the eigenvalues of transfer matrix $\bm M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
+}^{\pm }$ are the corresponding eigenvectors. Notice that $\det M=1$  exactly,
+so the product of eigenvalues $\Lambda_{+}\Lambda_{-}=1$ and the
+dispersion relation of the Bloch modes becomes
 \begin{equation}
-\cos KD=\frac{1}{2}\text{Tr}\,M  \label{dispersion}
+\cos KD=\frac{1}{2}\text{Tr}\,\bm M  \label{dispersion}
 \end{equation}%
@@
 	\caption{(a) Chirped-type photonic structure formed by two alternating
-		materials a and b, with refractive indices $n_{a}$ and $n_{b}$, and their
+		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
 		thickness $d_{a}$ and $d_{b}$ gradually increases according to the condition
@@
 
-Now, considering a finite system made of $P$ periods, with $PD$ thickness
-and placed on a substrate. For the extreme case of only $P=1$ period, the
+Now, consider a finite system made of $P$ periods, with thickness $PD$
+and placed on a substrate. Even for the extreme $P=1$  case, the
 optical properties of this system can be obtained by considering an incoming

### 2021-05-02 SupplementaryInformation.tex
Change caption of fig. 1

@@
 		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
-		thickness $d_{a}$ and $d_{b}$ gradually increases according to the condition
-		of $1/4$ of the wavelength at wich $j$-th. period will be sintonized.
-		\textbf{E}$_{\protect\alpha }^{\protect\beta }$ and \textbf{H}$_{\protect%
-			\alpha }^{\protect\beta }$ are the electric and magnetic fields, and \textbf{%
-			k}$_{\protect\alpha }^{\protect\beta }$ is the wavevector, where $\alpha
-		=\left\{ i,r,a,b\right\} $ corresponds to the medium where the wave is
-		traveling and $\beta =\{-,+\}$ to the direction of propagation of the wave
-		along the $\pm z$ axis. (b) The multilayer system can be replaced by a broad
-		effective layer within which the electric \textbf{E}$_{\protect\beta }$ and
-		magnetic \textbf{H}$_{\protect\beta }$ fields, and a Bloch wave \textbf{K}$_{%
-			\protect\beta }$ propagate in the positive direction and another set
-		propagate in the opposite direction along the $z$ axis.}
+		thickness $d_{a}$ and $d_{b}$ that increases gradually
+                according to some design scheme. We show schematically
+                the  incident and reflected electric and magnetic
+                fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
+                their wavevectors $\bm k_i$ and $\bm k_r$, the right
+                ($+$) and left ($-$) moving fields within each layer
+                as well as their wavevectors $\bm k_\alpha^\pm$. (b)
+                The multilayer system can be replaced by an
+		effective layer within which supports right and left
+                moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
+                K^\pm)$ and electric and magnetic field amplitudes
+                $\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
+              the wavevector unto the $xy$ plane is $\bm Q$ for all
+              the waves, due to translational symmetry.}
 	\label{Fig1}

### 2021-05-02 SupplementaryInformation.tex
Finish revision

@@
 \usepackage{graphicx}
+\usepackage{braket}
 \usepackage{dcolumn}
@@
                 moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
-                K^\pm)$ and electric and magnetic field amplitudes
+                \pm K)$ and electric and magnetic field amplitudes
                 $\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
               the wavevector unto the $xy$ plane is $\bm Q$ for all
-              the waves, due to translational symmetry.}
+              the waves, due to translational symmetry and $K$ is
+              obtained from Eq. \eqref{dispersion}.}
 	\label{Fig1}
@@
 transmitted to the substrate, and two Bloch waves within the structure, one
-moving up and other down, as show in Fig. \ref{Fig1}(b).
+moving rightwards and other leftwards, as show in Fig. \ref{Fig1}(b). Hence, the
+continuity of $E_{\Vert }$ and $H_{\Vert }$ yields two
+equations at each interface, with which the four unknowns are obtained,
+namely the reflection and transmission amplitudes $r$ and $t$, and the
+amplitudes of the two Bloch's waves. In a finite system,
+$K$ can be complex. Even in the presence of very little dissipation, Bloch's
+waves should decay as they propagate. Thus, the eigenvalue of the right-moving mode
+$\Lambda_{+}=e^{iKD}$ is identified as the one that obeys
+$|\Lambda_+|<1$,
+$\text{Im}\,K>0$, adding a negligible amount of dissipation if necessary to
+avoid the case $|\Lambda_+|=1$. Then, $\Lambda_-=1/\lambda_+$
 
-Hence, the continuity of $E_{\Vert }$ and $H_{\Vert }$ will produce two
-equations at each interface, with which the four unknowns are obtained,
-namely $r$, $t$ and the amplitudes of two Bloch's waves. In a finite system,
-$K$ can be complex. Even in the presence of very little dissipation, Bloch's
-waves should decay as they propagate. Thus, the eigenvalue of ascending mode
-$\Lambda_{+}=e^{iKD}$ is identified as the one that obeys $|\Lambda_+|<1$, $%
-\text{Im}K>0$, adding a negligible amount of dissipation if necessary to
-avoid cases $|\Lambda_+|=1$.
-
-From the eigenvalues $\Lambda_{\pm }$ of the transfer matrix, we may obtain
-the corresponding eigenvectors $E_{\Vert }^{\pm }$ and $H_{\Vert }^{\pm }$
-from Eq. (\ref{Bloch}), and from them, the corresponding surfaces impedances
+From the eigenvalues $\Lambda_{\pm }$ of the transfer matrix, we obtain
+the corresponding eigenvectors $(E_{\Vert }^{\pm }, H_{\Vert }^{\pm
+})$, and from them, the corresponding surfaces impedances, given by
 \begin{equation}
@@
 where $M_{ij}$ with $i=1,2$ and $j=1,2$ denote the elements of the transfer
-matrix $M$. By writing the fields at $z_{0}$ and $z_{N}$ as a superposition
+matrix $\bm M$. By writing the fields at $z_{0}$ and $z_{N}$ as a superposition
 of the upward and downward propagating (or decaying) fields, $E_{\Vert
@@
 \end{pmatrix}%
-_{z_{N}}=\tilde{M}%
+_{z_{N}}=\tilde{\bm M}%
 \begin{pmatrix}
@@
 \begin{equation}
-\tilde{M}=\frac{1}{Z^{+}-Z^{-}}%
+\tilde{\bm M}=\frac{1}{Z^{+}-Z^{-}}%
 \begin{pmatrix}
@@
 \end{pmatrix}%
-.  \label{tilM}
+,\label{tilM}
 \end{equation}%
-Finally, the explicit expressions for the optical coefficients are:
+and its determinant is 1, even if numerical errors creep into the
+calculation of the original matrix $\bm M$.
+Finally, the explicit expressions for the optical coefficients are
 \begin{equation}
@@
 decreases and the average reflectance increases, as shown in table 1. For example,
-you could have structures with a thickness of 10 $\mu$m and their average
-reflectance greater than 90$\%$.
+you could have structures with a thickness of 10 $\mu$m with an average
+reflectance greater than $90\%$.
 
 \begin{table}[tbph]
-	\caption{ Design parameters obtained after the optimization of functions for maximum average reflectance and minimum thickness }
+	\caption{Optimized design parameters for different profile
+          function classes for different porosity contrasts and some
+          properties (number of periods, thickness and average
+          reflectance) of the resulting structures.}
 	\includegraphics[width=\textwidth]
@@
 
-The mapping of the calculated reflectance of the structures designed with the
-optimized parameters is shown in Fig. \ref{Fig2}. Here it is observed that all of
-them have a PBG in the near infrared (NIR) region of the electromagnetic spectrum, i. e.,
+The calculated reflectance of the optimized structures
+is shown in Fig. \ref{Fig2}. it is observed that they
+have an ODB in the near infrared (NIR) region of the electromagnetic spectrum, i. e.,
 structures designed from functions $f_{1}$ and $f_{3}$ with a porosity contrast of
-$30/76\%$ have the highest PBG localized from 970 to 1370 nm, these are shown in
-panels (a) and (c). \begin{figure}[tbph]
+$30/76\%$ have the widest ODB spanning from 970 to 1370 nm.
+
+\begin{figure}[tbph]
 	\begin{center}
@@
 	\end{center}
-	\caption{Calculated reflectance of the structures designed with the optimized parameters of $f_{1}$ (left), $f_{2}$ (center) and $f_{3}$ (right) and with the porosity contrasts of $30/76\%$ (upper panels) and $42/76\%$ (lower panels).
-The dotted lines limit the area of the PBG.}
+	\caption{Calculated reflectance of the optimized structures
+          with profile class $f_{1}$ (left), $f_{2}$
+          (center) and $f_{3}$ (right) and with the porosities
+          $30\%/76\%$ (upper panels) and $42\%/76\%$ (lower
+          panels). The dotted lines limit the area of the ODB.}
 	\label{Fig2}
@@
 
-Before showing the design of the structures formed by the stacking of sub-mirrors,
-the transfer matrix trace of individual mirrors formed by one period (Fig.
-\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)) was calculated. The reflectance
-of each mirror with its respective periods was also calculated (Figs. \ref{Fig3}(c)
-and \ref{Fig3}(d)). Each mirror was designed to reflect a wavelength in the range of
-400-3000 nm and the illumination range was the same. Additionally, the
-$\text{Tr}|M|$ and $R(\lambda,\theta)$ were calculated for light with
-  TE
-polarization and $45^\circ$ of incidence. In Fig. \ref{Fig3}(d) it is shown that by using
-mirrors that have 6 periods and designed to reflect at wavelengths greater than 1000
-nm, they also reflect in a certain region of the visible spectrum. Then, to
-reinforce the reflection of the electromagnetic waves in the visible, it is enough
-to place a smaller number of periods. This is another reason for the increasing
-number of periods in the 400 to 800 nm region. \begin{figure}[tbph]
+We calclulated the trace of the transfer matrix of single Bragg mirrors formed by one period (Fig.
+\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)), as well as their
+corresponding reflectance (Figs. \ref{Fig3}(c)
+and \ref{Fig3}(d)), as a function of the design wavelength
+$\lambda_{\text{dis}}$ and the wavelength of the illuminating light.
+$\text{Tr}\,\bm M$ and $R(\lambda,\theta)$ were calculated for
+TE polarized light incident at an angle of $45^\circ$.
+Fig. \ref{Fig3}(d) shows that a
+6-period mirror tuned to a  wavelength greater than 1000
+nm, may also reflect in a certain region of the visible spectrum. Then, to
+reinforce the reflection of the electromagnetic waves in the visible
+a smaller number of periods is enough. This is another reason for increasing
+number of periods in the 400 to 800 nm region.
+\begin{figure}[tbph]
 	\begin{center}
@@
 	\end{center}
-	\caption{Calculated transfer matrix trace and reflectance of individual mirrors using ((a) and (c)) one period  and ((b) and (d)) six periods, respectively.
-Each mirror was tuned to a wavelength between 400 and 3000 nm.
-The calculations were made in the visible and NIR region and at 45${{}^\circ}$ of incidence.}
+	\caption{Calculated trace of the transfer matrix (left) and
+          reflectance (right) of single Bragg mirrors one (top)
+          and six (bottom) periods as a function of the design
+          wavelength $\lambda_{\text{dis}}$ and the illumination
+          wavelength $\lambda_{\text{ilum}}$.
+          The calculations correspond to an incidence angle $\theta=45^\circ$.}
 	\label{Fig3}
@@
 
-It is common to imagine that the stacking of the sub-mirrors is the following: that
-the PBG of the second mirror begins at the edge of the PBG of the first mirror, the
-third PBG that begins at the edge of the PBG of the second mirror, and so on until
-the desired interval is completed. With this configuration, the reflectance
-decreases at each intersection of the two PBGs. For example, Figs. \ref{Fig4}(a)
+One strategy to design a wide band mirror could be stacking of the
+sub-mirrors so that the leftmost edge of the band of one mirror begins
+at the rightmost of the band of the previous mirror. However, with this
+configuration, the reflectance
+decreases where these band edges meet. For example, Figs. \ref{Fig4}(a)
 and \ref{Fig4}(b) show the calculated $R(\lambda, \theta)$ for the structures formed
 by sub-mirrors that have one and six periods, respectively, using non-polarized
-light. In these cases, the calculations do not show a PBG, or quasi-PBG. For this
-reason, the $R_{Ave}(\lambda, \theta)$ was maximized through the percentage of
-overlap of the PBGs of two consecutive sub-mirrors. In Fig. \ref{Fig3}(b) of the main
+light. In these cases, the calculations do not show a ODM, or quasi-ODM. For this
+reason, we allowed succesive bands to overlap by some percentage
+chosen to optimize the average reflectance $\braket{R}$. In Fig. \ref{Fig3}(b) of the main
 article the results obtained at the end of the optimization process are shown. The
 calculated $R(\lambda, \theta)$ for the structures designed with 4 periods for each
-sub-mirror and using the pattern described in the main article are shown in Figs.
-\ref{Fig4}(c) and \ref{Fig4}(d) of this document, respectively. Here the overlap of
+sub-mirror and using the pattern described in the main article are
+shown in this document in Figs.
+\ref{Fig4}(c) and \ref{Fig4}(d), respectively. Here the overlap of
 the two consecutive PBGs was optimized, being $72\%$ for the first case and $78\%$
-for the last. Furthermore, the calculations indicate that the structures have a
-quasi-PBG.
+for the second. Furthermore, the calculations indicate that the structures have a
+quasi-ODB.
 

### 2021-05-03 SupplementaryInformation.tex
Quite los \newpage y unos cambiecillos mas

@@
 
+\begin{figure}[!ht]
+	\begin{center}
+		\includegraphics[width=\textwidth]
+		{SIF1Squeme1DPC.pdf}
+	\end{center}
+	\caption{(a) Chirped-type photonic structure formed by two alternating
+		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
+		thickness $d_{a}$ and $d_{b}$ that increases gradually
+		according to some design scheme. We show schematically
+		the  incident and reflected electric and magnetic
+		fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
+		their wavevectors $\bm k_i$ and $\bm k_r$, the right
+		($+$) and left ($-$) moving fields within each layer
+		as well as their wavevectors $\bm k_\alpha^\pm$. (b)
+		The multilayer system can be replaced by an
+		effective layer within which supports right and left
+		moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
+		\pm K)$ and electric and magnetic field amplitudes
+		$\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
+		the wavevector unto the $xy$ plane is $\bm Q$ for all
+		the waves, due to translational symmetry and $K$ is
+		obtained from Eq. \eqref{dispersion}.}
+	\label{Fig1}
+\end{figure}
+
 Many equivalent formulations have been proposed to obtain $\bm M$. For
@@
 \end{equation}%
-where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
-	\begin{center}
-		\includegraphics[width=\textwidth]
-		{SIF1Squeme1DPC.pdf}
-	\end{center}
-	\caption{(a) Chirped-type photonic structure formed by two alternating
-		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
-		thickness $d_{a}$ and $d_{b}$ that increases gradually
-                according to some design scheme. We show schematically
-                the  incident and reflected electric and magnetic
-                fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
-                their wavevectors $\bm k_i$ and $\bm k_r$, the right
-                ($+$) and left ($-$) moving fields within each layer
-                as well as their wavevectors $\bm k_\alpha^\pm$. (b)
-                The multilayer system can be replaced by an
-		effective layer within which supports right and left
-                moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
-                \pm K)$ and electric and magnetic field amplitudes
-                $\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
-              the wavevector unto the $xy$ plane is $\bm Q$ for all
-              the waves, due to translational symmetry and $K$ is
-              obtained from Eq. \eqref{dispersion}.}
-	\label{Fig1}
-\end{figure}
+where T$\text{r}$ denotes the trace.
 
@@
 
-\begin{table}[tbph]
+\begin{table}[!ht]
 	\caption{Optimized design parameters for different profile
@@
 
-\begin{figure}[tbph]
+\begin{figure}[!ht]
 	\begin{center}
@@
 
-\newpage
-
 \section{Photonic structure with sub-mirrors stacking}
@@
 We calclulated the trace of the transfer matrix of single Bragg mirrors formed by one period (Fig.
-\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)), as well as their
-corresponding reflectance (Figs. \ref{Fig3}(c)
+\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(c)), as well as their
+corresponding reflectance (Figs. \ref{Fig3}(b)
 and \ref{Fig3}(d)), as a function of the design wavelength
@@
 reinforce the reflection of the electromagnetic waves in the visible
-a smaller number of periods is enough. This is another reason for increasing
+a smaller number of periods is enough. This is another reason for decreasing
 number of periods in the 400 to 800 nm region.
-\begin{figure}[tbph]
+\begin{figure}[!ht]
 	\begin{center}
@@
 	\end{center}
-	\caption{Calculated trace of the transfer matrix (left) and
-          reflectance (right) of single Bragg mirrors one (top)
-          and six (bottom) periods as a function of the design
+	\caption{Calculated trace of the transfer matrix (top) and
+          reflectance (bottom) of single Bragg mirrors one (left)
+          and six (right) periods as a function of the design
           wavelength $\lambda_{\text{dis}}$ and the illumination
@@
 \end{figure}
-\newpage
 

### 2021-05-03 PaperVictor.tex
No se estaban respetando unos espacios adecuadamente

@@
         Perez2018}. Thus,
-whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
-electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
+whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$ electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
 photonic band gap within which we
@@
 nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
-ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
-\% of the \hl{quasi-ODW's of our $S_2$ and $S_3$ structures}. Aditionally, the table
+ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6\% 
+of the \hl{quasi-ODW's of our $S_2$ and $S_3$ structures}. Aditionally, the table
 reveals that the porous silicon based
@@
 This project is supported by Consejo Nacional de Ciencia y
-Tecnolog\'{i}a through grant No.A-S1-30393(VA), 256243 (DA), C\'{a}tedras
+Tecnolog\'{i}a through grant No. A-S1-30393(VA), 256243 (DA), C\'{a}tedras
 Conacyt program 1577 (DA), and by DGAPA-PAPIIT UNAM under grant IN111119 (LM).
